---
title: "Climate Analyses 1"
author: "Devin Gamble"
date: "5/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE, echo = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(broom)
library(here)
library(ggplot2)
library(visreg)
library(jtools)
```

## Objective:  
#### Identify the *climate variables*, *periods* (YoC, Norms), and *temporal windows* (seasons, months, before/after) for which phenology is most sensitive.  
* See 'EDA2.Rmd' for exploration of different models.  

**ToC**  
1. tbd...  


4.? Sensitivity to long-term (normals) vs anomalies in SAME MODEL (and interaction?)


**To-Do**  
- Fix & clean up models describing sensitivity to different aspects of local climate  
- Calculate new seasonal windows of climate parameters (and save to csv)  
- Statistically compare slope estimates of climate parameters on DOY to select the most influential parameters  
- Add in PI as a covariate in models  



<br>  

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load in data & establish error distance bins
nemo_spec <- read_csv(here::here("data_cleaning", "nemo_all_2.csv")) %>% 
  mutate(error_bin = case_when(error_dist_m <= 2000 ~ "<2 km",
                               error_dist_m > 2000 & error_dist_m <= 5000 ~ "2-5 km",
                               error_dist_m > 5000 & error_dist_m <= 10000 ~ "5-10 km",
                               error_dist_m > 10000 & error_dist_m <= 15000 ~ "10-15 km", 
                               error_dist_m > 15000 ~ ">15 km")) %>% 
  select(specimen_number:error_dist_m, error_bin, everything()) %>% mutate(error_bin = factor(error_bin, levels = c( "<2 km", "2-5 km", "5-10 km", "10-15 km", ">15 km"))) #specify factor & levels for error bin
#1764 total obs. #1240 obs with error distance
climNA_all <- read_csv(here::here("climateNA", "all_cna", "climNA_nemo_all.csv")) %>% 
  rename(year = YoC) #Also 1764 obs

#Transform Precipitation variables to be normal -- Log transforms Monthly and seasonal PPT, MAP, MSP #PAS ignored
climNA_all1 <- climNA_all %>% 
  mutate_at(vars(PPT01_N51:PPT12_N51, PPT_wt_N51:PPT_at_N51, MAP_N51, MSP_N51,
                 PPT01_N81:PPT12_N81, PPT_wt_N81:PPT_at_N81, MAP_N81, MSP_N81,
                 PPT01_100Y:PPT12_100Y, PPT_wt_100Y:PPT_at_100Y, MAP_100Y, MSP_100Y,
                 PPT01_L1:PPT12_L1, PPT_wt_L1:PPT_at_L1, MAP_L1, MSP_L1,
                 PPT01_Y:PPT12_Y, PPT_wt_Y:PPT_at_Y, MAP_Y, MSP_Y), log) %>% 
  na_if(y = -Inf)
#see EDA_climate for other variables to be transformed... (maybe AHM, DD if using)
```

**Formulate New Seasonal Windows**  

ClimateNA wt = Dec - Feb
ClimateNA sp = Mar - May

Create *new* averages for seasons:

_wt2 = Nov-Dec; _wt3 = Nov-Jan
_sp2 = Feb-Mar; _sp3 = Feb-Apr

```{r warning = FALSE, message = FALSE, results = 'hide'}
#2-month winter average


#3 month winter average



#2 month spring average


#3 month spring average


```




```{r echo = FALSE, message = FALSE, warning = FALSE}
#Merge herbarium records and climate data (by specimen number)
nemo_df1 <- merge(nemo_spec, climNA_all1) #1764 obs and 1250 total columns

#FILTER YEARS to those after 1901 (start of climate data).
nemo_df2 <- nemo_df1 %>% 
  filter(year >= 1901) #narrowed to 1677 obs, Same as YoC - 1
sum(!is.na(nemo_df2$MAT_L1)) #YoC-1 -- 1665 obs
sum(!is.na(nemo_df2$MAT_Y)) #YoC -- 1677 obs

#Saving a csv with combined specimen and climate data
write_csv(nemo_df2, here::here("data_cleaning", "nemo_full_1901_2019.csv")) #Use this in future scripts
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Subsetting data by error bins
nemo_all_errors <- nemo_df2 %>% 
  filter(!is.na(error_dist_m)) 
#1166 after rm records before 1901

#0-5 km resolution
nemo_e0_5 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km" | error_bin == "2-5 km") #1033 entries
#0-2 km
nemo_e2 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km") #743 obs
```

Probably best to use `nemo_df2` (records after 1900) and maybe try `nemo_e0_5` (records with errors 0-5 km).  

Models are constructed to see which climate variables explain the most variation in DOY. It is not necessary to include covariates (elevation, lat/long, year). Climate data are site [and year; YoC/anomalies] specific. Include covariates when interested in the particular effect of one (e.g. elevation).  


## Long-term (100Y) Climate Variables  

May also consider:  
- NFFD, bFFP, CMD, RH, DD5, MCMT (see EDA2)

**Annual Variables**  
```{r message = FALSE, warning = FALSE, results = 'hide'}
#100Y

ann_clim1 <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_df2)
ann_clim2 <- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m, data = nemo_df2)
ann_clim3 <- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m + long, data = nemo_df2)
ann_clim4 <- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m + long + year, data = nemo_df2)
#No interactions

summary(ann_clim1)
summary(ann_clim2)
summary(ann_clim3)
summary(ann_clim4)
#Controlling for elevation severely reduces the effect of MAT (ns)
#Controlling for elev and long - the effect of temperature returns but is still quite small

summ(ann_clim3, vif = TRUE) #VIF for long, elev, MAP, MAT is high

visreg(ann_clim1, "MAT_100Y", xlab = "MAT (1901-2000)", points = list(col = "#404040"))
visreg(ann_clim1, "MAP_100Y", xlab = "MAP (1901-2000)", points = list(col = "#404040"))

visreg(ann_clim3, "MAT_100Y", xlab = "MAT (1901-2000)", points = list(col = "#404040"))
visreg(ann_clim3, "MAP_100Y", xlab = "MAP (1901-2000)", points = list(col = "#404040"))

```


```{r message = FALSE, warning = FALSE, echo = FALSE, eval = FALSE}
#redudant with EDA2 code
#plots
#Non-climatic
#standardized: means = 0 and var = 1
#Compare relative effect of each variable

nonclim1 <- lm(DOY ~ scale(elev_m) + scale(long) + scale(year), data = nemo_df2)
summary(nonclim1)

visreg(nonclim1, xvar = "elev_m", xlab = "Elevation (m)", points = list(col = "#404040")) 
visreg(nonclim1, "year", xlab = "Year", points = list(col = "#404040"))
#visreg(nonclim1, "lat", xlab = "Latitude", points = list(col = "#404040"))
visreg(nonclim1, "long", xlab = "Longitude", points = list(col = "#404040"))
```


The relationship b/w DOY and MAT weakens as the model is parameterized,while the estimate of MAP strengthens. MAP appears to be driving variation in DOY. There were no significant interactions between any covariates.  
While MAT still appears to advance DOY, controlling for geography seems to explain a good deal of this variation (over a 100-yr avg). Examining seasonal climate and anomalies should shed more light on this.  


Note: Everything at the annual scale for 100Y averages is strongly correlated (see EDA2.Rmd). Refer to `ann_clim3` model above (controls for elev_m and long).  
<br>  

**Seasonal Variables**

For Seasonal variables, examine models with:
- Tmin & Tave (Winter, spring) [No Tmax]  
- PPT (Winter, Spring, Summer)  


May also consider  
- DD > 5 (spring and winter)   
- DD > 18 (spring and summer)  
- CMD (winter, spring, summer)? RH?  
<br>  


From 'EDA2.Rmd', Both Spring temperature and precipitation (from 100Y averages) appeared to be the most influential on DOY. Tave had a higher R2 and Beta than Tmin for spring temps...  

Winter Conditions
```{r message = FALSE, warning = FALSE, results = 'hide'}
library(interactions)
####Seasonal variables
#Winter Conditions
sz_wt1 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y, data = nemo_df2)
summary(sz_wt1)

visreg(sz_wt1, xvar = "PPT_wt_100Y", xlab = "PPT (winter)", points = list(col = "#404040"))
visreg(sz_wt1, xvar = "Tmin_wt_100Y", xlab = "Tmin (winter)", points = list(col = "#404040"))

sz_wt1.1 <- lm(DOY ~ Tave_wt_100Y + PPT_wt_100Y, data = nemo_df2)
#summary(sz_clim1.1) #These have low R2 and high SE, plus estimates are crazy  


sz_wt1.2 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + PPT_wt_100Y*Tmin_wt_100Y, data = nemo_df2)
summary(sz_wt1.2) #R2 - 0.18, interaction B = -1.25     #Tmin more significant, removed Tave
#Interaction more significant when Tave retained

visreg(sz_wt1.2, xvar = "PPT_wt_100Y", xlab = "PPT (winter)", points = list(col = "#404040"))
visreg(sz_wt1.2, xvar = "Tmin_wt_100Y", xlab = "Tmin (winter)", points = list(col = "#404040"))

johnson_neyman(sz_wt1.2, pred = "Tmin_wt_100Y", modx = "PPT_wt_100Y")
interact_plot(sz_wt1.2, pred = "Tmin_wt_100Y", modx = "PPT_wt_100Y")
interact_plot(sz_wt1.2, pred = "PPT_wt_100Y", modx = "Tmin_wt_100Y") + theme_bw()


```


Controlling for geographic location (long and elev) [not shown], the interaction between Tmin_wt and PPT_wt disappears. Including year as a covariate slightly improves $R^2$ and Tmin estimate.  


Spring Conditions
```{r message = FALSE, warning = FALSE, results = 'hide'}
#Spring Conditions
sz_sp1 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y, data = nemo_df2)
summary(sz_sp1)
sz_sp1.1 <- lm(DOY ~ Tave_sp_100Y +  PPT_sp_100Y, data = nemo_df2)
summary(sz_sp1)

sz_sp1.2 <- lm(DOY ~ Tmin_sp_100Y +  PPT_sp_100Y + Tmin_sp_100Y*PPT_sp_100Y, data = nemo_df2)
summary(sz_sp1.2) #Interaction with Tmin much more significant, higher R2 and estimate
#Tave does still explain some variation, despite the interaction. Removed


visreg(sz_sp1, xvar = "PPT_sp_100Y", xlab = "PPT (spring)", points = list(col = "#404040"))
visreg(sz_sp1, xvar = "Tmin_sp_100Y", xlab = "Tmin (spring)", points = list(col = "#404040"))


johnson_neyman(sz_sp1.2, pred = "Tmin_sp_100Y", modx = "PPT_sp_100Y")
interact_plot(sz_sp1.2, pred = "Tmin_sp_100Y", modx = "PPT_sp_100Y", x.label = "Tmin (spring)", legend.main = "PPT (spring)") + theme_bw()
interact_plot(sz_sp1.2, pred = "PPT_sp_100Y", modx = "Tmin_sp_100Y", x.label = "PPT (spring)", legend.main = "Tmin (spring)") + theme_bw()
#Swapping Tave for DD>5: similar but much weaker. DD v correlated to Tave

```



Interaction term becomes marginally significant. Removing it, we see results similar to the above winter 'standard' model - advancing effect of Tmin (+ year), delaying effect of PPT (+ long, elevation)

Tmin appears to explain more variation than Tave *in its interaction with PPT_sp*. Interaction is stronger with Tmin than Tave and PPT. Better $R^2$ and AIC with Tmin model (no interaction).  

[Summer conditions are likely not biologically important in the phenology of N menziesii, patterns due to correlation]
```{r message = FALSE, warning = FALSE, echo = FALSE, eval = FALSE}
#Summer Conditions
sz_clim3 <- lm(DOY ~ Tmin_sm_100Y + PPT_sm_100Y, data = nemo_df2)
summary(sz_clim3)
sz_clim3.1 <- lm(DOY ~ Tave_sm_100Y + PPT_sm_100Y, data = nemo_df2)
summary(sz_clim3.1)
sz_clim3.2 <- lm(DOY ~ Tmin_sm_100Y +  PPT_sm_100Y + Tmin_sm_100Y*PPT_sm_100Y, data = nemo_df2)
summary(stepAIC(sz_clim3.2, direction = "both"))
#Looks like Summer PPT has the largest effect, with Tmin marginally advancing DOY. No interaction
visreg(sz_clim3.2, xvar = "PPT_sm_100Y", xlab = "PPT (summer)", points = list(col = "#404040"))
```

Winter x Spring
```{r message = FALSE, warning = FALSE, results = 'hide'}
sz_wt_sp1 <- lm(DOY ~ Tmin_sp_100Y + PPT_wt_100Y, data = nemo_df2)
summary(sz_wt_sp1)

sz_wt_sp1.1 <- lm(DOY ~ Tmin_sp_100Y + PPT_wt_100Y + Tmin_sp_100Y*PPT_wt_100Y, data = nemo_df2)
summary(sz_wt_sp1.1)

johnson_neyman(sz_wt_sp1.1, pred = "Tmin_sp_100Y", modx = "PPT_wt_100Y")
interact_plot(sz_wt_sp1.1, pred = "Tmin_sp_100Y", modx = "PPT_wt_100Y", x.label = "Tmin (spring)", legend.main = "PPT (winter)") + theme_bw()
johnson_neyman(sz_wt_sp1.1, pred = "PPT_wt_100Y", modx = "Tmin_sp_100Y")
interact_plot(sz_wt_sp1.1, pred = "PPT_wt_100Y", modx = "Tmin_sp_100Y", x.label = "PPT (winter)", legend.main = "Tmin (spring)") + theme_bw()



```

Comparing Models
```{r warning = FALSE, message = FALSE, echo = FALSE}
plot_summs(sz_wt1, sz_sp1, model.names = c("Winter", "Spring"), coefs = c("Tmin (wt)" = "Tmin_wt_100Y", "Tmin (sp)" = "Tmin_sp_100Y", "PPT (wt)" = "PPT_wt_100Y", "PPT (sp)" = "PPT_sp_100Y"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()#additive effects

z
plot_summs(sz_wt1.2, sz_sp1.2, sz_wt_sp1.1, coefs = c("Winter T*PPT" = "Tmin_wt_100Y:PPT_wt_100Y", "Spring T*PPT" = "Tmin_sp_100Y:PPT_sp_100Y", "Winter PPT * Spring T" = "Tmin_sp_100Y:PPT_wt_100Y"), model.names = c("Winter", "Spring", "Wt x Sp"), scale = TRUE) +
  theme_bw()#multiplicative effects

```




<br>  



Year of Collection Models [or Anomaly Models]

```{r message = FALSE, warning = FALSE, results = 'hide'}

```








