---
title: "EDA1"
author: "Devin Gamble"
date: "4/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load Packages
library(tidyverse)
library(here)
library(ggplot2)
library(kableExtra)


```


# Explorator Data Analysis 1
### Exploring the structure and variables of our combined cch1 & cch2 data - duplicates removed, elevation added for all observations. (Prior to PI scoring).  


## Checking out the data

```{r message = FALSE, warning = FALSE, echo = FALSE}
nemo_all1 <- read_csv(here::here("data_cleaning", "nemo_all_2.csv")) %>% 
  mutate(error_bin = case_when(error_dist_m <= 2000 ~ "<2 km",
                               error_dist_m > 2000 & error_dist_m <= 5000 ~ "2-5 km",
                               error_dist_m > 5000 & error_dist_m <= 10000 ~ "5-10 km",
                               error_dist_m > 10000 & error_dist_m <= 15000 ~ "10-15 km", 
                               error_dist_m > 15000 ~ ">15 km")) %>% 
  select(specimen_number:error_dist_m, error_bin, everything()) %>% mutate(error_bin = factor(error_bin, levels = c( "<2 km", "2-5 km", "5-10 km", "10-15 km", ">15 km"))) #specify factor & levels for error bin

#1240 obs with error distance - added column with error distance categories


summary(nemo_all1)

```




1. Visualizing distributions of variables of interest [variation within variables]

### Numerical variables

```{r warning = FALSE, message = FALSE}
#Year
ggplot(data = nemo_all1, aes(x = year)) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,160)) +
  scale_x_continuous(breaks = seq(1850, 2020, 10)) +
  ylab("Count") + 
  xlab("Year of Collection")

#Explore subgroups/multimodal peaks in year of collection

#Addresss outliers in the followering variables
#Try out box/jitter plots?


#Month
ggplot(data = nemo_all1, aes(x = month)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(month)), col = "red", size = 1.5) + #mean
  geom_text(aes(x = mean(month), y = 0, label = round(mean(month), 4)),  size = 4, vjust = -30, hjust = -1) + #mean
  geom_vline(aes(xintercept = median(month)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,800)) +
  scale_x_continuous(breaks = seq(1, 8, 1)) +
  ylab("Count") + 
  xlab("Month of Collection")


#Check out kernal density on the following


#DOY
ggplot(data = nemo_all1, aes(x = DOY)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(DOY)), col = "red", size = 1.5) + #mean
  geom_text(aes(x = mean(DOY), y = 0, label = round(mean(DOY), 3)),  size = 4, vjust = -25, hjust = -0.2) + #mean
  geom_vline(aes(xintercept = median(DOY)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,300)) +
  scale_x_continuous(expand = c(0,0), breaks = seq(0, 250, 20)) +
  ylab("Count") + 
  xlab("DoY of Collection")


#Elevation
ggplot(data = nemo_all1, aes(x = elev_m)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(elev_m)), col = "red", size = 1.5) + #mean
  geom_vline(aes(xintercept = median(elev_m)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  scale_x_continuous(breaks = seq(0, 2600, 500)) +
  ylab("Count") + 
  xlab("Elevation (m)")


```


#### Latitude and Longitude

```{r warning = FALSE, message = FALSE}

#Lat
ggplot(data = nemo_all1, aes(x = lat)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(lat)), col = "red", size = 1.5) + #mean
  geom_vline(aes(xintercept = median(lat)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,300)) +
  scale_x_continuous(expand = c(0,0), breaks = seq(30, 45, 1)) +
  ylab("Count") + 
  xlab("Latitude (deg)") +
  coord_flip()
  
#Long
ggplot(data = nemo_all1, aes(x = long)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(long)), col = "red", size = 1.5) + #mean
  geom_vline(aes(xintercept = median(long)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  scale_x_continuous(expand = c(0,0), breaks = seq(-125, -115, 1)) +
  ylab("Count") + 
  xlab("Longitude (deg)")


#Both

ggplot(data = nemo_all1, aes(x = long, y = lat)) +
  geom_point(color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  ylab("Latitude (deg)") + 
  xlab("Longitude (deg)")


#Error distance & bin
  


```



### Categorical variables

```{r}
#Source


#Herbarium
#Create new column for herbarium code?


#County
counties <- nemo_all1 %>% 
  select(specimen_number, year, DOY, county) %>% 
  group_by(county) %>% 
  summarize(count = n(), meanDOY = mean(DOY)) %>% 
  arrange(-count)

counties

#Subspecies




```


### Other visualizations




2. Investigating covariation among variables

### Numeric variables


Is there any covariation among non-date/time variables?

```{r}



```






### Numeric x categorical variables









### Create Map (Raster) of all collection locations, including effect of year








# Investigating Climate Data (ClimateNA)








