---
title: "EDA1"
author: "Devin Gamble"
date: "4/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load Packages
library(tidyverse)
library(here)
library(ggplot2)
library(kableExtra)

```


# Explorator Data Analysis 1
### Exploring the structure and variables of our combined cch1 & cch2 data - duplicates removed, elevation added for all observations. (Prior to PI scoring).  


## Checking out the data

```{r message = FALSE, warning = FALSE, echo = FALSE}
nemo_all1 <- read_csv(here::here("data_cleaning", "nemo_all_2.csv")) %>% 
  mutate(error_bin = case_when(error_dist_m <= 2000 ~ "<2 km",
                               error_dist_m > 2000 & error_dist_m <= 5000 ~ "2-5 km",
                               error_dist_m > 5000 & error_dist_m <= 10000 ~ "5-10 km",
                               error_dist_m > 10000 & error_dist_m <= 15000 ~ "10-15 km", 
                               error_dist_m > 15000 ~ ">15 km")) %>% 
  select(specimen_number:error_dist_m, error_bin, everything()) %>% mutate(error_bin = factor(error_bin, levels = c( "<2 km", "2-5 km", "5-10 km", "10-15 km", ">15 km"))) #specify factor & levels for error bin

#1240 obs with error distance - added column with error distance categories


summary(nemo_all1)

```




1. Visualizing distributions of variables of interest [variation within variables]

### Numerical variables

```{r warning = FALSE, message = FALSE}
#Year
ggplot(data = nemo_all1, aes(x = year)) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,160)) +
  scale_x_continuous(breaks = seq(1850, 2020, 10)) +
  ylab("Count") + 
  xlab("Year of Collection")

#Explore subgroups/multimodal peaks in year of collection

#Addresss outliers in the followering variables
#Try out box/jitter plots?


#Month
ggplot(data = nemo_all1, aes(x = month)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(month)), col = "red", size = 1.5) + #mean
  geom_text(aes(x = mean(month), y = 0, label = round(mean(month), 4)),  size = 4, vjust = -30, hjust = -1) + #mean
  geom_vline(aes(xintercept = median(month)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,800)) +
  scale_x_continuous(breaks = seq(1, 8, 1)) +
  ylab("Count") + 
  xlab("Month of Collection")


#Check out kernal density on the following


#DOY
ggplot(data = nemo_all1, aes(x = DOY)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(DOY)), col = "red", size = 1.5) + #mean
  geom_text(aes(x = mean(DOY), y = 0, label = round(mean(DOY), 3)),  size = 4, vjust = -25, hjust = -0.2) + #mean
  geom_vline(aes(xintercept = median(DOY)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,300)) +
  scale_x_continuous(expand = c(0,0), breaks = seq(0, 250, 20)) +
  ylab("Count") + 
  xlab("DoY of Collection")

ggplot(data=nemo_all1, aes(y = DOY)) + 
  geom_boxplot(fill = "green", color = "black") +
  theme_classic()


#Elevation
ggplot(data = nemo_all1, aes(x = elev_m)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(elev_m)), col = "red", size = 1.5) + #mean
  geom_vline(aes(xintercept = median(elev_m)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  scale_x_continuous(breaks = seq(0, 2600, 500)) +
  ylab("Count") + 
  xlab("Elevation (m)")


```


#### Latitude and Longitude

```{r warning = FALSE, message = FALSE}
#Lat
ggplot(data = nemo_all1, aes(x = lat)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(lat)), col = "red", size = 1.5) + #mean
  geom_vline(aes(xintercept = median(lat)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,300)) +
  scale_x_continuous(expand = c(0,0), breaks = seq(30, 45, 1)) +
  ylab("Count") + 
  xlab("Latitude (deg)") +
  coord_flip()
  
#Long
ggplot(data = nemo_all1, aes(x = long)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(long)), col = "red", size = 1.5) + #mean
  geom_vline(aes(xintercept = median(long)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  scale_x_continuous(expand = c(0,0), breaks = seq(-125, -115, 1)) +
  ylab("Count") + 
  xlab("Longitude (deg)")


#Both

ggplot(data = nemo_all1, aes(x = long, y = lat)) +
  geom_point(color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  ylab("Latitude (deg)") + 
  xlab("Longitude (deg)")


ggplot(data = nemo_all1, aes(x = long, y = lat)) + 
  geom_hex() +
  scale_fill_continuous(type = "viridis") + 
  theme_classic()



```


```{r warning = FALSE, message = FALSE}
#Error distance & bin
ggplot(data = nemo_all1, aes(x = error_dist_m)) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,800)) +
  ylab("Count") + 
  xlab("Error distance (binned)")
  

ggplot(data = nemo_all1, aes(x = error_bin)) +
  geom_bar(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,800)) +
  ylab("Count") + 
  xlab("Error distance (binned)")
  
#BREAK DOWN to compare source

ggplot(data = nemo_all1, aes(x = error_bin, by = source)) +
  geom_bar(color = "black", aes(fill = source)) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,800)) +
  ylab("Count") + 
  xlab("Error distance (binned)")


sum(!(is.na(nemo_all1$georef_by))) #458 manually georeferenced specimens


ggplot(data = nemo_all1, aes(x = error_bin, by = georef_by)) +
  geom_bar(color = "black", aes(fill = georef_by), show.legend = FALSE) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,800)) +
  ylab("Count") + 
  xlab("Error distance (binned)") +
  labs(title = "Error distance bins (georeferenced)")


```



### Categorical variables

```{r}
#Source
ggplot(data = nemo_all1, aes(x = source, by = georef_by)) +
  geom_bar(aes(fill = georef_by), color = "black", show.legend = FALSE) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,1300)) +
  ylab("Count") + 
  xlab("Source") +
  labs(title = "Specimen count by source (georeferenced)")

#Herbarium
#Create new column for herbarium code?

ggplot(nemo_all1, aes(x = source, y = year)) + 
  geom_boxplot()

#County
counties <- nemo_all1 %>% 
  select(specimen_number, year, DOY, county) %>% 
  group_by(county) %>% 
  summarize(count = n(), meanDOY = mean(DOY)) %>% 
  arrange(-count)


#Subspecies

ggplot(data = nemo_all1, aes(x = sub_sp)) +
  geom_bar(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,1300)) +
  ylab("Count") + 
  xlab("Source")

```


2. Investigating covariation among variables

### Numeric variables


Is there any covariation among non-date/time variables?  

Does not look like it - not much to check.  
<br>  


```{r echo = FALSE}
ggplot(data = nemo_all1, aes(x = elev_m, y = DOY)) + 
  geom_point() +
  geom_smooth(method = "lm") + 
  theme_classic()

#Looks like DOY is earlier for specimens collected from lower elevations - makes sense

ggplot(data = nemo_all1, aes(x = year, y = DOY)) + 
  geom_point() +
  geom_smooth(method = "lm") + 
  theme_classic()

ggplot(data = nemo_all1, aes(x = long, y = DOY)) + 
  geom_point() +
  geom_smooth(method = "lm") + 
  theme_classic() #Earlier DOYs closer to the coast?

ggplot(data = nemo_all1, aes(x = lat, y = DOY)) + 
  geom_point() +
  geom_smooth(method = "lm") + 
  theme_classic() #very slight negative trend - earlier DOY with higher lat


```



<br>  


### Create Map (Raster) of all collection locations, including effect of year


 + Layer in elevation
 +year
 
```{r warning = FALSE, message = FALSE}
library(sf)
#convert coords to spatial data
nemo_sf <- st_as_sf(nemo_all1, crs = 4326, coords = c("long", "lat")) #specifies CRS (WGS84), coords

ca_border <- read_sf(here::here("analyses", "ca_state_border"), layer = "CA_State_TIGER2016") # imports all files with prefix


ggplot() +
  geom_sf(data = ca_border, fill = "#d9fae8") +
  geom_sf(data = nemo_sf, aes(color = year), alpha = 0.5, size = 1.5, show.legend = TRUE) + #Add 'pch' for borders
  scale_color_gradientn(colors = c("#ffffff", "#004063"), values = c(0, 1)) +
  theme_void()


ggplot() +
  geom_sf(data = ca_border, fill = "#d9fae8") +
  geom_sf(data = nemo_sf, aes(color = elev_m), alpha = 0.8, size = 1.5, show.legend = TRUE) +
  scale_color_gradientn(colors = c("#ade2ff", "#004063"), values = c(0, 1)) +
  theme_void()

ggplot() +
  geom_sf(data = ca_border, fill = "#d9fae8") +
  geom_sf(data = nemo_sf, aes(color = DOY), alpha = 0.8, size = 1.5, show.legend = TRUE) +
  scale_color_gradientn(colors = c("#ffffff", "#000003"), values = c(0, 1)) +
  theme_void()


```
 
 
