---
title: "Exploratory Analyses 2"
author: "Devin Gamble"
date: "4/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(here)
library(ggplot2)
library(corrplot)
library(visreg)
library(jtools)
library(interactions)
```


### Objective: Explore Models of DOY  

See 'EDA1.Rmd' for exploration of variables from the georeferrenced herbarium records and 'EDA_climate.Rmd' for ClimateNA variables (mostly distributions).  

**In This Document**  
1. DOY ~ Non-climatic variables [line 200]  
2. Correlations among variables [line 225]  (Model Diagnostic code [line 290])  
3. How has climate change over time [line 340]  
5. Exploratory DOY~Climate models [???700?]  


<br>  

#### Notes on Data sets and Organization:  

Through separate rounds of cleaning and duplicate removal, georeferencing, obtaining climate data, and (soon) scoring, there are several different csv files with *Nemophila* specimen data present in this project repository. For clarity, they are listed out her detailing what they contain and how recently they were made.  

**Specimen Records**:  
These csv files can be found in the 'data_cleaning' folder. They include  

CCH1 Data:  
- `Nemo_CCH1_02182020.csv` - CCH1 data set standardized by Ivana  
- `nemo_cch1_cleaned.csv` - cleaned (by DG) CCH1 data set
- Georeferenced CCH1 splits (folder) - split by herbarium and georeferenced; combined with CCH2 data


CCH2 Data:  
- `occurrences.csv` - the original specimen data downloaded from CCH2  
- `nemo_cch2_Dec2019.csv` - cleaned up from the occurrences data  
- `nemo_cch2_cleaned_V2.csv` - further cleaning, removing duplicates. This was then split up into subsets by herbarium for georeferencing & scoring.  
- Splits for PI folder has most recent cleaned CCH2 splits ("_pi.csv" files are more up to date! Dupes & odd things removed, data re-split by CCH2 herbaria *after* running `combine_cch1_cch2_V2.R` script)


Combined CCH1 & CCH2:  
* See "combine_cch1_cch2_V2.R" for more details.  
- `cch1&2_combined.csv` - attempt at combination, NOT cleaned  
- `nemo_all_1.csv` - first updated combination of CCH1 and CCH2 records  
- `nemo_all_2.csv` - second combination of CCH1 and CCH2 records, added elevation (m) from 'elevatr' package. (Used to make latest PI splits). **Most up-to-date combined specimen data!!**  


**Climate Data**:  
See "get_cna_all.Rmd" for more details. Uses `nemo_all_2.csv` as input to create ClimateNA compatible csv `all_CNA_s.csv`.  
- First-attempt CCH1 and 2 climate data can be found in their respective folders under "ClimateNA"  
- ClimateNA downloads are in the "cna_rawfiles" folder, in the "all_CNA" folder under  
- These were cleaned and combined to get `norms_raw_51_and_81.csv`, `YoC_Y_and_L1.csv`, `100y_avg.csv`  
- Anomalies calculated in 'get_cna_anoms.Rmd', creates `climNA_anoms.csv`  
- All the above data sets combined into `climNA_nemo_all.csv` saved in "all_cna" folder **Most up-to-date Climate-only data!!**  


**Combined data sets**:  
In this Rmd, `nemo_all_2.csv`, with added error distance, and `climNA_nemo_all.csv`, with PPT vars log-transformed, are combined and saved to `nemo_full_1901_2019.csv`, filtering for years only from 1901-2019.  **Most up-to-date combined file!!**  


<br>  

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load in data & establish error distance bins

nemo_spec <- read_csv(here::here("data_cleaning", "nemo_all_2.csv")) %>% 
  mutate(error_bin = case_when(error_dist_m <= 2000 ~ "<2 km",
                               error_dist_m > 2000 & error_dist_m <= 5000 ~ "2-5 km",
                               error_dist_m > 5000 & error_dist_m <= 10000 ~ "5-10 km",
                               error_dist_m > 10000 & error_dist_m <= 15000 ~ "10-15 km", 
                               error_dist_m > 15000 ~ ">15 km")) %>% 
  select(specimen_number:error_dist_m, error_bin, everything()) %>% mutate(error_bin = factor(error_bin, levels = c( "<2 km", "2-5 km", "5-10 km", "10-15 km", ">15 km"))) #specify factor & levels for error bin
#1240 obs with error distance - added column with error distance categories
#1764 obs total

climNA_all <- read_csv(here::here("climateNA", "all_cna", "climNA_nemo_all.csv")) %>% 
  rename(year = YoC) #Also 1764 obs

#Transform Precipitation variables to be normal -- Log transforms Monthly and seasonal PPT, MAP, MSP
#log transformations do not work on PAS
climNA_all1 <- climNA_all %>% 
  mutate_at(vars(PPT01_N51:PPT12_N51, PPT_wt_N51:PPT_at_N51, MAP_N51, MSP_N51,
                 PPT01_N81:PPT12_N81, PPT_wt_N81:PPT_at_N81, MAP_N81, MSP_N81,
                 PPT01_100Y:PPT12_100Y, PPT_wt_100Y:PPT_at_100Y, MAP_100Y, MSP_100Y,
                 PPT01_L1:PPT12_L1, PPT_wt_L1:PPT_at_L1, MAP_L1, MSP_L1,
                 PPT01_Y:PPT12_Y, PPT_wt_Y:PPT_at_Y, MAP_Y, MSP_Y), log) %>% 
  na_if(y = -Inf)
#see EDA_climate for other variables to be transformed... (maybe AHM, DD if using)
```
<br>  

Adding Collector information from original data sets back in  

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(lubridate)
#Read in 'original' cch1 data, isolate specimen_number, date_new, and collector
#cch1
nemo_cch1_1 <- read_csv(here::here("data_cleaning", "CCH1_scripts_data", "Nemo_CCH1_02182020.csv")) %>% 
  select(specimen_number, collector, verbatim_date) %>% 
  mutate(date_new = case_when(str_detect(verbatim_date, "-") ~ as_date(ymd(verbatim_date)),
         str_detect(verbatim_date, "/") ~ as_date(mdy(verbatim_date)))) #standardizes dates, this line copied from cch1_cleaning.R

nemo_cch1_2 <- nemo_cch1_1 %>% 
  mutate(collector = gsub('"', '', collector)) %>% #removes quotes
  select(specimen_number, date_new, collector)


#cch2 -- specimen_numbers manually fixed early on. Using 'id' as identifier instead
nemo_cch2_1 <- read_csv(here::here("data_cleaning", "CCH2 12-19-19 download", "occurrences.csv")) %>% 
  select(id, eventDate, recordedBy, year, month, day) %>% 
  mutate(date_new = make_date(year = year, month = month, day = day)) %>% #copied from cch2_cleaning.R , same date method #identical to eventDate but including here to be consistent
  rename(collector = recordedBy) %>% 
  select(id, date_new, collector)


#
#Add collector columns to latest specimen set
#Match by specimen number and date

collectormerge1 <- merge(nemo_spec, nemo_cch2_1, by = c('id', 'date_new'), all.x = TRUE)

collectormerge2 <- merge(collectormerge1, nemo_cch1_2, by = c('specimen_number', 'date_new'), all.x = TRUE)
#Some overlap for cch1 x cch2 duplicates


#combine the collector columns, have cch2 (collector.x) take priority
nemo_spec2 <- collectormerge2 %>% 
  mutate(collector = case_when(!is.na(collector.x) ~ collector.x, 
                               is.na(collector.x) ~ collector.y)) %>%  #Perfect!
  select(-collector.x, -collector.y) %>% 
  select(specimen_number, id, date_new, year, month, day, DOY, sub_sp, collector, everything()) #re-ordering columns
#Should now have 32 columns and 1764 obs

#Collector info for all but 8 (6 + 2 'unknown') records!
```


```{r echo = FALSE, message = FALSE, warning = FALSE}
#Merge herbarium records and climate data (by specimen number)
nemo_df1 <- merge(nemo_spec2, climNA_all1) #1764 obs and 1251 total columns

write_csv(nemo_df1, here::here("data_cleaning", "nemo_full_1861_2019.csv")) #All years in the data


#FILTER YEARS to those after 1901 (start of climate data).
nemo_df2 <- nemo_df1 %>% 
  filter(year >= 1901) #narrowed to 1677 obs, Same as YoC - 1
sum(!is.na(nemo_df2$MAT_L1)) #YoC-1 -- 1665 obs
sum(!is.na(nemo_df2$MAT_Y)) #YoC -- 1677 obs

#Saving a csv with combined specimen and climate data
write_csv(nemo_df2, here::here("data_cleaning", "nemo_full_1901_2019.csv")) #Use this in future scripts - 1677 obs, 1251 columns
```


Create subset of data where each observation has an error distance:  

```{r warning = FALSE, message = FALSE}

nemo_all_errors <- nemo_df2 %>% 
  filter(!is.na(error_dist_m)) 
#1239 out of 1764 obs with error distance
#1166 after rm records before 1901

#0-5 km resolution
nemo_e0_5 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km" | error_bin == "2-5 km") #1081 entries

#0-4 km
nemo_e0_4 <-  nemo_all_errors %>% 
  filter(error_dist_m >= 0 & error_dist_m <= 4000) #1010 obs #Do Not include error_bin in models

#0-2 km
nemo_e2 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km") #761 obs


```


<br>  


## How does DoY depend on non-climatic variables?  

```{r warning = FALSE, message = FALSE}
lm1 <- lm(DOY ~ elev_m + year + long, data = nemo_df1) #all years
lm1.1 <- lm(DOY ~ elev_m + year + long, data = nemo_df2) #>1900
summary(lm1.1)
#summary(lm1.1)

visreg(lm1, xvar = "elev_m", xlab = "Elevation (m)", points = list(col = "#404040")) 
visreg(lm1, "year", xlab = "Year", points = list(col = "#404040"))
visreg(lm1, "long", xlab = "Longitude", points = list(col = "#404040"))

lm1.2 <- lm(DOY ~ elev_m + year + long + long*elev_m, data = nemo_df2) 
summary(lm1.2)
#No interactions with year
#interact_plot(lm1.2, pred = "long", modx = "elev_m")

#summ(lm1.1, vif = TRUE) #VIF for long, elev, MAP, MAT is high

```
**DOY is earlier for lower elevations, lower latitudes, later years.**
<br>  


## Variable Correlations:

Which geographical and climate variables are correlated with one another?  
(And how could these make future analyses difficult?)  

```{r warning = FALSE, message = FALSE, echo = FALSE}
#check correlated climate variables for subset of whole df - 100 year averages
library(corrplot)
nemo_corrcheck_an <- nemo_df1 %>% 
  select(MAT_100Y:MCMT_100Y, MAP_100Y:DD5_100Y, NFFD_100Y, PAS_100Y, CMD_100Y, RH_100Y, lat, long, elev_m, year)

cor_an <- cor(nemo_corrcheck_an)
corrplot(cor_an, type = "upper", method = "square", addCoef.col = "black", number.cex = .6, diag = F)

#seasonal variables

nemo_corrcheck_sz <- nemo_df1 %>% 
  select(Tmin_wt_100Y:PPT_sp_100Y, DD5_wt_100Y:DD5_at_100Y, lat, long, elev_m, year)
#Humidty, NFFD, and CMD exlcuded: CMD_sp_100Y, CMD_sm_100Y, RH_wt_100Y:RH_at_100Y, NFFD_wt_100Y:NFFD_at_100Y
#PPT_sm_100Y all NAs, not included

cor_sz <- cor(nemo_corrcheck_sz)
corrplot(cor_sz, type = "upper", method = "square", addCoef.col = "black", number.cex = .5, diag = F)


##Correlations among YoC, Normals, and anomalies...   
nemo_cor_norms <- nemo_df2 %>% 
  filter(year >= 1901, year <= 2017) %>% 
  select(MAT_100Y, MAT_N51, MAT_N81, MAP_100Y, MAP_N51, MAP_N81, Tave_sp_100Y, Tave_sp_N81, MAT_Y, MAP_Y, Tave_sp_Y)
cor_norm <- cor(nemo_cor_norms)
corrplot(cor_norm, method = "square", addCoef.col = "black", number.cex = .8, diag = F, type = "upper", na.label = "o")
#Unsurprising, all normals extremely well correlated, choice of which not too important

#Anomalies
nemo_cor4 <- nemo_df2 %>% 
  filter(year >= 1901, year <= 2017) %>% 
  select(MAT_100Y, MAP_100Y, Tmin_sp_100Y, PPT_wt_100Y, MAT_Y, MAP_Y, Tmin_sp_Y, PPT_wt_Y, MAT_A, MAP_A, Tmin_sp_A, PPT_wt_A)
cor4 <- cor(nemo_cor4)
corrplot(cor4, method = "square", addCoef.col = "black", number.cex = .6, diag = F, type = "upper", na.label = "o")


#Significance test of correlations
#cr2 <- cor.mtest(nemo_corrcheck_sz, conf.level = 0.7)
#corrplot(cor_sz, p.mat = cr2$p, insig = "pch", pch.cex = 1, method = "square", type = "upper", order = "FPC", addCoef.col = "black", number.cex = 0.5, diag = F)
```


**Correlations** to be wary of:  
[Geographic]  
- *Lat* correlated with MAT, DD5, AHM (~-.3-.4 ), elev_m (-.4), AHM (-.6), MAP (.58)  
- *Long* correlated with CMD, AHM, MWMT (.4-.5), elev (.51), MAP (-.57)  
- *Elev_m* also correlated to MAT (-.47) [but not MAP], MCMT, NFFD (~-.6), DD_0 (.68), MSP, PAS (.44)  

[Climatic]  
- *MAT* with MAP/MSP (.59), DD5 (~1), DD_0 (-.76), CMD:NFFD (.6-.7), PAS (.62)  
- *MAP* also with DD5 (.62), AHM (.9)  
- *Anomalies*: Some variables negatively correlated b/w _Y and _As  

* Seasonal temperature variables correlated with each other, with elevation  
* Some Spring Tave and Spring PPT parameters correlated  
* Seasonal PPT correlated with DD5, Spring temperatures, *not* correlated to elevation  
* Lat and Long similarly correlated to MAT [+/-0.32] and MAP [+/- 0.57], lat*long = 0.93  
* Anomalies pretty uncorrelated to other periods!  

Year had no large correlations with any variables (all < .3). Normals strongly correlated from different periods - MAT x MAP correlations consistent. 

```{r echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE}
#Diagnostics
#Checking Linear Regression Assumptions
#• Linear relationship between covariates and response (residuals vs fitted plot) - plot 1 - check
#• Homoscedasticity (constant variance) - plot 3 - check
#• Normality (of the error distribution) (residual QQ plot) - plot 2 - check
#• Absence of multicollinearity - check
#• No autocorrelation - not time series data

plot(lm1) #nemo_df1

vif(lm1) #VIF < 2 generally okay.  
sqrt(vif(lm1)) > 2


#Check outliers
plot(lm1, 4)
#Use influence threshold of 4/n = 0.0022 - seems unreasonably low
#obs 155 may need to be removed?

#Influence of points on each coefficient
dfbetasPlots(lm1, id.n = 2, id.col = "red")


#Partial resid plots
crPlots(lm1)

#Check autocorrelation
rd <- residuals(lm1)

par(mfrow = c(1,2))
plot(rd, ylab = "Residuals", main = "Residuals plot", font.main=1, cex.main = 1)
abline(h=0)
plot(rd[-length(rd)], rd[-1],
     xlab = expression(hat(epsilon)[i]),
     ylab = expression(hat(epsilon)[i+1]), main = "Autocorrelation Check", font.main=1, cex.main = 1)
lines(lowess(rd[-length(rd)],rd[-1]), col = "red", lty = 2)



#
# * Re-do these diagnostics for final models in the future
```

------  


## How have climate variables changed over time???  

Objective:  
Describe trends and rates of change over time *across California* in the following types of variables in  
- YoC Climates  
- Climate Anomalies

Split by climate group and include as covariate? (As in Natalies *Streptanthus* analyses)

#### Annual Variables  

Quantify rate of climate change in 
- Tmin wt and sp  
- PPT wt and sp  
- MAT  
_ MAP  


Note: Though analyses of DOY ~ Climate may not include covariates (to focus on the effect of cliamte variables), geography (lat/long) and MAP are included here in addition to year to control for variation in climate over space. Also include PI when available.  

**MAT**  
```{r message = FALSE, warning = FALSE, echo = FALSE}
#YoC
mat_t1 <- lm(MAT_Y ~ year, data = nemo_df2)
#summary(mat_t1)


#Control for geography (and PI) - use this model
mat_t1.1 <- lm(MAT_Y ~ year + elev_m + long, data = nemo_df2)
#summary(mat_t1.1)

mat_t1.3 <- lm(MAT_Y ~ year + MAP_Y + elev_m + long, data = nemo_df2)
#summary(mat_t1.3) #Best model


mat_t1.4 <- lm(MAT_Y ~ year + MAP_Y + elev_m + long + MAP_Y*elev_m*long, data = nemo_df2)
summary(mat_t1.4) #Better R2 - significant interactions, lowest AIC w/ 3-way interaction
visreg(mat_t1.4, xvar = "year", points = list(col = "#404040"))
#Too many interactions and this gets crazy...

#Visualize Interactions
johnson_neyman(mat_t1.4, pred = "MAP_Y", modx = "long")
johnson_neyman(mat_t1.4, pred = "elev_m", modx = "long")
johnson_neyman(mat_t1.4, pred = "MAP_Y", modx = "elev_m") 
interact_plot(mat_t1.4, pred = "MAP_Y", modx = "elev_m")
interact_plot(mat_t1.4, pred = "elev_m", modx = "long", mod2 = "MAP_Y")

#Compare model estimates
#plot_summs(mat_t1, mat_t1.1, mat_t1.3, mat_t1.4, scale = TRUE)

#Change over time: MAT~Year beta = 0.011 [mat_t1.4]
print("MAT_Y warming (°C) over 120 years")
.0118*120


```

 
Interactions:  
- MAT_Y is greater at more inland longitudes, and at lower elevations  
- MAT_Y declines faster going up in elevation with more inland longitudes. This effect is strengthened by greater  MAP_Y (below 1000 m) in the west and weakened by greater MAP_Y in the east 
- Interactions with long are less significant than with elev_m and MAP  



**MAP**  
```{r warning = FALSE, message = FALSE, echo = FALSE}
#YoC
map_t1 <- lm(MAP_Y ~ year + elev_m + long, data = nemo_df2)
#summary(map_t1)

map_t1.1 <- lm(MAP_Y ~ year + elev_m + long + MAT_Y, data = nemo_df2)
summary(map_t1.1)
visreg(map_t1.1, xvar = "year", line = list(alpha = 0), points = list(col = "#404040"),  band = FALSE) #Not sure how to hide line without gg=TRUE...

```
No significant change in average MAP over years of collection  


**Frost Free Days**  
```{r warning = FALSE, message = FALSE}

ffd_t1 <- lm(NFFD_Y ~ year + elev_m + long + MAP_Y, data = nemo_df2)
summary(ffd_t1)

ffd_t1.1 <- lm(bFFP_Y ~ year + elev_m + long + MAP_Y, data = nemo_df2)
summary(ffd_t1.1)

visreg(ffd_t1.1, xvar = "year", points = list(col = "#404040"), gg = TRUE) + 
  theme_classic()


```



#### Seasonal Variables  
Note: See Climate_1.Rmd for selection of variables and seasons  




#### Monthly (& custom windows)  






Consider differences across geographic climate regions?  

### Change in Anomalies over time  

**MAT**
```{r message = FALSE, warning = FALSE, echo = FALSE}
#MAT Anomalies
mat_t2 <- lm(MAT_A ~ year + elev_m*long*MAT_Y, data = nemo_df2) #No effect of MAP_A, no interaction
summary(mat_t2)

visreg(mat_t2, xvar = "year", points = list(col = "#404040"), gg = TRUE, line = list(alpha = 0), band = FALSE) + 
  geom_smooth(method = "gam", col = "red") + 
  theme_bw()
#Maybe a different type of model would be more appropriate (not lm)


plot(mat_t2)

#MAT_A is normal, but the residuals are not - autocorrelation?
durbinWatsonTest(mat_t2)
#Looks like residuals are correlated.... 
#Do we need to create better models if we're just following a trend? No, but to quantify the rate of change (Slope) we would.

print("MAT anomalies (°C) increase over 120 years")
.007*120 #Not sure this makes sense since the relationship is not linear...
```
Similar interactions explain variation in MAT_A...   


**MAP**  
```{r warning = FALSE, message = FALSE, echo = FALSE}
#Anomalies
map_t2 <- lm(MAP_A ~ year + elev_m + long + MAP_Y + MAT_Y, data = nemo_df2) #YoC & anom correlated (r = .45), include?
summary(map_t2)

visreg(map_t2, xvar = "year", points = list(col = "#404040"), gg = TRUE, line = list(alpha = 0), band = FALSE) + 
  theme_bw()

```

Slightly significant effect of year becomes ns when controlling for YoC MAP/MAT
<br>  



## EXPLORATORY ANALYSES - See 'Climate_1.Rmd' for more finalized analyses  

### How does DOY depend on climate?  



Note: The following parameter estimates of Precipitation variables on DOY are log-transformed and need to be back-transformed to be adequately interpreted.  
Note2: It is not necessary to include covariates for elev_m, lat/long, year if we're mainly interested in the effect of climate variables on DOY...  

<br>  

#### Annual Climate  

```{r message = FALSE, warning = FALSE, results = 'hide'}
MAT_lm1 <- lm(DOY ~ MAT_100Y + year + elev_m + lat, data = nemo_df1)
MAT_lm1.1 <- lm(DOY ~ MAT_100Y, data = nemo_df1)
summary(MAT_lm1) #R2 = .2646, MAT B = -2.53
summary(MAT_lm1.1)

MAP_lm1 <- lm(DOY ~ MAP_100Y + year + elev_m + lat, data = nemo_df1)
MAP_lm1.1 <- lm(DOY ~ MAP_100Y, data = nemo_df1)
summary(MAP_lm1)#R2 = .2894, MAP B = 14.6
summary(MAP_lm1.1)


ann_lm1 <- lm(DOY ~ MAT_100Y + MAP_100Y + long + elev_m + year, data = nemo_df2)
ann_lm1.1 <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_df2)
summary(ann_lm1) #R2 = .2989 #MAT estimate is much lower than in first lm (MAP slightly lower)
summary(ann_lm1.1)
#MAT NS if nemo_df1 is used
#MAP and MAT somewhat correlated (r = -.58) but no interaction present

ann_lm1.2 <- lm(DOY ~ MAT_Y + MAP_Y, data = nemo_df2)
summary(ann_lm1.2)

```


```{r message = FALSE, warning = FALSE}

summary(ann_lm1.1)
visreg(ann_lm1.1, "MAT_100Y", xlab = "MAT 100Y")
visreg(ann_lm1.1, "MAP_100Y", xlab = "MAP 100Y")

summary(ann_lm1.2)
visreg(ann_lm1.2, "MAT_Y", xlab = "MAT Y")
visreg(ann_lm1.2, "MAP_Y", xlab = "MAP Y")

#Analyses w normals not shown
#R2 highest (and coeffs most -) for 100Y avg climate - use it for long term avg.  
```

```{r message = FALSE, warning = FALSE, echo = FALSE}
##
#NICE PLOT of DOY ~ MAT
##
MAT_lm1 <- lm(DOY ~ MAT_100Y , data = nemo_df1)
summary(MAT_lm1)

ggplot(aes(x = MAT_100Y, y = DOY), data = nemo_df1) +
  geom_point(aes(color = MAP_100Y), alpha = .8) +
  labs(color = "log(MAP)") +
  geom_smooth(method = "lm", color = "#454545") +
  scale_color_gradientn(colors = c("#ade2ff", "#001775"), values = c(0, 1)) +
  xlab("MAT (°C)") +
  ylab("DOY") +
  theme_classic()
#ggsave(here::here("analyses", "figs1", "DOY-MAT_MAP_point.png"), height = 5, width = 8) #saved version PPT not transformed
  
#Opposite

ggplot(aes(x = MAP_100Y, y = DOY), data = nemo_df1) +
  geom_point(aes(color = MAT_100Y), alpha = .8) +
  labs(color = "MAT (°C)") +
  geom_smooth(method = "lm", color = "#454545") +
  scale_color_gradientn(colors = c("#fdff91", "#e30000"), values = c(0, 1)) +
  xlab("log(MAP)") +
  ylab("DOY") +
  theme_classic()

#ggsave(here::here("analyses", "figs1", "DOY-MAP_MAT_point.png"), height = 5, width = 8)

```



MAT predicts advanced DOY, MAP predicts delayed DOY.

Elevation and MAP/MAT appear to have the most significant effects on DOY.  

<br>  


MAT 
```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
MAT_m0 <- lm(DOY ~ MAT_100Y, data = nemo_df1)
MAT_m1 <- lm(DOY ~ MAT_100Y + elev_m, data = nemo_df1)
MAT_m1.1 <- lm(DOY ~ MAT_100Y + elev_m, data = nemo_df2)
MAT_m1.2 <- lm(DOY ~ MAT_100Y + elev_m, data = nemo_e0_5) #Best
summary(MAT_m1)
summary(MAT_m1.1)
summary(MAT_m1.2) #or summ(MAT_m1.2, vifs =  TRUE)
#0-5 km model best, df1 and df2 similar

#Anomalies...

#YoC
MAT_m2.2 <- lm(DOY ~ MAT_Y + elev_m, data = nemo_e0_5)
summary(MAT_m2.2)

#plot_summs(MAT_m1, MAT_m1.1, MAT_m1.2, MAT_m2.2, scale = TRUE, coefs = c("MAT (1901-2000)" = "MAT_100Y", "MAT (YoC)" = "MAT_Y", "Elevation (m)" = "elev_m"), model.names = c("All records", "Records 1901-2019", "Errors 0-5 km", "YoC 0-5 km"), legend.title = expression('Model')) #Same pattern with YoC climate

```


MWMT & MCMT  

```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
MW_m0 <- lm(DOY ~ MWMT_100Y, data = nemo_df1)
MW_m1 <- lm(DOY ~ MWMT_100Y + elev_m + lat, data = nemo_df1)
MW_m1.1 <- lm(DOY ~ MWMT_100Y + elev_m + lat, data = nemo_df2)
MW_m1.2 <- lm(DOY ~ MWMT_100Y + elev_m + lat, data = nemo_e0_5) #Better
summary(MW_m1)
summary(MW_m1.1)
summary(MW_m1.2)

MC_m0 <- lm(DOY ~ MCMT_100Y, data = nemo_df1)
MC_m1 <- lm(DOY ~ MCMT_100Y + elev_m + lat, data = nemo_df1) #barely better, all similar
MC_m1.1 <- lm(DOY ~ MCMT_100Y + elev_m + lat, data = nemo_df2)
MC_m1.2 <- lm(DOY ~ MCMT_100Y + elev_m + lat, data = nemo_e0_5) 
summary(MC_m1)
summary(MC_m1.1)
summary(MC_m1.2)

```

DD > 5  
```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
dd5_m0 <- lm(DOY ~ DD5_100Y, data = nemo_df1)
dd5_m1 <- lm(DOY ~ DD5_100Y + elev_m, data = nemo_df1)
dd5_m1.1 <- lm(DOY ~ DD5_100Y + elev_m, data = nemo_df2)
dd5_m1.2 <- lm(DOY ~ DD5_100Y + elev_m, data = nemo_e0_5) #better
##DD5 correlated w/ MAT
#lat first included, but ns

summary(dd5_m1)
summary(dd5_m1.1)
summary(dd5_m1.2)

```

NFFD

```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
ffd_m1 <- lm(DOY ~ NFFD_100Y + elev_m + lat, data = nemo_df1) 
ffd_m1.1 <- lm(DOY ~ NFFD_100Y + elev_m + lat, data = nemo_df2)
ffd_m1.2 <- lm(DOY ~ NFFD_100Y + elev_m + lat, data = nemo_e0_5) #same as 1, but best estimate

summary(ffd_m1)
summary(ffd_m1.1)
summary(ffd_m1.2)
visreg(ffd_m1.2, "NFFD_100Y")

#NFFD might need a transformation...
```


MAP, MSP

```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
MAP_m1 <- lm(DOY ~ MAP_100Y + elev_m + long, data = nemo_df1) #Good
MAP_m1.1 <- lm(DOY ~ MAP_100Y + elev_m + long, data = nemo_df2) #Better
MAP_m1.2 <- lm(DOY ~ MAP_100Y + elev_m + long, data = nemo_e0_5)

summary(MAP_m1)
summary(MAP_m1.1)
summary(MAP_m1.2)
#Long more significant than lat, higher R2


#MSP

#
#100Y
MSP_m1 <- lm(DOY ~ MSP_100Y + elev_m, data = nemo_df1) 
MSP_m1.1 <- lm(DOY ~ MSP_100Y + elev_m, data = nemo_df2) 
MSP_m1.2 <- lm(DOY ~ MSP_100Y + elev_m, data = nemo_e0_5)
#Long does not significant here
#Models all very similar

summary(MSP_m1)
summary(MSP_m1.1)
summary(MSP_m1.2)

```


CMD, RH

```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
#RH ALL ns at the annual, 100Y scale

#CMD
#100Y
cmd_m0 <- lm(DOY ~ CMD_100Y, data = nemo_df1)
cmd_m1 <- lm(DOY ~ CMD_100Y + elev_m, data = nemo_df1)
cmd_m1.1<- lm(DOY ~ CMD_100Y + elev_m, data = nemo_df2) #slightly higher estimate
cmd_m1.2 <- lm(DOY ~ CMD_100Y + elev_m, data = nemo_e0_5) #better but not by much

summary(cmd_m1)
summary(cmd_m1.1)
summary(cmd_m1.2)

```

AHM (SHM)

```{r message = FALSE, warning = FALSE, eval = FALSE}
#AHM
#100Y
ahm_m0 <- lm(DOY ~ AHM_100Y, data = nemo_df1)
ahm_m1 <- lm(DOY ~ AHM_100Y + elev_m, data = nemo_df1)
ahm_m1.1<- lm(DOY ~ AHM_100Y + elev_m, data = nemo_df2) 
ahm_m1.2 <- lm(DOY ~ AHM_100Y + elev_m, data = nemo_e0_5) #better 
#Pretty correlated to temp, dd>5

summary(ahm_m1)
summary(ahm_m1.1)
summary(ahm_m1.2)

#SHM not as significant as AHM

```

<br>  


**Seasonal Variables**  

##### Temperature  


```{r message = FALSE, warning = FALSE, results = 'hide'}
#Tmin
Tmin_wt_lm1 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + Tmin_wt_100Y*PPT_wt_100Y, data = nemo_df1)
summary(Tmin_wt_lm1) ##significant interaction

Tmin_sp_lm1 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_100Y*PPT_sp_100Y, data = nemo_df1)
summary(Tmin_sp_lm1) #R2 = .2677 B = -2.57

Tmin_sm_lm1 <- lm(DOY ~ Tmin_sm_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tmin_sm_lm1) #R2 = .265 B = -1.64



#Tave
Tave_wt_lm1 <- lm(DOY ~ Tave_wt_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tave_wt_lm1) #ns

Tave_sp_lm1 <- lm(DOY ~ Tave_sp_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tave_sp_lm1) # R = .2724 B = -3.58  #lat ns here

Tave_sm_lm1 <- lm(DOY ~ Tave_sm_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tave_sm_lm1) #R2 = .263 B = -1.15

#Tmax
Tmax_sp_lm1 <- lm(DOY ~ Tmax_sp_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tmax_sp_lm1) #R2 = .2609 B = -1.42
```


```{r message = FALSE, warning = FALSE}
visreg(Tmin_sp_lm1, "Tmin_sp_100Y")
visreg(Tave_sp_lm1, "Tave_sp_100Y")
```

Spring Tave has a larger estimate and explains more variation in DOY than Spring Tmin (and Tmax). Winter temperature is nonsignificant on DOY.  

Interestingly, latitude is nonsignificant in the Tave model, but not in the Tmin model
<br>  

##### PPT  

```{r message = FALSE, warning = FALSE, results = 'hide'}
#PPT
PPT_wt_lm1 <- lm(DOY ~ PPT_wt_100Y + year + elev_m + lat, data = nemo_df1) #log transform PPT? here or in df?
summary(PPT_wt_lm1) #R2 = .2853 B = 12.88
visreg(PPT_wt_lm1, "PPT_wt_100Y")

PPT_sp_lm1 <- lm(DOY ~ PPT_sp_100Y + year + elev_m + lat, data = nemo_df1)
summary(PPT_sp_lm1) #R2 = .2929 B = 14.87   #lat ns #preferred model?
visreg(PPT_sp_lm1, "PPT_sp_100Y")
  
PPT_sm_lm1 <- lm(DOY ~ PPT_sm_100Y + year + elev_m + lat, data = nemo_df1, na.action = na.omit)
summary(PPT_sm_lm1) #R2 = .2668 B = 5.01
#var. in PPT much lower than for spring and witner
```


```{r message = FALSE, warning = FALSE}
PPT_sp_lm1 <- lm(DOY ~ PPT_sp_100Y + year + elev_m + lat, data = nemo_df1)
#summary(PPT_sp_lm1)  #R2 = .2929 B = 14.87 
visreg(PPT_sp_lm1, "PPT_sp_100Y")

```

Delaying effect of PPT observable in wt, sp, and sm. Model with spring PPT has highest $R^2$ and a higher parameter estimate than that of winter PPT. The estimate for the summer PPT model is quite large, but has a low R2.  

<br>  


**In Summary**  

DOY is sensitive to both MAT (advancing effect) and MAP (delaying effect) over 100 years, and precipitation may be just as stronger, or even stronger, than MAT.  

Spring temperatures (particularly Tave and also Tmin) explain more variation and have larger estimates in their relationship with DOY than winter temperatures.  

Precipitation has the strongest effect on DOY for spring, followed by winter, averages. Summer PPT had a large paramter estimate but the model R2 was much lower.  
<br>  


```{r echo = FALSE, eval = FALSE, warning = FALSE, message = FALSE}
#Susan's shared code for visualizing interactions and dw plots
plot_summs(cylindrica_model_Winter_Tmin_YoC, unguiculata_model_Winter_Tmin_YoC, colors = c("blue", "brown"), coefs = c ("Winter Tmin (Year of Collection)" = "Tmin_wt_Ann", "MAP (Year of Collection)" = "MAP_Ann",  "Winter Tmin Anomaly" = "Tmin_wt_AnnDev", "Annual Precipitation Anomaly" = "MAP_AnnDev", "Log10(PI)" = "Log10_PI"), scale = TRUE, model.names = c("cylindrica", "unguiculata"), legend.title = expression('Species’)))


johnson_neyman(cylindrica_model_Winter_Tmin_YoC, Tmin_wt_AnnDev, Tmin_wt_Ann, sig.color="blue", insig.color="red")
interact_plot(cylindrica_model_Winter_Tmin_YoC, pred=Tmin_wt_AnnDev, modx=Tmin_wt_Ann)

```

