---
title: "Exploratory Analyses 2"
author: "Devin Gamble"
date: "4/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(here)
library(ggplot2)
library(corrplot)
library(visreg)
library(jtools)
library(interactions)
```


### Objective: Explore Models of DOY  

See 'EDA1.Rmd' for exploration of variables from the georeferrenced herbarium records and 'EDA_climate.Rmd' for ClimateNA variables (mostly distributions).  

**In This Document**  
1. DOY ~ Non-climatic variables [line 100]  
2. Correlations among variables [line 125]  (Model Diagnostic code [line 190])  
3. How has climate change over time [line 240]  
4. What is the effect of Error distance on models? [?line 400?]  
5. Exploratory DOY~Climate models [???700?]  


**To-Do**  
- Update models in this script with *PI as a covariate*  
- Measure change in seasonal climate variables over time  
- Finalize analyses/script for 'Herbarium Methods' manuscript  

<br>  

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load in data & establish error distance bins

nemo_spec <- read_csv(here::here("data_cleaning", "nemo_all_2.csv")) %>% 
  mutate(error_bin = case_when(error_dist_m <= 2000 ~ "<2 km",
                               error_dist_m > 2000 & error_dist_m <= 5000 ~ "2-5 km",
                               error_dist_m > 5000 & error_dist_m <= 10000 ~ "5-10 km",
                               error_dist_m > 10000 & error_dist_m <= 15000 ~ "10-15 km", 
                               error_dist_m > 15000 ~ ">15 km")) %>% 
  select(specimen_number:error_dist_m, error_bin, everything()) %>% mutate(error_bin = factor(error_bin, levels = c( "<2 km", "2-5 km", "5-10 km", "10-15 km", ">15 km"))) #specify factor & levels for error bin
#1240 obs with error distance - added column with error distance categories
#1764 obs total

climNA_all <- read_csv(here::here("climateNA", "all_cna", "climNA_nemo_all.csv")) %>% 
  rename(year = YoC) #Also 1764 obs

#Transform Precipitation variables to be normal -- Log transforms Monthly and seasonal PPT, MAP, MSP
#log transformations do not work on PAS
climNA_all1 <- climNA_all %>% 
  mutate_at(vars(PPT01_N51:PPT12_N51, PPT_wt_N51:PPT_at_N51, MAP_N51, MSP_N51,
                 PPT01_N81:PPT12_N81, PPT_wt_N81:PPT_at_N81, MAP_N81, MSP_N81,
                 PPT01_100Y:PPT12_100Y, PPT_wt_100Y:PPT_at_100Y, MAP_100Y, MSP_100Y,
                 PPT01_L1:PPT12_L1, PPT_wt_L1:PPT_at_L1, MAP_L1, MSP_L1,
                 PPT01_Y:PPT12_Y, PPT_wt_Y:PPT_at_Y, MAP_Y, MSP_Y), log) %>% 
  na_if(y = -Inf)
#see EDA_climate for other variables to be transformed... (maybe AHM, DD if using)

#Merge herbarium records and climate data (by specimen number)
nemo_df1 <- merge(nemo_spec, climNA_all1) #1764 obs and 1250 total columns

```
Create subset of data where each observation has an error distance:  

```{r warning = FALSE, message = FALSE}

#Filter specimens to those collected after 1900
nemo_df2 <- nemo_df1 %>% 
  filter(year >= 1901) #1677 obs

nemo_all_errors <- nemo_df2 %>% 
  filter(!is.na(error_dist_m)) 
#1239 out of 1764 obs with error distance
#1166 after rm records before 1901

#0-5 km resolution
nemo_e0_5 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km" | error_bin == "2-5 km") #1081 entries

#0-4 km
nemo_e0_4 <-  nemo_all_errors %>% 
  filter(error_dist_m >= 0 & error_dist_m <= 4000) #1010 obs #Do Not include error_bin in models

#0-2 km
nemo_e2 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km") #761 obs


```

An combined dataset (`nemo_df2`) is saved within 'Climate_1.Rmd' and titled 'nemo_full_1901_2019.csv'

<br>  


## How does DoY depend on non-climatic variables?  

```{r warning = FALSE, message = FALSE}
lm1 <- lm(DOY ~ elev_m + year + long, data = nemo_df1) #all years
lm1.1 <- lm(DOY ~ elev_m + year + long, data = nemo_df2) #>1900
summary(lm1.1)
#summary(lm1.1)

visreg(lm1, xvar = "elev_m", xlab = "Elevation (m)", points = list(col = "#404040")) 
visreg(lm1, "year", xlab = "Year", points = list(col = "#404040"))
visreg(lm1, "long", xlab = "Longitude", points = list(col = "#404040"))

lm1.2 <- lm(DOY ~ elev_m + year + long + long*elev_m, data = nemo_df2) 
summary(lm1.2)
#No interactions with year
#interact_plot(lm1.2, pred = "long", modx = "elev_m")

#summ(lm1.1, vif = TRUE) #VIF for long, elev, MAP, MAT is high

```
**DOY is earlier for lower elevations, lower latitudes, later years.**
<br>  


## Variable Correlations:

Which geographical and climate variables are correlated with one another?  
(And how could these make future analyses difficult?)  

```{r warning = FALSE, message = FALSE, echo = FALSE}
#check correlated climate variables for subset of whole df - 100 year averages
library(corrplot)
nemo_corrcheck_an <- nemo_df1 %>% 
  select(MAT_100Y:MCMT_100Y, MAP_100Y:DD5_100Y, NFFD_100Y, PAS_100Y, CMD_100Y, RH_100Y, lat, long, elev_m, year)

cor_an <- cor(nemo_corrcheck_an)
corrplot(cor_an, type = "upper", method = "square", addCoef.col = "black", number.cex = .6, diag = F)

#seasonal variables

nemo_corrcheck_sz <- nemo_df1 %>% 
  select(Tmin_wt_100Y:PPT_sp_100Y, DD5_wt_100Y:DD5_at_100Y, lat, long, elev_m, year)
#Humidty, NFFD, and CMD exlcuded: CMD_sp_100Y, CMD_sm_100Y, RH_wt_100Y:RH_at_100Y, NFFD_wt_100Y:NFFD_at_100Y
#PPT_sm_100Y all NAs, not included

cor_sz <- cor(nemo_corrcheck_sz)
corrplot(cor_sz, type = "upper", method = "square", addCoef.col = "black", number.cex = .5, diag = F)


##Correlations among YoC, Normals, and anomalies...   
nemo_cor_norms <- nemo_df2 %>% 
  filter(year >= 1901, year <= 2017) %>% 
  select(MAT_100Y, MAT_N51, MAT_N81, MAP_100Y, MAP_N51, MAP_N81, Tave_sp_100Y, Tave_sp_N81, MAT_Y, MAP_Y, Tave_sp_Y)
cor_norm <- cor(nemo_cor_norms)
corrplot(cor_norm, method = "square", addCoef.col = "black", number.cex = .8, diag = F, type = "upper", na.label = "o")
#Unsurprising, all normals extremely well correlated, choice of which not too important

#Anomalies
nemo_cor4 <- nemo_df2 %>% 
  filter(year >= 1901, year <= 2017) %>% 
  select(MAT_100Y, MAP_100Y, Tmin_sp_100Y, PPT_wt_100Y, MAT_Y, MAP_Y, Tmin_sp_Y, PPT_wt_Y, MAT_A, MAP_A, Tmin_sp_A, PPT_wt_A)
cor4 <- cor(nemo_cor4)
corrplot(cor4, method = "square", addCoef.col = "black", number.cex = .6, diag = F, type = "upper", na.label = "o")


#Significance test of correlations
#cr2 <- cor.mtest(nemo_corrcheck_sz, conf.level = 0.7)
#corrplot(cor_sz, p.mat = cr2$p, insig = "pch", pch.cex = 1, method = "square", type = "upper", order = "FPC", addCoef.col = "black", number.cex = 0.5, diag = F)
```


**Correlations** to be wary of:  
[Geographic]  
- *Lat* correlated with MAT, DD5, AHM (~-.3-.4 ), elev_m (-.4), AHM (-.6), MAP (.58)  
- *Long* correlated with CMD, AHM, MWMT (.4-.5), elev (.51), MAP (-.57)  
- *Elev_m* also correlated to MAT (-.47) [but not MAP], MCMT, NFFD (~-.6), DD_0 (.68), MSP, PAS (.44)  

[Climatic]  
- *MAT* with MAP/MSP (.59), DD5 (~1), DD_0 (-.76), CMD:NFFD (.6-.7), PAS (.62)  
- *MAP* also with DD5 (.62), AHM (.9)  
- *Anomalies*: Some variables negatively correlated b/w _Y and _As  

* Seasonal temperature variables correlated with each other, with elevation  
* Some Spring Tave and Spring PPT parameters correlated  
* Seasonal PPT correlated with DD5, Spring temperatures, *not* correlated to elevation  
* Lat and Long similarly correlated to MAT [+/-0.32] and MAP [+/- 0.57], lat*long = 0.93  
* Anomalies pretty uncorrelated to other periods!  

Year had no large correlations with any variables (all < .3). Normals strongly correlated from different periods - MAT x MAP correlations consistent. 

```{r echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE}
#Diagnostics
#Checking Linear Regression Assumptions
#• Linear relationship between covariates and response (residuals vs fitted plot) - plot 1 - check
#• Homoscedasticity (constant variance) - plot 3 - check
#• Normality (of the error distribution) (residual QQ plot) - plot 2 - check
#• Absence of multicollinearity - check
#• No autocorrelation - not time series data

plot(lm1) #nemo_df1

vif(lm1) #VIF < 2 generally okay.  
sqrt(vif(lm1)) > 2


#Check outliers
plot(lm1, 4)
#Use influence threshold of 4/n = 0.0022 - seems unreasonably low
#obs 155 may need to be removed?

#Influence of points on each coefficient
dfbetasPlots(lm1, id.n = 2, id.col = "red")


#Partial resid plots
crPlots(lm1)

#Check autocorrelation
rd <- residuals(lm1)

par(mfrow = c(1,2))
plot(rd, ylab = "Residuals", main = "Residuals plot", font.main=1, cex.main = 1)
abline(h=0)
plot(rd[-length(rd)], rd[-1],
     xlab = expression(hat(epsilon)[i]),
     ylab = expression(hat(epsilon)[i+1]), main = "Autocorrelation Check", font.main=1, cex.main = 1)
lines(lowess(rd[-length(rd)],rd[-1]), col = "red", lty = 2)



#
# * Re-do these diagnostics for final models in the future
```

------  


## How have climate variables changed over time???  

Objective:  
Describe trends and rates of change over time *across California* in the following types of variables in  
- YoC Climates  
- Climate Anomalies

Split by climate group and include as covariate? (As in Natalies *Streptanthus* analyses)

#### Annual Variables  

Quantify rate of climate change in 
- Tmin wt and sp  
- PPT wt and sp  
- MAT  
_ MAP  


Note: Though analyses of DOY ~ Climate may not include covariates (to focus on the effect of cliamte variables), geography (lat/long) and MAP are included here in addition to year to control for variation in climate over space. Also include PI when available.  

**MAT**  
```{r message = FALSE, warning = FALSE, echo = FALSE}
#YoC
mat_t1 <- lm(MAT_Y ~ year, data = nemo_df2)
#summary(mat_t1)


#Control for geography (and PI) - use this model
mat_t1.1 <- lm(MAT_Y ~ year + elev_m + long, data = nemo_df2)
#summary(mat_t1.1)

mat_t1.3 <- lm(MAT_Y ~ year + MAP_Y + elev_m + long, data = nemo_df2)
#summary(mat_t1.3) #Best model


mat_t1.4 <- lm(MAT_Y ~ year + MAP_Y + elev_m + long + MAP_Y*elev_m*long, data = nemo_df2)
summary(mat_t1.4) #Better R2 - significant interactions, lowest AIC w/ 3-way interaction
visreg(mat_t1.4, xvar = "year", points = list(col = "#404040"))
#Too many interactions and this gets crazy...

#Visualize Interactions
johnson_neyman(mat_t1.4, pred = "MAP_Y", modx = "long")
johnson_neyman(mat_t1.4, pred = "elev_m", modx = "long")
johnson_neyman(mat_t1.4, pred = "MAP_Y", modx = "elev_m") 
interact_plot(mat_t1.4, pred = "MAP_Y", modx = "elev_m")
interact_plot(mat_t1.4, pred = "elev_m", modx = "long", mod2 = "MAP_Y")

#Compare model estimates
#plot_summs(mat_t1, mat_t1.1, mat_t1.3, mat_t1.4, scale = TRUE)

#Change over time: MAT~Year beta = 0.011 [mat_t1.4]
print("MAT_Y warming (°C) over 120 years")
.0118*120


```

 
Interactions:  
- MAT_Y is greater at more inland longitudes, and at lower elevations  
- MAT_Y declines faster going up in elevation with more inland longitudes. This effect is strengthened by greater  MAP_Y (below 1000 m) in the west and weakened by greater MAP_Y in the east 
- Interactions with long are less significant than with elev_m and MAP  



**MAP**  
```{r warning = FALSE, message = FALSE, echo = FALSE}
#YoC
map_t1 <- lm(MAP_Y ~ year + elev_m + long, data = nemo_df2)
#summary(map_t1)

map_t1.1 <- lm(MAP_Y ~ year + elev_m + long + MAT_Y, data = nemo_df2)
summary(map_t1.1)
visreg(map_t1.1, xvar = "year", line = list(alpha = 0), points = list(col = "#404040"),  band = FALSE) #Not sure how to hide line without gg=TRUE...

```
No significant change in average MAP over years of collection  


**Frost Free Days**  
```{r warning = FALSE, message = FALSE}

ffd_t1 <- lm(NFFD_Y ~ year + elev_m + long + MAP_Y, data = nemo_df2)
summary(ffd_t1)

ffd_t1.1 <- lm(bFFP_Y ~ year + elev_m + long + MAP_Y, data = nemo_df2)
summary(ffd_t1.1)

visreg(ffd_t1.1, xvar = "year", points = list(col = "#404040"), gg = TRUE) + 
  theme_classic()


```



#### Seasonal Variables  
Note: See Climate_1.Rmd for selection of variables and seasons  




#### Monthly (& custom windows)  






Consider differences across geographic climate regions?  

### Change in Anomalies over time  

**MAT**
```{r message = FALSE, warning = FALSE, echo = FALSE}
#MAT Anomalies
mat_t2 <- lm(MAT_A ~ year + elev_m*long*MAT_Y, data = nemo_df2) #No effect of MAP_A, no interaction
summary(mat_t2)

visreg(mat_t2, xvar = "year", points = list(col = "#404040"), gg = TRUE, line = list(alpha = 0), band = FALSE) + 
  geom_smooth(method = "gam", col = "red") + 
  theme_bw()
#Maybe a different type of model would be more appropriate (not lm)


plot(mat_t2)

#MAT_A is normal, but the residuals are not - autocorrelation?
durbinWatsonTest(mat_t2)
#Looks like residuals are correlated.... 
#Do we need to create better models if we're just following a trend? No, but to quantify the rate of change (Slope) we would.

print("MAT anomalies (°C) increase over 120 years")
.007*120 #Not sure this makes sense since the relationship is not linear...
```
Similar interactions explain variation in MAT_A...   


**MAP**  
```{r warning = FALSE, message = FALSE, echo = FALSE}
#Anomalies
map_t2 <- lm(MAP_A ~ year + elev_m + long + MAP_Y + MAT_Y, data = nemo_df2) #YoC & anom correlated (r = .45), include?
summary(map_t2)

visreg(map_t2, xvar = "year", points = list(col = "#404040"), gg = TRUE, line = list(alpha = 0), band = FALSE) + 
  theme_bw()

```

Slightly significant effect of year becomes ns when controlling for YoC MAP/MAT
<br>  


------  

## Effect of Error Distance on DOY ~ Climate models  

The following analyses aim to measure the effect of different error distance on model outputs, specifically,  

- $R^2$ values  
- Parameter estimates and  
- significance of climate variables in their effect on DOY  

For 100 year averages for MAT, MAP, Tmin_sp, Tave_sp, PPT_sp, PPT_wt

Including error distance (or error bin) as a covariate shows no model improvement. Though the smallest bin, 0-2 km error, has a significant effect in the model, none of the parameter estimates of the bins are significantly different from one another.  

<br>  


```{r message = FALSE, warning = FALSE, echo = FALSE, results = 'hide'}
#Effect of Error Distance

##
#Single Temp
##
MAT_e <- lm(DOY ~ MAT_100Y, data = nemo_df2)

er_mat0 <- lm(DOY ~ MAT_100Y, data = nemo_all_errors)
er_mat1 <- lm(DOY ~ MAT_100Y, data = nemo_e0_5)
er_mat2 <- lm(DOY ~ MAT_100Y, data = nemo_e2)

plot_summs(MAT_e, er_mat0, er_mat1, er_mat2, model.names = c("Original", "all errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
#scale = TRUE refits model to mean-center & standardize the predictors but not the response. Use 'center = TRUE' to only mean center variables
summary(MAT_e)
summary(er_mat0)$r.squared
summary(er_mat1)$r.squared
summary(er_mat2)$r.squared


Tsp_e <- lm(DOY ~ Tmin_sp_100Y, data = nemo_df2)

er_tsp0 <- lm(DOY ~ Tmin_sp_100Y, data = nemo_all_errors)
er_tsp1 <- lm(DOY ~ Tmin_sp_100Y, data = nemo_e0_5)
er_tsp2 <- lm(DOY ~ Tmin_sp_100Y, data = nemo_e2)

plot_summs(Tsp_e, er_tsp0, er_tsp1, er_tsp2, model.names = c("Original", "all errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
#scale = TRUE refits model to mean-center & standardize the predictors but not the response. Use 'center = TRUE' to only mean center variables
summary(Tsp_e)
summary(er_tsp0)$r.squared
summary(er_tsp1)$r.squared
summary(er_tsp2)$r.squared


#Single PPT

MAP_e <- lm(DOY ~ MAP_100Y, data = nemo_df2)

er_map0 <- lm(DOY ~ MAP_100Y, data = nemo_all_errors)
er_map1 <- lm(DOY ~ MAP_100Y, data = nemo_e0_5)
er_map2 <- lm(DOY ~ MAP_100Y, data = nemo_e2)

plot_summs(MAP_e, er_map0, er_map1, er_map2, model.names = c("Original", "all errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
#scale = TRUE refits model to mean-center & standardize the predictors but not the response. Use 'center = TRUE' to only mean center variables
summary(MAP_e)
summary(er_map0)$r.squared
summary(er_map1)$r.squared
summary(er_map2)$r.squared


Psp_e <- lm(DOY ~ PPT_sp_100Y, data = nemo_df2)

er_psp0 <- lm(DOY ~ PPT_sp_100Y, data = nemo_all_errors)
er_psp1 <- lm(DOY ~ PPT_sp_100Y, data = nemo_e0_5)
er_psp2 <- lm(DOY ~ PPT_sp_100Y, data = nemo_e2)

plot_summs(Psp_e, er_psp0, er_psp1, er_psp2, model.names = c("Original", "all errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
#scale = TRUE refits model to mean-center & standardize the predictors but not the response. Use 'center = TRUE' to only mean center variables
summary(Psp_e)
summary(er_psp0)$r.squared
summary(er_psp1)$r.squared
summary(er_psp2)$r.squared

```


```{r message = FALSE, warning = FALSE, echo = FALSE}
#Effect of Error Distance

##
#MAT & MAP
##
an_lm_e <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_df2)

er_an0 <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_all_errors)
er_an1 <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_e0_5)
er_an2 <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_e2)

plot_summs(an_lm_e, er_an0, er_an1, er_an2, model.names = c("Original", "all errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
#scale = TRUE refits model to mean-center & standardize the predictors but not the response. Use 'center = TRUE' to only mean center variables
summary(an_lm_e)
summary(er_an0)$r.squared
summary(er_an1)$r.squared
summary(er_an2)$r.squared

#Including other covariates
an_lm_ec <- lm(DOY ~ MAT_100Y + MAP_100Y+ elev_m + long + year, data = nemo_df2)

erc_an0 <- lm(DOY ~ MAT_100Y + MAP_100Y+ elev_m + long + year, data = nemo_all_errors)
erc_an1 <- lm(DOY ~ MAT_100Y + MAP_100Y+ elev_m + long + year, data = nemo_e0_5)
erc_an2 <- lm(DOY ~ MAT_100Y + MAP_100Y+ elev_m + long + year, data = nemo_e2)

plot_summs(an_lm_ec, erc_an0, erc_an1, erc_an2, model.names = c("Original", "All errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
summary(an_lm_ec)
summary(erc_an0)$r.squared
summary(erc_an1)$r.squared
summary(erc_an2)$r.squared


##
#Winter
##
#Without covariates
sz_wt_lm_e <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y, data = nemo_df2)

er_wt0 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y, data = nemo_all_errors)
er_wt1 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y, data = nemo_e0_5)
er_wt2 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y, data = nemo_e2)

plot_summs(sz_wt_lm_e, er_wt0, er_wt1, er_wt2, model.names = c("Original", "All errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
summary(sz_wt_lm_e)
summary(er_wt0)$r.squared
summary(er_wt1)$r.squared
summary(er_wt2)$r.squared

#With Covariates
sz_wt_lm_ec <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + elev_m + long + year, data = nemo_df2)

erc_wt0 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + elev_m + long + year, data = nemo_all_errors)
erc_wt1 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + elev_m + long + year, data = nemo_e0_5)
erc_wt2 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + elev_m + long + year, data = nemo_e2)

plot_summs(sz_wt_lm_ec, erc_wt0, erc_wt1, erc_wt2, model.names = c("OG", "all errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
summary(sz_wt_lm_ec)
summary(erc_wt0)$r.squared
summary(erc_wt1)$r.squared
summary(erc_wt2)$r.squared


##
#Spring
##
#Without covariates
sz_sp_lm_e <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_100Y*PPT_sp_100Y, data = nemo_df2)

er_sp0 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_100Y*PPT_sp_100Y, data = nemo_all_errors)
er_sp1 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_100Y*PPT_sp_100Y, data = nemo_e0_5)
er_sp2 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_100Y*PPT_sp_100Y, data = nemo_e2)

plot_summs(sz_sp_lm_e, er_sp0, er_sp1, er_sp2, model.names = c("Original", "All errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
summary(sz_sp_lm_e)
summary(er_sp0)$r.squared
summary(er_sp1)$r.squared
summary(er_sp2)$r.squared

#With Covariates - interaction ns and removed
sz_sp_lm_ec <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + elev_m + long + year, data = nemo_df2)

erc_sp0 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + elev_m + long + year, data = nemo_all_errors)
erc_sp1 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + elev_m + long + year, data = nemo_e0_5)
erc_sp2 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + elev_m + long + year, data = nemo_e2)

plot_summs(sz_sp_lm_ec, erc_sp0, erc_sp1, erc_sp2, model.names = c("Original", "All errors", "0-5 km", "0-2 km"), scale = TRUE) + theme_bw()
summary(sz_sp_lm_ec)
summary(erc_sp0)$r.squared
summary(erc_sp1)$r.squared
summary(erc_sp2)$r.squared

```


##### In Summary  


Filtering out larger error_bins led to no real improvements in model $R^2$s, though of the *subsets* the 0-5 group often had better $R^2$s. Based on confidence intervals, there are no significant differences in parameter estiamtes between data including all observations and data including less uncertain coordinate estimates.

Using data from more precise error distances led to **increases in parameter estimate varaition (SE)**, especially for 0-2 km.  

Lack of improvements may be due to loss of meaningful variation from records with greater uncertainty. Also, looking only at records with any error distance, there is a reduction in $R^2$ values.


[From old models]  
> Including error bin as a covariate (for models with 2+ bins) slightly increases $R^2$ but not parameter estimate (by much). For this reason, and the fact that uncertainty should have no direct effect on DOY, I've removed it. 
The significant effect of 2-5 km bin for error distance on DOY - slightly earlier - is likely due to chance.  

> Filtering out records with larger error distances generally improves models, but improvements seem greatest for `MAT`, `Tmin` and `Tave`. `MAP`, `PPT_wt`, and `PPT_sp` models had larger parameter estimates for 0-2 km errors but Filtering finely to records with 0-2 km error led to larger parameter estimates, but at the cost of reduced R2 values and much larger SE. This could be due to a loss of variation and represents a trade-off to consider with future models. Oddly, a couple models with errors from 0-4 km were worse (for MAT, Tave_sp) than 0-2 or 0-5 error models.  Model improvements were persistent when the error_bin covariate was removed from models, though R2 values were very slightly reduced.  




In future models,  
- Consider treating error distance as a random effect?
- Consider comparing all data with those with *errors from 0-5 km* 

<br>  


### Investigating the effect of manually georeferenced specimens on the relationship b/w DOY and climate variables  

```{r message = FALSE, warning = FALSE, echo = FALSE}
#Records we georeferenced:
nemo_geor <- nemo_df1 %>% 
  filter(!is.na(georef_by)) #458 obs

nemo_ngeo <- nemo_df1 %>% 
  filter(is.na(georef_by)) #records that we did not georeference

```

MAT & MAP

```{r message = FALSE, warning = FALSE}
#summary(an_lm_e) #nemo_df2
#summary(an_lm_ec) #with other covariates

an_lm_g1<- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_geor)
an_lm_g1.1<- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m + long + year, data = nemo_geor)
summary(an_lm_g1) #R2 = 0.2026 B = -2.38
summary(an_lm_g1.1)


plot_summs(an_lm_e, an_lm_g1, model.names = c("All data", "Geo"), scale = TRUE)

plot_summs(an_lm_ec, an_lm_g1.1, model.names = c("All data", "Geo"), scale = TRUE)

```

From these averages it's clear that subsetting by specimens we georeferenced increases variation in the parameter estiamte, as did subsetting by smaller error distances earlier.

What about data we did not georeference?  

```{r warning = FALSE, message = FALSE, echo = FALSE}
#summary(an_lm_e) #nemo_df2
#summary(an_lm_ec) #with covariates
an_lm_g1.2<- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_ngeo)
an_lm_g1.3<- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m + long + year, data = nemo_ngeo)
summary(an_lm_g1.2)
summary(an_lm_g1.3)

plot_summs(an_lm_e, an_lm_g1, an_lm_g1.2, model.names = c("All data", "Geo", "Herb"), scale = TRUE)

plot_summs(an_lm_ec, an_lm_g1.1, an_lm_g1.3, model.names = c("All data", "Geo", "Herb"), scale = TRUE)

```

Ours still seem a little more variables (and NS in a couple cases), but are quite similar to herbarium-georeferenced data.


------  


<br>  

## EXPLORATORY ANALYSES - See 'Climate_1.Rmd' for more finalized analyses  

### How does DOY depend on climate?  



Note: The following parameter estimates of Precipitation variables on DOY are log-transformed and need to be back-transformed to be adequately interpreted.  
Note2: It is not necessary to include covariates for elev_m, lat/long, year if we're mainly interested in the effect of climate variables on DOY...  

<br>  

#### Annual Climate  

```{r message = FALSE, warning = FALSE, results = 'hide'}
MAT_lm1 <- lm(DOY ~ MAT_100Y + year + elev_m + lat, data = nemo_df1)
MAT_lm1.1 <- lm(DOY ~ MAT_100Y, data = nemo_df1)
summary(MAT_lm1) #R2 = .2646, MAT B = -2.53
summary(MAT_lm1.1)

MAP_lm1 <- lm(DOY ~ MAP_100Y + year + elev_m + lat, data = nemo_df1)
MAP_lm1.1 <- lm(DOY ~ MAP_100Y, data = nemo_df1)
summary(MAP_lm1)#R2 = .2894, MAP B = 14.6
summary(MAP_lm1.1)


ann_lm1 <- lm(DOY ~ MAT_100Y + MAP_100Y + long + elev_m + year, data = nemo_df2)
ann_lm1.1 <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_df2)
summary(ann_lm1) #R2 = .2989 #MAT estimate is much lower than in first lm (MAP slightly lower)
summary(ann_lm1.1)
#MAT NS if nemo_df1 is used
#MAP and MAT somewhat correlated (r = -.58) but no interaction present

ann_lm1.2 <- lm(DOY ~ MAT_Y + MAP_Y, data = nemo_df2)
summary(ann_lm1.2)

```


```{r message = FALSE, warning = FALSE}

summary(ann_lm1.1)
visreg(ann_lm1.1, "MAT_100Y", xlab = "MAT 100Y")
visreg(ann_lm1.1, "MAP_100Y", xlab = "MAP 100Y")

summary(ann_lm1.2)
visreg(ann_lm1.2, "MAT_Y", xlab = "MAT Y")
visreg(ann_lm1.2, "MAP_Y", xlab = "MAP Y")

#Analyses w normals not shown
#R2 highest (and coeffs most -) for 100Y avg climate - use it for long term avg.  
```

```{r message = FALSE, warning = FALSE, echo = FALSE}
##
#NICE PLOT of DOY ~ MAT
##
MAT_lm1 <- lm(DOY ~ MAT_100Y , data = nemo_df1)
summary(MAT_lm1)

ggplot(aes(x = MAT_100Y, y = DOY), data = nemo_df1) +
  geom_point(aes(color = MAP_100Y), alpha = .8) +
  labs(color = "log(MAP)") +
  geom_smooth(method = "lm", color = "#454545") +
  scale_color_gradientn(colors = c("#ade2ff", "#001775"), values = c(0, 1)) +
  xlab("MAT (°C)") +
  ylab("DOY") +
  theme_classic()
#ggsave(here::here("analyses", "DOY-MAT_MAP_point.png"), height = 5, width = 8) #saved version PPT not transformed
  
#Opposite

ggplot(aes(x = MAP_100Y, y = DOY), data = nemo_df1) +
  geom_point(aes(color = MAT_100Y), alpha = .8) +
  labs(color = "MAT (°C)") +
  geom_smooth(method = "lm", color = "#454545") +
  scale_color_gradientn(colors = c("#fdff91", "#e30000"), values = c(0, 1)) +
  xlab("log(MAP)") +
  ylab("DOY") +
  theme_classic()


```



MAT predicts advanced DOY, MAP predicts delayed DOY.

Elevation and MAP/MAT appear to have the most significant effects on DOY.  

<br>  


MAT 
```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
MAT_m0 <- lm(DOY ~ MAT_100Y, data = nemo_df1)
MAT_m1 <- lm(DOY ~ MAT_100Y + elev_m, data = nemo_df1)
MAT_m1.1 <- lm(DOY ~ MAT_100Y + elev_m, data = nemo_df2)
MAT_m1.2 <- lm(DOY ~ MAT_100Y + elev_m, data = nemo_e0_5) #Best
summary(MAT_m1)
summary(MAT_m1.1)
summary(MAT_m1.2) #or summ(MAT_m1.2, vifs =  TRUE)
#0-5 km model best, df1 and df2 similar

#Anomalies...

#YoC
MAT_m2.2 <- lm(DOY ~ MAT_Y + elev_m, data = nemo_e0_5)
summary(MAT_m2.2)

#plot_summs(MAT_m1, MAT_m1.1, MAT_m1.2, MAT_m2.2, scale = TRUE, coefs = c("MAT (1901-2000)" = "MAT_100Y", "MAT (YoC)" = "MAT_Y", "Elevation (m)" = "elev_m"), model.names = c("All records", "Records 1901-2019", "Errors 0-5 km", "YoC 0-5 km"), legend.title = expression('Model')) #Same pattern with YoC climate

```


MWMT & MCMT  

```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
MW_m0 <- lm(DOY ~ MWMT_100Y, data = nemo_df1)
MW_m1 <- lm(DOY ~ MWMT_100Y + elev_m + lat, data = nemo_df1)
MW_m1.1 <- lm(DOY ~ MWMT_100Y + elev_m + lat, data = nemo_df2)
MW_m1.2 <- lm(DOY ~ MWMT_100Y + elev_m + lat, data = nemo_e0_5) #Better
summary(MW_m1)
summary(MW_m1.1)
summary(MW_m1.2)

MC_m0 <- lm(DOY ~ MCMT_100Y, data = nemo_df1)
MC_m1 <- lm(DOY ~ MCMT_100Y + elev_m + lat, data = nemo_df1) #barely better, all similar
MC_m1.1 <- lm(DOY ~ MCMT_100Y + elev_m + lat, data = nemo_df2)
MC_m1.2 <- lm(DOY ~ MCMT_100Y + elev_m + lat, data = nemo_e0_5) 
summary(MC_m1)
summary(MC_m1.1)
summary(MC_m1.2)

```

DD > 5  
```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
dd5_m0 <- lm(DOY ~ DD5_100Y, data = nemo_df1)
dd5_m1 <- lm(DOY ~ DD5_100Y + elev_m, data = nemo_df1)
dd5_m1.1 <- lm(DOY ~ DD5_100Y + elev_m, data = nemo_df2)
dd5_m1.2 <- lm(DOY ~ DD5_100Y + elev_m, data = nemo_e0_5) #better
##DD5 correlated w/ MAT
#lat first included, but ns

summary(dd5_m1)
summary(dd5_m1.1)
summary(dd5_m1.2)

```

NFFD

```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
ffd_m1 <- lm(DOY ~ NFFD_100Y + elev_m + lat, data = nemo_df1) 
ffd_m1.1 <- lm(DOY ~ NFFD_100Y + elev_m + lat, data = nemo_df2)
ffd_m1.2 <- lm(DOY ~ NFFD_100Y + elev_m + lat, data = nemo_e0_5) #same as 1, but best estimate

summary(ffd_m1)
summary(ffd_m1.1)
summary(ffd_m1.2)
visreg(ffd_m1.2, "NFFD_100Y")

#NFFD might need a transformation...
```


MAP, MSP

```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
MAP_m1 <- lm(DOY ~ MAP_100Y + elev_m + long, data = nemo_df1) #Good
MAP_m1.1 <- lm(DOY ~ MAP_100Y + elev_m + long, data = nemo_df2) #Better
MAP_m1.2 <- lm(DOY ~ MAP_100Y + elev_m + long, data = nemo_e0_5)

summary(MAP_m1)
summary(MAP_m1.1)
summary(MAP_m1.2)
#Long more significant than lat, higher R2


#MSP

#
#100Y
MSP_m1 <- lm(DOY ~ MSP_100Y + elev_m, data = nemo_df1) 
MSP_m1.1 <- lm(DOY ~ MSP_100Y + elev_m, data = nemo_df2) 
MSP_m1.2 <- lm(DOY ~ MSP_100Y + elev_m, data = nemo_e0_5)
#Long does not significant here
#Models all very similar

summary(MSP_m1)
summary(MSP_m1.1)
summary(MSP_m1.2)

```


CMD, RH

```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y
#RH ALL ns at the annual, 100Y scale

#CMD
#100Y
cmd_m0 <- lm(DOY ~ CMD_100Y, data = nemo_df1)
cmd_m1 <- lm(DOY ~ CMD_100Y + elev_m, data = nemo_df1)
cmd_m1.1<- lm(DOY ~ CMD_100Y + elev_m, data = nemo_df2) #slightly higher estimate
cmd_m1.2 <- lm(DOY ~ CMD_100Y + elev_m, data = nemo_e0_5) #better but not by much

summary(cmd_m1)
summary(cmd_m1.1)
summary(cmd_m1.2)

```

AHM (SHM)

```{r message = FALSE, warning = FALSE, eval = FALSE}
#AHM
#100Y
ahm_m0 <- lm(DOY ~ AHM_100Y, data = nemo_df1)
ahm_m1 <- lm(DOY ~ AHM_100Y + elev_m, data = nemo_df1)
ahm_m1.1<- lm(DOY ~ AHM_100Y + elev_m, data = nemo_df2) 
ahm_m1.2 <- lm(DOY ~ AHM_100Y + elev_m, data = nemo_e0_5) #better 
#Pretty correlated to temp, dd>5

summary(ahm_m1)
summary(ahm_m1.1)
summary(ahm_m1.2)

#SHM not as significant as AHM

```

<br>  


**Seasonal Variables**  

##### Temperature  


```{r message = FALSE, warning = FALSE, results = 'hide'}
#Tmin
Tmin_wt_lm1 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + Tmin_wt_100Y*PPT_wt_100Y, data = nemo_df1)
summary(Tmin_wt_lm1) ##significant interaction

Tmin_sp_lm1 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_100Y*PPT_sp_100Y, data = nemo_df1)
summary(Tmin_sp_lm1) #R2 = .2677 B = -2.57

Tmin_sm_lm1 <- lm(DOY ~ Tmin_sm_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tmin_sm_lm1) #R2 = .265 B = -1.64



#Tave
Tave_wt_lm1 <- lm(DOY ~ Tave_wt_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tave_wt_lm1) #ns

Tave_sp_lm1 <- lm(DOY ~ Tave_sp_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tave_sp_lm1) # R = .2724 B = -3.58  #lat ns here

Tave_sm_lm1 <- lm(DOY ~ Tave_sm_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tave_sm_lm1) #R2 = .263 B = -1.15

#Tmax
Tmax_sp_lm1 <- lm(DOY ~ Tmax_sp_100Y + year + elev_m + lat, data = nemo_df1)
summary(Tmax_sp_lm1) #R2 = .2609 B = -1.42
```


```{r message = FALSE, warning = FALSE}
visreg(Tmin_sp_lm1, "Tmin_sp_100Y")
visreg(Tave_sp_lm1, "Tave_sp_100Y")
```

Spring Tave has a larger estimate and explains more variation in DOY than Spring Tmin (and Tmax). Winter temperature is nonsignificant on DOY.  

Interestingly, latitude is nonsignificant in the Tave model, but not in the Tmin model
<br>  

##### PPT  

```{r message = FALSE, warning = FALSE, results = 'hide'}
#PPT
PPT_wt_lm1 <- lm(DOY ~ PPT_wt_100Y + year + elev_m + lat, data = nemo_df1) #log transform PPT? here or in df?
summary(PPT_wt_lm1) #R2 = .2853 B = 12.88
visreg(PPT_wt_lm1, "PPT_wt_100Y")

PPT_sp_lm1 <- lm(DOY ~ PPT_sp_100Y + year + elev_m + lat, data = nemo_df1)
summary(PPT_sp_lm1) #R2 = .2929 B = 14.87   #lat ns #preferred model?
visreg(PPT_sp_lm1, "PPT_sp_100Y")
  
PPT_sm_lm1 <- lm(DOY ~ PPT_sm_100Y + year + elev_m + lat, data = nemo_df1, na.action = na.omit)
summary(PPT_sm_lm1) #R2 = .2668 B = 5.01
#var. in PPT much lower than for spring and witner
```


```{r message = FALSE, warning = FALSE}
PPT_sp_lm1 <- lm(DOY ~ PPT_sp_100Y + year + elev_m + lat, data = nemo_df1)
#summary(PPT_sp_lm1)  #R2 = .2929 B = 14.87 
visreg(PPT_sp_lm1, "PPT_sp_100Y")

```

Delaying effect of PPT observable in wt, sp, and sm. Model with spring PPT has highest $R^2$ and a higher parameter estimate than that of winter PPT. The estimate for the summer PPT model is quite large, but has a low R2.  

<br>  


**In Summary**  

DOY is sensitive to both MAT (advancing effect) and MAP (delaying effect) over 100 years, and precipitation may be just as stronger, or even stronger, than MAT.  

Spring temperatures (particularly Tave and also Tmin) explain more variation and have larger estimates in their relationship with DOY than winter temperatures.  

Precipitation has the strongest effect on DOY for spring, followed by winter, averages. Summer PPT had a large paramter estimate but the model R2 was much lower.  
<br>  


```{r echo = FALSE, eval = FALSE, warning = FALSE, message = FALSE}
#Susan's shared code for visualizing interactions and dw plots
plot_summs(cylindrica_model_Winter_Tmin_YoC, unguiculata_model_Winter_Tmin_YoC, colors = c("blue", "brown"), coefs = c ("Winter Tmin (Year of Collection)" = "Tmin_wt_Ann", "MAP (Year of Collection)" = "MAP_Ann",  "Winter Tmin Anomaly" = "Tmin_wt_AnnDev", "Annual Precipitation Anomaly" = "MAP_AnnDev", "Log10(PI)" = "Log10_PI"), scale = TRUE, model.names = c("cylindrica", "unguiculata"), legend.title = expression('Species’)))


johnson_neyman(cylindrica_model_Winter_Tmin_YoC, Tmin_wt_AnnDev, Tmin_wt_Ann, sig.color="blue", insig.color="red")
interact_plot(cylindrica_model_Winter_Tmin_YoC, pred=Tmin_wt_AnnDev, modx=Tmin_wt_Ann)

```

