---
title: "Climate EDA"
author: "Devin Gamble"
date: "4/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load Packages
library(tidyverse)
library(here)
library(ggplot2)
library(corrplot)

```



#Exploratory Data Analysis - ClimateNA Data  
###  See 'EDA1.Rmd' for EDA on herbarium data alone (and CA Maps of some climate variables)


```{r message = FALSE, warning = FALSE, echo = FALSE}
nemo_all1 <- read_csv(here::here("data_cleaning", "nemo_all_2.csv")) %>% 
  mutate(error_bin = case_when(error_dist_m <= 2000 ~ "<2 km",
                               error_dist_m > 2000 & error_dist_m <= 5000 ~ "2-5 km",
                               error_dist_m > 5000 & error_dist_m <= 10000 ~ "5-10 km",
                               error_dist_m > 10000 & error_dist_m <= 15000 ~ "10-15 km", 
                               error_dist_m > 15000 ~ ">15 km")) %>% 
  select(specimen_number:error_dist_m, error_bin, everything()) %>% mutate(error_bin = factor(error_bin, levels = c( "<2 km", "2-5 km", "5-10 km", "10-15 km", ">15 km"))) #specify factor & levels for error bin

#1240 obs with error distance - added column with error distance categories


```



Import ClimateNA data:  
```{r warning = FALSE, message = FALSE, echo = FALSE}
climNA_all <- read_csv(here::here("climateNA", "all_cna", "climNA_nemo_all.csv")) %>% 
  rename(year = YoC)

```



# Climate Normals/ Long-term Averages  

## Annual Variables

#### 1951 - 1980  

```{r message = FALSE, warning = FALSE, echo = FALSE}
#Temperature 

ggplot(data = climNA_all, aes(x = MAT_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(MAT_N51)), col = "red", size = 1.5) + #mean
  geom_text(aes(x = mean(MAT_N51), y = 0, label = round(mean(MAT_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  geom_vline(aes(xintercept = median(MAT_N51)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,250)) +
  ylab("Count") + 
  xlab("MAT 1951 - 1980")


ggplot(data = climNA_all, aes(x = MWMT_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(MWMT_N51)), col = "red", size = 1.5) + #mean
  geom_text(aes(x = mean(MWMT_N51), y = 0, label = round(mean(MWMT_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  geom_vline(aes(xintercept = median(MWMT_N51)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,350)) +
  ylab("Count") + 
  xlab("MWMT 1951 - 1980")


ggplot(data = climNA_all, aes(x = MCMT_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(MCMT_N51)), col = "red", size = 1.5) + #mean
  geom_text(aes(x = mean(MCMT_N51), y = 0, label = round(mean(MCMT_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  geom_vline(aes(xintercept = median(MCMT_N51)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,250)) +
  ylab("Count") + 
  xlab("MCMT 1951 - 1980")
```

Annual Temp distributions look okay.  


Precipitation
```{r message = FALSE, warning = FALSE, echo = FALSE}
ggplot(data = climNA_all, aes(x = MAP_N51)) +
  geom_histogram(fill = "blue", color = "black", binwidth = 100) +
  geom_vline(aes(xintercept = mean(MAP_N51)), col = "red", size = 1.5) + #mean
    geom_text(aes(x = mean(MAP_N51), y = 0, label = round(mean(MAP_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  geom_vline(aes(xintercept = median(MAP_N51)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,350)) +
  ylab("Count") + 
  xlab("MAP 1951 - 1980")

ggplot(data = climNA_all, aes(x = MSP_N51)) +
  geom_histogram(fill = "blue", color = "black", binwidth = 10) +
  geom_vline(aes(xintercept = mean(MSP_N51)), col = "red", size = 1.5) + #mean
    geom_text(aes(x = mean(MSP_N51), y = 0, label = round(mean(MSP_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  geom_vline(aes(xintercept = median(MSP_N51)), col = "orange", size = 1) + #median
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,550)) +
  ylab("Count") + 
  xlab("MSP 1951 - 1980")

ggplot(data = climNA_all, aes(x = PAS_N51)) +
  geom_histogram(fill = "blue", color = "black", binwidth = 5) +
  geom_vline(aes(xintercept = mean(PAS_N51)), col = "red", size = 1) + #mean
    geom_text(aes(x = mean(PAS_N51), y = 0, label = round(mean(PAS_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,800)) +
  ylab("Count") + 
  xlab("PAS 1951 - 1980")
```



Looks like most precipitation parameters will need some kind of transformation - log. There also look to be a lot of outliers.  

**Log Transformed** Precipitation:  

```{r warning = FALSE, echo = FALSE, message = FALSE}
#Log transformations for precipitation
ggplot(data = climNA_all, aes(x = log(MAP_N51))) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  ylab("Count") + 
  xlab("Log(MAP) 1951 - 1980")

ggplot(data = climNA_all, aes(x = log(MSP_N51))) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  ylab("Count") + 
  xlab("Log(MSP) 1951 - 1980")

ggplot(data = climNA_all, aes(x = log(PAS_N51))) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  ylab("Count") + 
  xlab("Log(PAS) 1951 - 1980")

#These appear to create more normal distributions (except PAS) - transform variables in `EDA2` where new csv is saved.

#Back transform when reporting results
```




```{r message = FALSE, warning = FALSE, echo = FALSE}
#Heat moisture Indeces - measured as Temp over PPT fraction (standardized)

ggplot(data = climNA_all, aes(x = AHM_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(AHM_N51)), col = "red", size = 1) + #mean
  geom_text(aes(x = mean(AHM_N51), y = 0, label = round(mean(AHM_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,350)) +
  ylab("Count") + 
  xlab("AHM 1951 - 1980")
#Slightly right skewed

ggplot(data = climNA_all, aes(x = SHM_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(SHM_N51)), col = "red", size = 1) + #mean
  geom_text(aes(x = mean(SHM_N51), y = 0, label = round(mean(SHM_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,250)) +
  ylab("Count") + 
  xlab("SHM 1951 - 1980")

#Also right skewed


#Degree days

ggplot(data = climNA_all, aes(x = DD_0_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(DD_0_N51)), col = "red", size = 1) + #mean
  geom_text(aes(x = mean(DD_0_N51), y = 0, label = round(mean(DD_0_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,400)) +
  ylab("Count") + 
  xlab("DD < 0 1951 - 1980")


ggplot(data = climNA_all, aes(x = DD5_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(DD5_N51)), col = "red", size = 1) + #mean
  geom_text(aes(x = mean(DD5_N51), y = 0, label = round(mean(DD5_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  ylab("Count") + 
  xlab("DD > 5 1951 - 1980")


ggplot(data = climNA_all, aes(x = CMD_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  ylab("Count") + 
  xlab("CMD 1951 - 1980")

```


I don't understand why DD > 5 has values over 365 days (and over 31 days for monthly variables), in all climateNA files?? They are the cumulative degrees in a period (month, season, year) for days where temps are under 0/over 5.


```{r message = FALSE, warning = FALSE, echo = FALSE}

ggplot(data = climNA_all, aes(x = NFFD_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(NFFD_N51)), col = "red", size = 1) + #mean
  geom_text(aes(x = mean(NFFD_N51), y = 0, label = round(mean(NFFD_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,260)) +
  ylab("Count") + 
  xlab("NFFD 1951 - 1980")

#Left skewed


ggplot(data = climNA_all, aes(x = NFFD_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(NFFD_N51)), col = "red", size = 1) + #mean
  geom_text(aes(x = mean(NFFD_N51), y = 0, label = round(mean(NFFD_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,260)) +
  ylab("Count") + 
  xlab("NFFD 1951 - 1980")

  
ggplot(data = climNA_all, aes(x = CMD_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(CMD_N51)), col = "red", size = 1) + #mean
  geom_text(aes(x = mean(CMD_N51), y = 0, label = round(mean(CMD_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  ylab("Count") + 
  xlab("CMD 1951 - 1980")


ggplot(data = climNA_all, aes(x = RH_N51)) +
  geom_histogram(fill = "blue", color = "black") +
  geom_vline(aes(xintercept = mean(RH_N51)), col = "red", size = 1) + #mean
  geom_text(aes(x = mean(RH_N51), y = 0, label = round(mean(RH_N51), 4)),  size = 4, vjust = -30, hjust = -1) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,300)) +
  ylab("Count") + 
  xlab("RH 1951 - 1980")


```


It seems likely that a lot of the skew in the above variables may be associated with the skew in elevation - fewer specimens collected at high elevations, but tail out into extremes.  
<br>  

##### Climate Anomalies  

```{r message = FALSE, warning = FALSE}

ggplot(data = climNA_all, aes(x = MAT_A)) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  ylab("Count") + 
  xlab("MAT Anomalies")

#Does PPT_A need to be log transformed or scaled somehow?
ggplot(data = climNA_all, aes(x = MAP_A)) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  ylab("Count") + 
  xlab("MAP Anomalies")


ggplot(data = climNA_all, aes(x = Tmin_sp_A)) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  ylab("Count") + 
  xlab("Tmin_sp Anomalies")

ggplot(data = climNA_all, aes(x = PPT_wt_A)) +
  geom_histogram(fill = "blue", color = "black") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  ylab("Count") + 
  xlab("PPT_st Anomalies")

#Everything is pretty normally distributed



#ANOMALIES over time
ggplot(data = climNA_all, aes(x = year, y = MAT_A)) + 
  geom_point() + 
  geom_smooth(method = "loess", col = "red") +
  scale_x_continuous(limits = c(1900, 2020)) +
  theme_classic()
#gam fit is also cool

ggplot(data = climNA_all, aes(x = year, y = Tmin_wt_A)) + 
  geom_point() + 
  geom_smooth(method = "gam", col = "red") +
  scale_x_continuous(limits = c(1900, 2020)) +
  theme_classic()
ggplot(data = climNA_all, aes(x = year, y = Tmin_sp_A)) + 
  geom_point() + 
  geom_smooth(method = "gam", col = "red") +
  scale_x_continuous(limits = c(1900, 2020)) +
  theme_classic()


#PPT
ggplot(data = climNA_all, aes(x = year, y = MAP_A)) + 
  geom_point() + 
  geom_smooth(method = "lm", col = "blue") +
  scale_x_continuous(limits = c(1900, 2020)) +
  theme_classic()
#No change in PPT anomalies

ggplot(data = climNA_all, aes(x = year, y = PPT_wt_A)) + 
  geom_point() + 
  geom_smooth(method = "lm", col = "blue") +
  scale_x_continuous(limits = c(1900, 2020)) +
  theme_classic()

ggplot(data = climNA_all, aes(x = year, y = PPT_sp_A)) + 
  geom_point() + 
  geom_smooth(method = "lm", col = "blue") +
  scale_x_continuous(limits = c(1900, 2020)) +
  theme_classic()
#Increase in dry anomalies in the spring over time?

ggplot(data = climNA_all, aes(x = year, y = PPT_sm_A)) + 
  geom_point() + 
  geom_smooth(method = "lm", col = "blue") +
  scale_x_continuous(limits = c(1900, 2020)) +
  theme_classic()

```






<br>  


#### All Normals/Long-term climate  

Here I compare between different normal periods, since the underlying distributions are unlikely to change much in shape, but may shift over time.  


```{r message = FALSE, warning = FALSE, echo = FALSE}
ggplot(data = climNA_all, aes(x = MAT_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = MAT_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = MAT_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.25)) +
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("MAT")

#The long term average is clearly very similar to the 1951 - 1980 norms


ggplot(data = climNA_all, aes(x = MWMT_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = MWMT_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = MWMT_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.25)) +
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Desnity") + 
  xlab("MWMT")


ggplot(data = climNA_all, aes(x = MCMT_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = MCMT_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = MCMT_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.25)) +
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("MCMT")
```

Looks like MCMT and MAT have changed more than MWMT wrt time - positive shifts from 100Y avg to '51 Norms to `81 Norms.  


```{r message = FALSE, warning = FALSE, echo = FALSE}

#Precipitation

ggplot(data = climNA_all, aes(x = MAP_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = MAP_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = MAP_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.0018)) +
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("MAP")

#Distributions among normals for MAP very similar


ggplot(data = climNA_all, aes(x = MSP_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = MSP_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = MSP_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.03)) +
  scale_x_continuous(limit = c(0, 200)) + #Cuts off outliers
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("MSP")


ggplot(data = climNA_all, aes(x = PAS_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = PAS_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = PAS_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.2)) +
  scale_x_continuous(limit = c(0, 50)) + #Cuts off outliers
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("PAS")

```

There doesn't appear to be much difference in Precipitation among climate normals.  


```{r message = FALSE, warning = FALSE, echo = FALSE}
ggplot(data = climNA_all, aes(x = AHM_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = AHM_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = AHM_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.02)) +
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("AHM")

ggplot(data = climNA_all, aes(x = SHM_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = SHM_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = SHM_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.001)) +
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("SHM")


ggplot(data = climNA_all, aes(x = DD_0_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = DD_0_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = DD_0_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.04)) +
  scale_x_continuous(limits = c(0,150)) + #Cut off tail
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("DD < 0")

#DD < 0 looks like it might be getting smaller over time 

ggplot(data = climNA_all, aes(x = DD5_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = DD5_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = DD5_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.00075)) + 
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("DD > 5")

#GDD becoming greater ober time! Another case where 51 and 100Y are very similar
```

Looks like GDD (Days > 5) are becoming greater and days < 0 fewer over time (though still unsure about values).  


```{r message = FALSE, warning = FALSE, echo = FALSE}
ggplot(data = climNA_all, aes(x = NFFD_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = NFFD_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = NFFD_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.02)) + 
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("NFFD")

#Fewer FFD in more recent Normals set


ggplot(data = climNA_all, aes(x = CMD_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = CMD_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = CMD_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.0021)) + 
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("CMD")

#CMD distribution slightly left-shifted (lower values) for normals 


ggplot(data = climNA_all, aes(x = RH_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = RH_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = RH_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.08)) + 
  scale_fill_manual(name = "Period", values = c("1951-1980" = "blue", "1981-2010" = "green", "1901-2000" = "orange")) +
  ylab("Density") + 
  xlab("RH")

#But RH is right-shifted - greater - in `81 Norms!


```

Increase in RH probably tied to temperature.  
<br>  



## Seasonal & Monthly Variables  

### Exploring Seasonal/Monthly Temperature  
<br>  

#### Tmin  


```{r message = FALSE, warning = FALSE, echo = FALSE}
ggplot(data = climNA_all, aes(x = Tmin_sp_N51)) + 
  geom_density(aes(fill = "1951-1980"), alpha = 0.5) +
  geom_density(aes(x = Tmin_sp_N81, fill = "1981-2010"), alpha = 0.5) +
  geom_density(aes(x = Tmin_sp_100Y, fill = "1901-2000"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.25)) +
  ylab("Density") + 
  xlab("Spring Tmin")


ggplot(data = climNA_all, aes(x = Tmin_wt_100Y)) + 
  geom_density(aes(fill = "Winter"), alpha = 0.5) +
  geom_density(aes(x = Tmin_sp_100Y, fill = "Spring"), alpha = 0.5) +
  geom_density(aes(x = Tmin_sm_100Y, fill = "Summer"), alpha = 0.5) +
  geom_density(aes(x = Tmin_at_100Y, fill = "Autumn"), alpha = 0.5) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,.25)) +
  ylab("Density") + 
  xlab("Tmin by Season")

```






# YoC Annual Climate and Anomalies  

## Looking at climates of collection across California  

Spatial visualization of collections using `sf`  


```{r message = FALSE, warning = FALSE, echo = FALSE}
library(sf)
ca_border <- read_sf(here::here("analyses", "ca_state_border"), layer = "CA_State_TIGER2016") # imports all files with prefix
ca_counties <- read_sf(here::here("analyses", "ca_counties_border"), layer = "CA_Counties_TIGER2016")


nemo_sf <- st_as_sf(nemo_all1, crs = 4326, coords = c("long", "lat"))
clim_dfsf <- st_as_sf(climNA_all, crs = 4326, coords = c("long","lat"))



ggplot() +
  geom_sf(data = ca_counties, fill = "#dfffd1") +
  geom_sf(data = clim_dfsf, aes(color = MAT_100Y), alpha = 0.8, size = 2, show.legend = TRUE) +
  labs(color = "MAT (°C)") +
  scale_color_gradientn(colors = c("#fdff91", "#e30000"), values = c(0, 1)) +
  theme_minimal() #1764 points
ggsave(here::here("analyses", "figs1", "MAT_100Y_raster.png"))


ggplot() +
  geom_sf(data = ca_border, fill = "#dfffd1") +
  geom_sf(data = clim_dfsf, aes(color = MAP_100Y), alpha = 0.8, size = 2, show.legend = TRUE) +
  labs(color = "CAP (mm)") +
  scale_color_gradientn(colors = c("#ade2ff", "#004063"), values = c(0, 1)) +
  theme_minimal()
ggsave(here::here("analyses", "figs1", "MAP_100Y_raster.png"))


##COMBINED MAP & MAT

##Figures save better (for some reason) when entire chunk is run.
#Check out tmap for better mapping?

ggplot() +
  geom_sf(data = ca_counties, fill = "#dfffd1") +
  geom_sf(data = clim_dfsf, aes(fill = MAT_100Y, size = MAP_100Y/10), pch = 21, alpha = 1, show.legend = TRUE) +
  scale_size_continuous(range = c(1, 5)) +
  labs(size = "CAP (cm)") +
  labs(fill = "MAT (°C)") +
  scale_fill_gradientn(colors = c("#63c8ff", "#cc0000"), values = c(0, 1)) +
  theme_minimal() + 
  theme(legend.key.size = unit(5, "mm"), legend.position = c(0.9, 0.7))
ggsave(here::here("analyses", "figs1", "MAP-MAT-combo_100Y_raster.png"))


#Version 2
ggplot() +
  geom_sf(data = ca_counties, fill = "#dfffd1") +
  geom_sf(data = clim_dfsf, aes(fill = MAT_100Y, size = (MAP_100Y/10)), pch = 21, alpha = 1, show.legend = TRUE) +
  scale_size_continuous(range = c(0.5, 4.5)) +
  labs(size = "CAP (cm)") +
  labs(fill = "MAT (°C)") +
  scale_fill_gradientn(colors = c("#63c8ff", "#cc0000"), values = c(0, 1)) +
  theme_minimal() + 
  theme(legend.key.size = unit(5, "mm"), legend.position = c(0.9, 0.7))
ggsave(here::here("analyses", "figs1", "MAP-MAT-combo_100Y_raster_v2.png"))


##Heat-Moisture Index

ggplot() +
  geom_sf(data = ca_border, fill = "#dfffd1") +
  geom_sf(data = clim_dfsf, aes(color = AHM_100Y), alpha = 0.8, size = 2, show.legend = TRUE) +
  labs(color = "SHM") +
  scale_color_gradientn(colors = c("#ade2ff", "#e30000"), values = c(0, 1)) +
  theme_minimal()
#ggsave(here::here("analyses", "figs1", "MAP_100Y_raster.png"))


```


**Tmap** Distribution Maps

```{r message = FALSE, eval = FALSE}
#sf is laready loaded
library(tmap)

#Need additional raster files for elevation, climate, etc...

tm_shape(ca_counties) + tm_polygons(border.col = "white") +
  tm_raster(style = "cont", title = "Elevation", palette = terrain.colors)

```




```{r warning = FALSE, message = FALSE, echo = FALSE, results = 'hide'}
#MOVE TO ANALYSES 1


newdf <- merge(nemo_all1, climNA_all)




ggplot(data = newdf, aes(x = year, y = DOY)) + 
  geom_point(aes(color = MAT_N51)) +
  geom_smooth(method = "lm") +
  scale_color_gradientn(colors = c("#fff71c", "#e60000"), values = c(0, 1)) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  ylab("DOY") + 
  xlab("Year")



ggplot(data = newdf, aes(x = MAT_N51, y = DOY)) + 
  geom_point()+
  geom_smooth(method = "lm") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  ylab("DOY") + 
  xlab("MAT (1951 - 1981)")


ggplot(data = newdf, aes(x = MAP_N51, y = DOY)) + 
  geom_point()+
  geom_smooth(method = "lm") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  ylab("DOY") + 
  xlab("MAP (1951 - 1981)")


```






