---
title: "sensitivity_2"
author: "Devin Gamble"
date: "4/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE, echo = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(broom)
library(here)
library(ggplot2)
library(visreg)
library(jtools)
```


## Objective:  
#### Determine how sensitivity to different climate variables, for different seasons/months, and for long-term vs anomalouse climate varies  
- through time  
- Across space (lat, long, elev)  
- by climate region  

```{r message = FALSE, warning = FALSE}
#Load Data

nemo_df2 <- read_csv(here::here("data_cleaning", "nemo_full_1901_2019.csv")) %>%  
  mutate(error_bin = as_factor(error_bin)) #Should this be ordered? #Combined specimen & climate data from 1901-2019
#1677 obs, 1251 columns

nemo_df1 <- read_csv(here::here("data_cleaning", "nemo_full_1861_2019.csv")) #Combined data for all years
#1764 obs, 1251 columns


#Set contrasts
options(contrasts = c("contr.sum", "contr.poly"))
```


# Finer-grain analyses of Phenological Sensitivity
**Analyze month-of and months-prior sensitivity to climate**

* See 'EDA2.Rmd' for exploration of different models.








