---
title: "Sensitivity Analyses"
author: "Devin Gamble"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r warning = FALSE, message = FALSE, echo = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(broom)
library(here)
library(ggplot2)
library(visreg)
library(jtools)
library(interactions)
```

*To-Do*
- Clean up code chunks
- See Tadeo's code from the Poppy paper (Madrono)


## Objective:  
#### Determine how sensitivity to different climate variables, for different seasons/months, and for long-term vs anomalouse climate varies  
- through time  
- Across space (lat, long, elev)  
- by climate region  

```{r message = FALSE, warning = FALSE}
#Load Data

nemo_df2 <- read_csv(here::here("data_cleaning", "nemo_full_1901_2019.csv")) %>%  
  mutate(error_bin = as_factor(error_bin)) #Should this be ordered? #Combined specimen & climate data from 1901-2019
#1677 obs, 1251 columns

nemo_df1 <- read_csv(here::here("data_cleaning", "nemo_full_1861_2019.csv")) #Combined data for all years
#1764 obs, 1251 columns


#Set contrasts
options(contrasts = c("contr.sum", "contr.poly"))
```


## Identify Sensitivity to different climatic variables  
* See 'EDA2.Rmd' for exploration of different models.



*To-Do*  
- Fix & clean up models describing sensitivity to different aspects of local climate  
- Calculate new seasonal windows of climate parameters (and save to csv)  
- Statistically compare slope estimates of climate parameters on DOY to select the most influential parameters  
- Add in PI as a covariate in models  

<br>  

May also consider:  
- NFFD, bFFP, CMD, RH, DD5, MCMT (see EDA2)

## Annual Conditions  

*100Y Norms* only
```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y

ann_clim1 <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_df2)
ann_clim2 <- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m, data = nemo_df2)
ann_clim3 <- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m + long, data = nemo_df2)
ann_clim4 <- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m + lat + long + year, data = nemo_df2) #Best, though adding year doesn't change much
#No interactions

summary(ann_clim1)
summary(ann_clim2)
summary(ann_clim3)
summary(ann_clim4)
summ(ann_clim4, scale = TRUE, vif = TRUE)
#Controlling for elevation severely reduces the effect of MAT (ns)
#Controlling for elev and long - the effect of temperature returns but is still quite small

summ(ann_clim3, vif = TRUE) #VIF for long, elev, MAP, MAT is high

visreg(ann_clim1, "MAT_100Y", xlab = "MAT (1901-2000)", points = list(col = "#404040"))
visreg(ann_clim1, "MAP_100Y", xlab = "MAP (1901-2000)", points = list(col = "#404040"))

visreg(ann_clim3, "MAT_100Y", xlab = "MAT (1901-2000)", points = list(col = "#404040"))
visreg(ann_clim3, "MAP_100Y", xlab = "MAP (1901-2000)", points = list(col = "#404040"))

visreg(ann_clim4, "MAT_100Y", xlab = "MAT (1901-2000)", points = list(col = "#333333"), gg = TRUE) + theme_apa()
#ggsave(here::here("analyses", "figs1", "MAT_100Y_phensen.png"), height = 4, width = 6)
visreg(ann_clim4, "MAP_100Y", xlab = "MAP (1901-2000)", points = list(col = "#333333"), gg = TRUE) + theme_apa()
#ggsave(here::here("analyses", "figs1", "MAP_100Y_phensen.png"), height = 4, width = 6)

##Plots same as those created in `bias_error.Rmd'

```

```{r message = FALSE, warning = FALSE, echo = FALSE, eval = FALSE}
#redudant with EDA2 code
#plots
#Non-climatic
#scaled: means = 0 and var = 1
#Compare relative effect of each variable

nonclim1 <- lm(DOY ~ scale(elev_m) + scale(long) + scale(year), data = nemo_df2)
summary(nonclim1)

visreg(nonclim1, xvar = "elev_m", xlab = "Elevation (m)", points = list(col = "#404040")) 
visreg(nonclim1, "year", xlab = "Year", points = list(col = "#404040"))
#visreg(nonclim1, "lat", xlab = "Latitude", points = list(col = "#404040"))
visreg(nonclim1, "long", xlab = "Longitude", points = list(col = "#404040"))
```

The relationship b/w DOY and MAT weakens as the model is parameterized, while the estimate of MAP strengthens. MAP appears to be driving variation in DOY. There were no significant interactions between any covariates.  
While MAT still appears to advance DOY, controlling for geography seems to explain a good deal of this variation (over a 100-yr avg). Examining seasonal climate and anomalies should shed more light on this.  

Note: Everything at the annual scale for 100Y averages is strongly correlated (see EDA2.Rmd). Refer to `ann_clim3` model above (controls for elev_m and long).  

*Anomalies* only  
```{r message = FALSE, warning = FALSE, eval = FALSE}
#100Y

anom_clim1 <- lm(DOY ~ MAT_A + MAP_A, data = nemo_df2)
anom_clim2 <- lm(DOY ~ MAT_A + MAP_A + elev_m, data = nemo_df2)
anom_clim3 <- lm(DOY ~ MAT_A + MAP_A + elev_m + long, data = nemo_df2)
anom_clim4 <- lm(DOY ~ MAT_A + MAP_A + elev_m + long + year, data = nemo_df2) #Best, though adding year doesn't change much
#No interactions

summary(anom_clim1)
summary(anom_clim2)
summary(anom_clim3)
summary(anom_clim4)
summ(anom_clim4, scale = FALSE, vif = TRUE)
#Controlling for elevation severely reduces the effect of MAT (ns)
#Controlling for elev and long - the effect of temperature returns but is still quite small

#summ(anom_clim3, vif = TRUE) #VIF for long, elev, MAP, MAT is high

visreg(anom_clim1, "MAT_A", xlab = "MAT (anomaly)", points = list(col = "#404040"))
visreg(anom_clim1, "MAP_A", xlab = "MAP (anomaly)", points = list(col = "#404040"))

visreg(anom_clim3, "MAT_A", xlab = "MAT (anomaly)", points = list(col = "#404040"))
visreg(anom_clim3, "MAP_A", xlab = "MAP (anomaly)", points = list(col = "#404040"))

visreg(anom_clim4, "MAT_A", xlab = "MAT (anomaly)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
#ggsave(here::here("analyses", "figs1", "MAT_A_phensen.png"), height = 4, width = 6)
visreg(anom_clim4, "MAP_A", xlab = "MAP (anomaly)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
#ggsave(here::here("analyses", "figs1", "MAP_A_phensen.png"), height = 4, width = 6)

##Plots same as those created in `bias_error.Rmd'
```



**Normals & Anomalies**
Final models -- use these
```{r warning = FALSE, message = FALSE}
#an_full_clim1 <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A, data = nemo_df2)
#an_full_clim2 <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m, data = nemo_df2)
#an_full_clim3 <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + lat + long, data = nemo_df2)
an_full_clim4 <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + lat + long + year, data = nemo_df2) #Best, though adding year doesn't change much
#No interactions

summ(an_full_clim4, vif = TRUE) #Not scaled
summ(an_full_clim4, scale = TRUE, vif = TRUE) #Scaled = sdtandardized (centered & scaled)

#Visualize Phenological sensitivity (slope estimates are NOT standardized)
#Anomalies
visreg(an_full_clim4, "MAT_A", xlab = "MAT (Anomaly)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
ggsave(here::here("analyses", "figs1", "MAT_A_phensen.png"), height = 4, width = 6)

visreg(an_full_clim4, "MAP_A", xlab = "MAP (Anomaly)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
ggsave(here::here("analyses", "figs1", "MAP_A_phensen.png"), height = 4, width = 6)

#Norms
visreg(an_full_clim4, "MAT_100Y", xlab = "MAT (1901-2000)", points = list(col = "#333333"), gg = TRUE) + theme_apa()
ggsave(here::here("analyses", "figs1", "MAT_100Y_phensen.png"), height = 4, width = 6)

visreg(an_full_clim4, "MAP_100Y", xlab = "MAP (1901-2000)", points = list(col = "#333333"), gg = TRUE) + theme_apa() #reverse transform?
ggsave(here::here("analyses", "figs1", "MAP_100Y_phensen.png"), height = 4, width = 6)


```

<br>  


### Seasonal Conditions

For Seasonal variables, examine models with:
- Tmin & Tave (Winter, spring) [No Tmax]  
- PPT (Winter, Spring, Summer)  

May also consider  
- DD > 5 (spring and winter); DD > 18 (spring and summer); CMD (winter, spring, summer)? RH?  
--
From 'EDA2.Rmd', Both Spring temperature and precipitation (from 100Y averages) appeared to be the most influential on DOY. Tave had a higher R2 and Beta than Tmin for spring temps...  


**Winter Conditions** only
```{r message = FALSE, warning = FALSE}
#Winter Conditions
sz_wt1 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + Tmin_wt_A + PPT_wt_A, data = nemo_df2)
#summ(sz_wt1, vifs = TRUE)

sz_wt1c <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + Tmin_wt_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2) #Tmin
summ(sz_wt1c, vifs = TRUE)
summ(sz_wt1c, scale = TRUE, vifs = TRUE)

visreg(sz_wt1c, xvar = "PPT_wt_100Y", xlab = "PPT Norm (winter)", points = list(col = "#333333"), gg = TRUE) + theme_apa()
visreg(sz_wt1c, xvar = "Tmin_wt_100Y", xlab = "Tmin Norm (winter)", points = list(col = "#333333"),gg = TRUE) + theme_apa()
visreg(sz_wt1c, xvar = "PPT_wt_A", xlab = "PPT Anom. (winter)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
visreg(sz_wt1c, xvar = "Tmin_wt_A", xlab = "Tmin Anom. (winter)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)


#Ave Tmin - higher VIFs fo TAve_100Y (> 5) -- possibility from colinaerity with lat/long...?
sz_wt1cave <- lm(DOY ~ Tave_wt_100Y + PPT_wt_100Y + Tave_wt_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2) #Tave
#summ(sz_wt1cave, vifs = TRUE) #These have low R2 and high SE, plus estimates are crazy
```


Winter Interaction Models
**(See `sensitivity_3.Rmd` for Normal x Anom. interaction models!)**
```{r message = FALSE, warning = FALSE, eval = FALSE}
#Interaction Models
sz_wt1_int1 <- lm(DOY ~ Tmin_wt_100Y*PPT_wt_100Y + Tmin_wt_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2) #NS w/ elev + long
summ(sz_wt1_int1) #R2 - 0.18, interaction B = -1.25     #Tmin more significant, removed Tave

sz_wt1_int2 <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + Tmin_wt_A*PPT_wt_A + elev_m + lat + long + year, data = nemo_df2) #NS w/ elev + long
summ(sz_wt1_int2)
#Both NS

```


Controlling for geographic location (lat and long and elev), the interaction between Tmin_wt and PPT_wt disappears. Including year as a covariate slightly improves $R^2$.  


**Spring Conditions**

```{r message = FALSE, warning = FALSE}
sz_sp1c <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)
summ(sz_sp1c, vifs = TRUE)
summ(sz_sp1c, scale = TRUE, vifs = TRUE)


#Visualizations#
visreg(sz_sp1c, xvar = "PPT_sp_100Y", xlab = "Spring PPT (1901-2000)", points = list(col = "#333333"), gg = TRUE) + theme_apa()
ggsave(here::here("analyses", "figs1", "spring_PPT100_phensen.png"), height = 4, width = 6)

visreg(sz_sp1c, xvar = "Tmin_sp_100Y", xlab = "Spring Tmin (1901-2000)", points = list(col = "#333333"),gg = TRUE) + theme_apa()
ggsave(here::here("analyses", "figs1", "spring_Tmin100_phensen.png"), height = 4, width = 6)

visreg(sz_sp1c, xvar = "PPT_sp_A", xlab = "Spring PPT (Anomaly)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
ggsave(here::here("analyses", "figs1", "spring_PPT_A_phensen.png"), height = 4, width = 6)

visreg(sz_sp1c, xvar = "Tmin_sp_A", xlab = "Spring Tmin (Anomaly)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
ggsave(here::here("analyses", "figs1", "spring_Tmin_A_phensen.png"), height = 4, width = 6)


#Tave model
sz_sp1cave <- lm(DOY ~ Tave_sp_100Y + PPT_sp_100Y + Tave_sp_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)
#summ(sz_sp1cave, vifs = TRUE)
#VIF for Tave is much higher than VIF for Tmin - another reason to use Tmin...
```


```{r message = FALSE, warning = FALSE, eval = FALSE}
#ALTERNATIVE FIGS for poster
#More compressed, saved as narrower in ggsave()

#Visualizations#
visreg(sz_sp1c, xvar = "PPT_sp_100Y", xlab = "Spring PPT (1901-2000)", points = list(col = "#333333"), gg = TRUE) + theme_apa()
ggsave(here::here("analyses", "figs1", "spring_PPT100_phensenV2.png"), height = 4, width = 5)

visreg(sz_sp1c, xvar = "Tmin_sp_100Y", xlab = "Spring Tmin (1901-2000)", points = list(col = "#333333"),gg = TRUE) + theme_apa()
ggsave(here::here("analyses", "figs1", "spring_Tmin100_phensenV2.png"), height = 4, width = 5)

visreg(sz_sp1c, xvar = "PPT_sp_A", xlab = "Spring PPT (Anomaly)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
ggsave(here::here("analyses", "figs1", "spring_PPT_A_phensenV2.png"), height = 4, width = 5)

visreg(sz_sp1c, xvar = "Tmin_sp_A", xlab = "Spring Tmin (Anomaly)", points = list(col = "#333333"), gg = TRUE) + theme_apa() +
  geom_vline(xintercept = 0, lty = 2)
ggsave(here::here("analyses", "figs1", "spring_Tmin_A_phensenV2.png"), height = 4, width = 5)

```



Spring Interaction Models:
```{r message = FALSE, warning = FALSE, eval = FALSE}
#Interaction Models
sz_sp1_int1 <- lm(DOY ~ Tmin_sp_100Y*PPT_sp_100Y + Tmin_sp_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) #NS w/ elev + long
summ(sz_wt1_int1, vifs = TRUE) #R2 - 0.18, interaction B = -1.25     #Tmin more significant, removed Tave

sz_sp1_int2 <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_A*PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) #NS w/ elev + long
summ(sz_wt1_int2, vifs = TRUE)
#Both NS

```


Interaction term becomes non-significant with all other covariates. Removing it, we see results similar to the above winter 'standard' model - advancing effect of Tmin (+ year), delaying effect of PPT (+ long, elevation)

[Summer conditions are likely not biologically important in the phenology of N menziesii, patterns due to correlation]

```{r message = FALSE, warning = FALSE, echo = FALSE, eval = FALSE}
#Summer Conditions
sz_clim3 <- lm(DOY ~ Tmin_sm_100Y + PPT_sm_100Y, data = nemo_df2)
summary(sz_clim3)
sz_clim3.1 <- lm(DOY ~ Tave_sm_100Y + PPT_sm_100Y, data = nemo_df2)
summary(sz_clim3.1)
sz_clim3.2 <- lm(DOY ~ Tmin_sm_100Y +  PPT_sm_100Y + Tmin_sm_100Y*PPT_sm_100Y, data = nemo_df2)
#summary(stepAIC(sz_clim3.2, direction = "both"))
#Looks like Summer PPT has the largest effect, with Tmin marginally advancing DOY. No interaction
visreg(sz_clim3.2, xvar = "PPT_sm_100Y", xlab = "PPT (summer)", points = list(col = "#404040"))
```

<br>  

#### Comparing Additive Winter & Spring Models  

```{r warning = FALSE}
AIC(sz_wt1c, sz_sp1c, an_full_clim4)
#More support for spring model, as expected

```



**Winter AND Spring Conditions** Together  
Exploring different additive combinations of parameters -- use AIC to find most-supported model.  
[Result: Spring-only model better than each combination]
```{r message = FALSE, warning = FALSE, eval = FALSE}
sz_wtxsp_1a <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + Tmin_wt_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)
sz_wtxsp_1b <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + Tmin_sp_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2)
#Winter Norms, Spring Anom.
sz_wtxsp_1c <- lm(DOY ~ Tmin_wt_100Y + PPT_wt_100Y + Tmin_sp_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)

sz_wtxsp_1d <- lm(DOY ~ Tmin_wt_100Y + PPT_sp_100Y + Tmin_sp_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) #Second Lowest
sz_wtxsp_1e <- lm(DOY ~ Tmin_wt_100Y + PPT_sp_100Y + Tmin_sp_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2)

sz_wtxsp_1f <- lm(DOY ~ Tmin_wt_100Y + PPT_sp_100Y + Tmin_wt_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2)
#Winter Tmin, Spring PPT
sz_wtxsp_1g <- lm(DOY ~ Tmin_wt_100Y + PPT_sp_100Y + Tmin_wt_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) #Third Lowest

#Spring Norms, Winter Anom. 
sz_wtxsp_1h <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_wt_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2)

sz_wtxsp_1i <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_wt_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) #LOWEST AIC
sz_wtxsp_1j <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2)

sz_wtxsp_1k <- lm(DOY ~ Tmin_sp_100Y + PPT_wt_100Y + Tmin_sp_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)
#Winter PPT, Spring Tmin
sz_wtxsp_1l <- lm(DOY ~ Tmin_sp_100Y + PPT_wt_100Y + Tmin_sp_A + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2)
sz_wtxsp_1m <- lm(DOY ~ Tmin_sp_100Y + PPT_wt_100Y + Tmin_wt_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)

#Compare AIC values
AIC(sz_wtxsp_1a, sz_wtxsp_1b, sz_wtxsp_1c, sz_wtxsp_1d, sz_wtxsp_1e, sz_wtxsp_1f, sz_wtxsp_1g, sz_wtxsp_1h, sz_wtxsp_1i, sz_wtxsp_1j, sz_wtxsp_1k, sz_wtxsp_1l, sz_wtxsp_1m) #Mostly pretty close
#"Best" Model: Long-term Spring averages, Winter Tmin Anom. & Spring PPT Anom.

lapply(list(sz_wtxsp_1i, sz_wtxsp_1d, sz_wtxsp_1g), summ, scale = TRUE, vifs = TRUE) #scale true
#Adj. R2s are all equal

#Compare with spring-only model:
AIC(sz_sp1c, sz_wtxsp_1i, sz_wtxsp_1d, sz_wtxsp_1g)
#Spring-only model is still best!!!

```

Given that there were no significant interactions in winter-only or spring-only models, winter x spring interactions are not examined here.

Winter & Spring interactions (Among Norms *or* Anomalies)
```{r message = FALSE, warning = FALSE}
#Interaction Models 
#Use spring conditions for "control" climate parameters since they were most predictive according to model comparisons

#Norms interactions
sz_wt_sp1a_int <- lm(DOY ~ Tmin_sp_100Y*PPT_wt_100Y + Tmin_sp_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)
summ(sz_wt_sp1a_int, vifs = TRUE) #Significant Interaction!

johnson_neyman(sz_wt_sp1a_int, pred = "Tmin_sp_100Y", modx = "PPT_wt_100Y")
interact_plot(sz_wt_sp1a_int, pred = "Tmin_sp_100Y", modx = "PPT_wt_100Y", x.label = "Tmin (spring)", legend.main = "PPT (winter)") + theme_bw()
#ggsave(here::here("analyses", "figs1", "intplot_wtP_spT1_100Y.png"), height = 4, width = 6)
johnson_neyman(sz_wt_sp1a_int, pred = "PPT_wt_100Y", modx = "Tmin_sp_100Y")
interact_plot(sz_wt_sp1a_int, pred = "PPT_wt_100Y", modx = "Tmin_sp_100Y", x.label = "PPT (winter)", legend.main = "Tmin (spring)") + theme_bw()


sz_wt_sp1b_int <- lm(DOY ~ Tmin_wt_100Y*PPT_sp_100Y + Tmin_sp_A + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)
#Interaction NS
#Anomalies Interactions
sz_wt_sp2a_int <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_wt_A*PPT_sp_A + elev_m + lat + long + year, data = nemo_df2)
#Interaction NS
sz_wt_sp2b_int <- lm(DOY ~ Tmin_sp_100Y + PPT_sp_100Y + Tmin_sp_A*PPT_wt_A + elev_m + lat + long + year, data = nemo_df2)
#Interaction NS




#Spring-only model vs Norms interaction model
AIC(sz_sp1c, sz_wt_sp1a_int, an_full_clim4) 
#Spring-only model still preferred! 

```

The **Spring Model** Has the most support compared to Winter-only, mixed winter and spring, and MAT based on AIC comparisons above.
Did not use stepAIC since it's difficult to avoid collinearity when testing more than four climate predictors at a time.

This suggests that both Spring PPT and Tmin are major determinants of DOY. 

**Plots/Visualizations** - Only additive models included
```{r warning = FALSE, message = FALSE, echo = FALSE}
#Center & Scale Estimates to make comparisons

#Just Seasonal Variables
plot_summs(sz_wt1c, sz_sp1c, sz_wt_sp2, model.names = c("Winter", "Spring", "Wt_T & Sp_PPT"), coefs = c("Tmin_wt_100Y", "Tmin_sp_100Y", "PPT_wt_100Y", "PPT_sp_100Y"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()#including covariates

#Seasonal & Annual Variables
plot_summs(ann_clim4, sz_wt1c, sz_sp1c, sz_wt_sp2, model.names = c("MAT/P", "Winter", "Spring", "Wt_T & Sp_PPT"), coefs = c("MAT_100Y", "MAP_100Y", "Tmin_wt_100Y", "Tmin_sp_100Y", "PPT_wt_100Y", "PPT_sp_100Y"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()

#Without mixed-season model
plot_summs(ann_clim4, sz_wt1c, sz_sp1c, model.names = c("MAT/P", "Winter", "Spring"), coefs = c("MAT_100Y", "MAP_100Y", "Tmin_wt_100Y", "Tmin_sp_100Y", "PPT_wt_100Y", "PPT_sp_100Y"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()

ggsave(here::here("analyses", "figs1", "plot_summs_An_wt_sp_100Y.png"), height = 4, width = 6)

#Centering only - leads to same relative positioning of effect sizes, just different magnitudes/abs values

```


[Anomalies Only]

**Plots** - Only additive models included
```{r warning = FALSE, message = FALSE, echo = FALSE}
#Scaling = Standardize & Center Estimates to make comparisons

#Just Seasonal Variables
plot_summs(sz_wt1A, sz_sp1cmaxA, sz_wt_sp1Amax, model.names = c("Winter", "Spring", "Wt_T & Sp_PPT"), coefs = c("Tmin_wt_A", "Tmax_sp_A", "PPT_wt_A", "PPT_sp_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()#including covariates


#Seasonal & Annual Variables
plot_summs(anom_clim4, sz_wt1A, sz_sp1cmaxA, sz_wt_sp1Amax, model.names = c("MAT/P", "Winter", "Spring", "Wt_T & Sp_PPT"), coefs = c("MAT_A", "MAP_A", "Tmin_wt_A", "Tmax_sp_A", "PPT_wt_A", "PPT_sp_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()

#Without mixed-season model
plot_summs(anom_clim4, sz_wt1A, sz_sp1cmaxA, model.names = c("MAT/P", "Winter", "Spring"), coefs = c("MAT_A", "MAP_A", "Tmin_wt_A", "Tmax_sp_A", "PPT_wt_A", "PPT_sp_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw() #Tmax_sp

ggsave(here::here("analyses", "figs1", "plot_summs_Anom_wt_sp_A(Tmax_sp).png"), height = 4, width = 6)

plot_summs(anom_clim4, sz_wt1A, sz_sp1A, model.names = c("MAT/P", "Winter", "Spring"), coefs = c("MAT_A", "MAP_A", "Tmin_wt_A", "Tmin_sp_A", "PPT_wt_A", "PPT_sp_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw() #Tmin_sp

ggsave(here::here("analyses", "figs1", "plot_summs_Anom_wt_sp_A(Tmin_sp).png"), height = 4, width = 6)

#Both Tmin and Tmax spring models:
#plot_summs(anom_clim4, sz_wt1A, sz_sp1A, sz_sp1cmaxA, model.names = c("MAT/P", "Winter", "Spring"), coefs = c("MAT_A", "MAP_A", "Tmin_wt_A", "Tmin_sp_A", "Tmax_sp_A", "PPT_wt_A", "PPT_sp_A"), inner_ci_level = 0.8, scale = TRUE) +
#  theme_bw() #Tmin_sp


#ggsave(here::here("analyses", "figs1", "plot_summs_An_wt_sp_A.png"), height = 4, width = 6)

```


**Compare** Long-term and anomalies sensitivies (separate models)

```{r warning = FALSE, eval = FALSE}
plot_summs(anom_clim4, ann_clim4, model.names = c("MAT/P_100Y", "MAT/P_A"), coefs = c("MAT_100Y", "MAT_A", "MAP_100Y", "MAP_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()

ggsave(here::here("analyses", "figs1", "plot_summs_MAT-P_Anomx100Y.png"), height = 4, width = 6)

plot_summs(sz_wt1c, sz_wt1A, model.names = c("Winter_100Y", "Winter_A"), coefs = c("Tmin_wt_100Y", "Tmin_wt_A", "PPT_wt_100Y", "PPT_wt_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw() #Winter
ggsave(here::here("analyses", "figs1", "plot_summs_Wt_Anomx100Y.png"), height = 4, width = 6)

plot_summs(sz_sp1c, sz_sp1cmaxA, model.names = c("Spring_100Y", "Spring_A"), coefs = c("Tmin_sp_100Y", "Tmax_sp_A", "PPT_sp_100Y", "PPT_sp_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw() #Spring
ggsave(here::here("analyses", "figs1", "plot_summs_Sp_Anomx100Y.png"), height = 4, width = 6)


#plot_summs(sz_wt1c, sz_sp1c, sz_wt1A, sz_sp1cmaxA, model.names = c("Winter_100Y", "Spring_100Y", "Winter_A", "Spring_A"), coefs = c("Tmin_wt_100Y", "Tmin_wt_A", "Tmin_sp_100Y", "Tmax_sp_A", "PPT_wt_100Y", "PPT_wt_A", "PPT_sp_100Y", "PPT_sp_A"), inner_ci_level = 0.8, scale = TRUE) +
#  theme_bw() #Both

```


<br>  


