---
title: "sensitivity_3"
author: "Devin Gamble"
date: "4/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Investigating variation in phenological sensitivity  

A. Through time
B. Across regions [Line ~ 150]

```{r warning = FALSE, message = FALSE, echo = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(broom)
library(here)
library(ggplot2)
library(visreg)
library(jtools)
library(interactions)
```



```{r message = FALSE, warning = FALSE}
#Load Data
nemo_df2 <- read_csv(here::here("data_cleaning", "nemo_full_1901_2019.csv")) %>%  
  mutate(error_bin = as_factor(error_bin)) #Should this be ordered? #Combined specimen & climate data from 1901-2019
#1677 obs, 1251 columns

nemo_df1 <- read_csv(here::here("data_cleaning", "nemo_full_1861_2019.csv")) #Combined data for all years
#1764 obs, 1251 columns

#Set contrasts
options(contrasts = c("contr.sum", "contr.poly"))
```





## Temporal variation in Phenological Sensitivity  

Investigate whether phenological sensitivity (slope/regression coefficient of climate parameter with DOY) to long-term & anomalous climate  *varies* through time.

### Categorical Comparison: Bin by years  

```{r}
#New data subsets for year

## 20 year bins
nemo_1901_20 <- nemo_df2 %>% filter(year >= 1901, year <= 1920)
nemo_1921_40 <- nemo_df2 %>% filter(year >= 1921, year <= 1940)
nemo_1941_60 <- nemo_df2 %>% filter(year >= 1941, year <= 1960)
nemo_1961_80 <- nemo_df2 %>% filter(year >= 1961, year <= 1980)
nemo_1981_00 <- nemo_df2 %>% filter(year >= 1981, year <= 2000)
nemo_2001_19 <- nemo_df2 %>% filter(year >= 2001, year <= 2019)

#30 year bins - larger sample sizes
nemo_1901_30 <- nemo_df2 %>% filter(year >= 1901, year <= 1930)
nemo_1931_60 <- nemo_df2 %>% filter(year >= 1931, year <= 1960)
nemo_1961_90 <- nemo_df2 %>% filter(year >= 1961, year <= 1990)
nemo_1991_19 <- nemo_df2 %>% filter(year >= 1991, year <= 2019)

```


**MAT/MAP**
```{r}
base_lm1 <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_df2)

MA_20_1lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1901_20)
MA_20_2lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1921_40)
MA_20_3lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1941_60)
MA_20_4lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1961_80)
MA_20_5lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1981_00)
MA_20_6lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1901_20)


MA_30_1lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1901_30)
MA_30_2lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1931_60)
MA_30_3lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1961_90)
MA_30_4lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + long + year, data = nemo_1991_19)

lapply(list(MA_30_1lm, MA_30_2lm, MA_30_3lm, MA_30_4lm), summ, vif = TRUE, scale = TRUE)
##ATTN!!!### VIF > 4, but for longitude only (not interested in coefficient...)
```


Plots:
```{r}
#Bins = 20, long-term
plot_summs(MA_20_1lm, MA_20_2lm, MA_20_3lm, MA_20_4lm, MA_20_5lm, MA_20_6lm, model.names = c("1", "2", "3", "4", "5", "6"), coefs = c("MAT_100Y", "MAP_100Y"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()


#Bins = 20, anomalies
plot_summs(MA_20_1lm, MA_20_2lm, MA_20_3lm, MA_20_4lm, MA_20_5lm, MA_20_6lm, model.names = c("1", "2", "3", "4", "5", "6"), coefs = c("MAT_A", "MAP_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()


#Bins = 30, long-term
plot_summs(MA_30_1lm, MA_30_2lm, MA_30_3lm, MA_30_4lm, model.names = c("1901-1930", "1931-1960", "1961-1990", "1990-2019"), coefs = c("MAT_100Y", "MAP_100Y"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()
ggsave(here::here("analyses", "figs1", "sens_3_figs", "temp_sens_100Y_30.png"), height = 4, width = 6)


#Bins = 30, anomalies
plot_summs(MA_30_1lm, MA_30_2lm, MA_30_3lm, MA_30_4lm, model.names = c("1901-1930", "1931-1960", "1961-1990", "1990-2019"), coefs = c("MAT_A", "MAP_A"), inner_ci_level = 0.8, scale = TRUE) +
  theme_bw()
ggsave(here::here("analyses", "figs1", "sens_3_figs", "temp_sens_Anom_30.png"), height = 4, width = 6)

```

30 year bins seem more appropriate at a glance--larger sample sizes, clearer trends. The sensitivity to anomalies increases most apparently with MAT in these models (final plot).  

Differences in sensitivity to spatial (long-term) variation in climate across periods due to sampling effects?

*Examine*: Distributions of DOYs across periods!!!




### Quantitative Analysis: Interaction with year


```{r}
year_int_lm1 <- lm(DOY ~ MAT_100Y*year + MAP_100Y*year + elev_m + long + year, data = nemo_df2)
summary(year_int_lm1)
year_int_lm2 <- lm(DOY ~ MAT_A*year + MAP_A*year + elev_m + long + year, data = nemo_df2)
summary(year_int_lm2)

```







## Geographic/Climatic Variation in Phenological Sensitivity

#### Does Sensitivity to MAT/MAP anomalies depend on chronic climate?  




```{r}
sens_int_lm1 <- lm(DOY ~ MAT_A*MAT_100Y + MAT_A*MAP_100Y + elev_m + lat + long + year, data = nemo_df2) #does not control for MAP_A...
sens_int_lm2 <- lm(DOY ~ MAP_A*MAT_100Y + MAP_A*MAP_100Y + elev_m + lat + long + year, data = nemo_df2)

lapply(list(sens_int_lm1, sens_int_lm2), summ, scale = TRUE, vifs = TRUE)
#Original: 1st, 3rd and 4th interactions significant


#Controlling for MAP_A and MAT_A, respectively
sens_int_lm1b <- lm(DOY ~ MAT_A*MAT_100Y + MAT_A*MAP_100Y + MAP_A + elev_m + lat + long + year, data = nemo_df2) #does control for MAP_A
sens_int_lm2b <- lm(DOY ~ MAP_A*MAT_100Y + MAP_A*MAP_100Y + MAT_A + elev_m + lat + long + year, data = nemo_df2)

lapply(list(sens_int_lm1b, sens_int_lm2b), summ, scale = TRUE, vifs = TRUE)
#No change in Adj. R2. BUT MAP_A*MAP_100Y interaction becomes NS!!!!!! VIFs are okay.
#1st and 3rd interactions significant (MAT_A*MAP_100Y became NS when controlling for MAP_A...)


#Excluding Main effect of interacting anomaly (led to a VIF issue with seasonal models below):
sens_int_lm1c <- lm(DOY ~ MAT_A:MAT_100Y + MAT_A:MAP_100Y + MAP_A + elev_m + lat + long + year, data = nemo_df2) 
sens_int_lm2c <- lm(DOY ~ MAP_A:MAT_100Y + MAP_A:MAP_100Y + MAT_A + elev_m + lat + long + year, data = nemo_df2)

lapply(list(sens_int_lm1c, sens_int_lm2c), summ, scale = TRUE, vifs = TRUE)
#The R2 values of these models are much lower -- loss of significance for some interactions
#1st interaction only significant



#AIC comparison:
AIC(sens_int_lm1, sens_int_lm1b, sens_int_lm1c, sens_int_lm2, sens_int_lm2b, sens_int_lm2c)
#Controlling for MAT_A and MAP_A lead to better models, bet excluding main (single) effect terms of predictors in an interaction does not! 
#(1b and 2b models are best)

```

Significant Interactions: MAT_A x MAT_100Y && MAP_A x MAT_100Y


```{r}
#MAT_A
johnson_neyman(sens_int_lm1b, pred = "MAT_A", modx = "MAT_100Y")
#This J-N plot is super weird... possibly has a tighter CI than linear regression output????
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_int_JN_MAT1.png"), height = 4, width = 5)

interact_plot(sens_int_lm1b, pred = "MAT_A", modx = "MAT_100Y", x.label = "MAT (anomaly)", legend.main = "MAT (1901-2000)") + theme_bw() + geom_vline(xintercept = 0, lty = 2, col = "#808080")
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAT1.png"), height = 4, width = 6)

#MAP_A
johnson_neyman(sens_int_lm2b, pred = "MAP_A", modx = "MAT_100Y")
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_int_JN_MAP1.png"), height = 4, width = 5)
interact_plot(sens_int_lm2b, pred = "MAP_A", modx = "MAT_100Y", x.label = "MAP (anomaly)", legend.main = "MAT (1901-2000)") + theme_bw() + geom_vline(xintercept = 0, lty = 2, col = "#808080")
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAP1.png"), height = 4, width = 6)


#The following interaction now NS
johnson_neyman(sens_int_lm2b, pred = "MAP_A", modx = "MAP_100Y")
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_int_JN_MAP2.png"), height = 4, width = 5)
interact_plot(sens_int_lm2b, pred = "MAP_A", modx = "MAP_100Y", x.label = "MAP (anomaly)", legend.main = "MAP (1901-2000)") + theme_bw() + geom_vline(xintercept = 0, lty = 2, col = "#808080")
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAP2.png"), height = 4, width = 6)
```

**Simple Slopes analysis**  

Determine conditional slope of predictor for different values of mod var.
```{r}
##Following function (from 'interactions') mean-centers non-focal predictor var.s && calculate conditional slopes for means +/- 1 SD
## Similar to Johnson-Nayman plots in aim
sslm1 <- sim_slopes(sens_int_lm1b, pred = "MAT_A", modx = "MAT_100Y")
sslm1
plot(sslm1)

sslm2a <- sim_slopes(sens_int_lm2b, pred = "MAP_A", modx = "MAT_100Y")
sslm2a
plot(sslm2a)

#sslm2b <- sim_slopes(sens_int_lm2b, pred = "MAP_A", modx = "MAP_100Y")
#sslm2b
#plot(sslm2b)

```
It appears that these interactions are N.S. for high values of MAT_100Y (mean + 1 SD); and low values of MAP_100Y (mean = 1 SD). MAT_A*MAT_100Y high-end is only marginally NS... 



##### Model Diagnostics  

```{r}
plot(sens_int_lm1b)
plot(sens_int_lm2b)

##Check assumption that relationship b/w anomaly and DOY is linear regardless of level of mod.x (long-term MAT/MAP)
interact_plot(sens_int_lm1b, pred = "MAT_A", modx = "MAT_100Y", x.label = "MAT (anomaly)", legend.main = "MAT (1901-2000)", linearity.check = TRUE)
interact_plot(sens_int_lm2b, pred = "MAP_A", modx = "MAT_100Y", x.label = "MAT (anomaly)", legend.main = "MAT (1901-2000)", linearity.check = TRUE)
interact_plot(sens_int_lm2b, pred = "MAP_A", modx = "MAP_100Y", x.label = "MAT (anomaly)", legend.main = "MAT (1901-2000)", linearity.check = TRUE)

#Suggests that all interactions found here are nonlinear! 
#Solution: polynomial terms, GAMs/etc. [Polynomials didn't help much].
```




Final versions of interaction plots:

```{r warning = FALSE}
#Legend titles are weird with theme_apa() -- may need to add to image later
#80% intervals, option to remove

#MAT_100Y * MAT_A
interact_plot(sens_int_lm1b, pred = "MAT_A", modx = "MAT_100Y", x.label = "MAT (anomaly)", legend.main = "MAT (1901-2000)") + theme_bw() +
geom_vline(xintercept = 0, lty = 2, col = "#808080") + scale_y_continuous(limits = c(80, 120), n.breaks = 3)
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAT_A_v2.png"), height = 4, width = 5.5)
#Edited breaks to have DOY scale line up, combine plots into a single figure

#MAT_100Y * MAP_A 
interact_plot(sens_int_lm2b, pred = "MAP_A", modx = "MAT_100Y", x.label = "MAP (anomaly)", legend.main = "MAT (1901-2000)") + theme_bw() + 
geom_vline(xintercept = 0, lty = 2, col = "#808080") + scale_y_continuous(limits = c(80, 120), n.breaks = 3)
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAP_A_v2.png"), height = 4, width = 5.5)


#MAP_100Y * MAP_A ###!! Became NS when controlling for MAP_A!
#interact_plot(sens_int_lm2b, pred = "MAP_A", modx = "MAP_100Y", x.label = "MAP (anomaly)", legend.main = "MAP (1901-2000)") + theme_apa() + 
#geom_vline(xintercept = 0, lty = 2, col = "#808080")
#ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAPb_v2.png"), height = 4, width = 6)

#Only marginally NS, however (p = 0.06)^^^
```

<br>  

#### Seasonl Interactions Models  

**Choose best seasonal model to explore norm x anomaly interactions here**  
See `sensitivity_1.Rmd` for original seasonal models.  


*Winter Conditions*  
**Not as well supported as Spring models
```{r eval = FALSE}
#Anomaly*Norm Interactions

wt_int_2a <- lm(DOY ~ Tmin_wt_A*Tmin_wt_100Y + Tmin_wt_A*PPT_wt_100Y + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2) 
summ(wt_int_2a, vifs = TRUE)

wt_int_2b <- lm(DOY ~ PPT_wt_A*Tmin_wt_100Y + PPT_wt_A*PPT_wt_100Y + Tmin_wt_A + elev_m + lat + long + year, data = nemo_df2) 
summ(wt_int_2b, vifs = TRUE)
#Both terms significant

#High VIF values here (but not for MAT/MAP interactions) with complete interaction model. Test interaction only:

wt_int_2a.2 <- lm(DOY ~ Tmin_wt_A:Tmin_wt_100Y + Tmin_wt_A:PPT_wt_100Y + PPT_wt_A + elev_m + lat + long + year, data = nemo_df2) 
summ(wt_int_2a.2, vifs = TRUE) #Looks better, but has much lower R2
#Significant Interaction
wt_int_2b.2 <- lm(DOY ~ PPT_wt_A:Tmin_wt_100Y + PPT_wt_A:PPT_wt_100Y + Tmin_wt_A + elev_m + lat + long + year, data = nemo_df2) 
summ(wt_int_2b.2, vifs = TRUE)
#These also fail to control for the norms... not sure about using these models
```

Colinearity among seasonal variables is likely greater, producing more variance inflation compared to annual parameters.

**Question**: Can we ignore high VIFs for significant interaction terms, if they're only due to the addition of a main effect of a predictor present in that interaction...?
It sounds like this might be reasonable. If so, the first models would be the best.

*Spring Conditions*  
```{r}
#Anomaly*Norm Interactions
sp_int_1a <- lm(DOY ~ Tmin_sp_A*Tmin_sp_100Y + Tmin_sp_A*PPT_sp_100Y + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_1a, vifs = TRUE)

sp_int_1b <- lm(DOY ~ PPT_sp_A*Tmin_sp_100Y + PPT_sp_A*PPT_sp_100Y + Tmin_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_1b, vifs = TRUE)
#Marginally NS (p = 0.051038) 
#Crazy high VIF values!!!
#Significant when not controlling for Tmin_A


#High VIF values here (but not for MAT/MAP interactions) with complete interaction model. Test interaction only:
sp_int_2a <- lm(DOY ~ Tmin_sp_A:Tmin_sp_100Y + Tmin_sp_A:PPT_sp_100Y + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_2a, vifs = TRUE)

sp_int_2b <- lm(DOY ~ PPT_sp_A:Tmin_sp_100Y + PPT_sp_A:PPT_sp_100Y + Tmin_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_2b, vifs = TRUE)
#Still some VIF issues (in interaction terms...), but lower R2s and loss of significance


#Alternative: Test only single Interaction terms, including main effect:
#(Also adding a covariate to control for the Norm not included)
sp_int_3a <- lm(DOY ~ Tmin_sp_A*Tmin_sp_100Y + PPT_sp_100Y + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_3a, vifs = TRUE)

sp_int_3b <- lm(DOY ~ Tmin_sp_A*PPT_sp_100Y + Tmin_sp_100Y + Tmin_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_3b, vifs = TRUE)

sp_int_3c <- lm(DOY ~ PPT_sp_A*Tmin_sp_100Y + PPT_sp_100Y + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_3c , vifs = TRUE)

sp_int_3d <- lm(DOY ~ PPT_sp_A*PPT_sp_100Y + Tmin_sp_100Y + Tmin_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_3d, vifs = TRUE)

#R2s better
#VIF issues persist...

##
# REGARDLESS
##

#No significant interactions from these models

```
**Long-term Annual Norms & Spring Anomalies**:  

```{r}
sp_int_4a <- lm(DOY ~ Tmin_sp_A*MAT_100Y + Tmin_sp_A*MAP_100Y + PPT_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_4a, vifs = TRUE)

sp_int_4b <- lm(DOY ~ PPT_sp_A*MAT_100Y + PPT_sp_A*MAP_100Y + Tmin_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_4b, vifs = TRUE)

##Barely significant PPT_sp_A*MAP_100Y interaction
##Try PPT_wt instead?

sp_int_4c <- lm(DOY ~ PPT_sp_A*MAT_100Y + PPT_sp_A*PPT_wt_100Y + Tmin_sp_A + elev_m + lat + long + year, data = nemo_df2) 
summ(sp_int_4c, vifs = TRUE)
#NS

#VIFs still insane...

```




**Visualizations**  
Assuming the first Spring interaction models are acceptable:
```{r}
#MAT_100Y * MAT_A
interact_plot(sp_int_1a, pred = "Tmin_sp_A", modx = "Tmin_sp_100Y", x.label = "Spring Tmin (anomaly)", legend.main = "Spring Tmin (1901-2000)") + theme_apa() +
geom_vline(xintercept = 0, lty = 2, col = "#808080")
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAT_v2.png"), height = 4, width = 6)


#MAP_100Y * MAT_A
interact_plot(sens_int_lm2, pred = "Tmin_sp_A", modx = "PPT_sp_100Y", x.label = "Spring Tmin (anomaly)", legend.main = "MAT (1901-2000)") + theme_apa() + theme(legend.title = element_text("MAT (1901-2000)")) +
geom_vline(xintercept = 0, lty = 2, col = "#808080")
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAPa_v2.png"), height = 4, width = 6)


#MAP_100Y * MAP_A
interact_plot(sens_int_lm2, pred = "MAP_A", modx = "MAP_100Y", x.label = "MAP (anomaly)", legend.main = "MAP (1901-2000)") + theme_apa() + theme(legend.title = element_text("MAT (1901-2000)")) +
geom_vline(xintercept = 0, lty = 2, col = "#808080")
ggsave(here::here("analyses", "figs1", "sens_3_figs", "clim_intplot_MAPb_v2.png"), height = 4, width = 6)
```



**Diagnostics & J-N plots**  





<br>  



#### Are certain regions more sensitive?  

Examine sensitivity by lat and long. 

If plants at lower latitudes flower earlier, are these early bloomers also more sensitive to climate???












