---
title: "Sensitivity Analyses"
author: "Devin Gamble"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r warning = FALSE, message = FALSE, echo = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(broom)
library(here)
library(ggplot2)
library(visreg)
library(jtools)
```

## Objective:  
#### Determine how sensitivity to different climate variables, for different seasons/months, and for long-term vs anomalouse climate varies  
- through time  
- Across space (lat, long, elev)  
- by climate region  



* See 'Climate_1.Rmd' for analyses identifying DOY sensitivity to different climatic variables. Also see 'EDA2.Rmd' for exploration of different models.  

<br>  

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load in data & establish error distance bins
nemo_spec <- read_csv(here::here("data_cleaning", "nemo_all_2.csv")) %>% 
  mutate(error_bin = case_when(error_dist_m <= 2000 ~ "<2 km",
                               error_dist_m > 2000 & error_dist_m <= 5000 ~ "2-5 km",
                               error_dist_m > 5000 & error_dist_m <= 10000 ~ "5-10 km",
                               error_dist_m > 10000 & error_dist_m <= 15000 ~ "10-15 km", 
                               error_dist_m > 15000 ~ ">15 km")) %>% 
  select(specimen_number:error_dist_m, error_bin, everything()) %>% mutate(error_bin = factor(error_bin, levels = c( "<2 km", "2-5 km", "5-10 km", "10-15 km", ">15 km"))) #specify factor & levels for error bin
#1764 total obs. #1240 obs with error distance
climNA_all <- read_csv(here::here("climateNA", "all_cna", "climNA_nemo_all.csv")) %>% 
  rename(year = YoC) #Also 1764 obs

#Transform Precipitation variables to be normal -- Log transforms Monthly and seasonal PPT, MAP, MSP #PAS ignored
climNA_all1 <- climNA_all %>% 
  mutate_at(vars(PPT01_N51:PPT12_N51, PPT_wt_N51:PPT_at_N51, MAP_N51, MSP_N51,
                 PPT01_N81:PPT12_N81, PPT_wt_N81:PPT_at_N81, MAP_N81, MSP_N81,
                 PPT01_100Y:PPT12_100Y, PPT_wt_100Y:PPT_at_100Y, MAP_100Y, MSP_100Y,
                 PPT01_L1:PPT12_L1, PPT_wt_L1:PPT_at_L1, MAP_L1, MSP_L1,
                 PPT01_Y:PPT12_Y, PPT_wt_Y:PPT_at_Y, MAP_Y, MSP_Y), log) %>% 
  na_if(y = -Inf)
#see EDA_climate for other variables to be transformed... (maybe AHM, DD if using)
#Transform anomalies after they are added to ClimNA_nemo_all csv!

#Merge herbarium records and climate data (by specimen number)
nemo_df1 <- merge(nemo_spec, climNA_all1) #1764 obs and 1181 total columns

#FILTER YEARS to those after 1901 (start of climate data).
nemo_df2 <- nemo_df1 %>% 
  filter(year >= 1901) #narrowed to 1677 obs, Same as YoC - 1
sum(!is.na(nemo_df2$MAT_L1)) #YoC-1
sum(!is.na(nemo_df2$MAT_Y)) #YoC

#Subsetting data by error bins
nemo_all_errors <- nemo_df2 %>% 
  filter(!is.na(error_dist_m)) #1166 after rm records before 1901
#0-5 km resolution
nemo_e0_5 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km" | error_bin == "2-5 km") #1033 entries
#0-2 km
nemo_e2 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km") #743 obs
```




## Variation in Phenological Sensitvity  

Using the slope of basic regression models (DOY ~ one climate variable)

### Phenological Sensitivity through time  

Climate Variables - 100Y average:  
- Tmin_sp  
- Tave_sp
- PPT_wt  
- PPT_sp




























