---
title: "Error Distance Analyses 2"
author: "Devin Gamble"
date: "8/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bootstrap Resampling Analyses  
on the effect of coordinate uncertainty (error distance) on pheno-climatic models  

*TO-DO*  
- Fix and validate bootstrap confidence intervals  
- **Standardize (Scale)** coefficient estimates (and CIs) for comparison among long-term climate and anomalies (be consistent)  
- Take a Bayesian approach instead...?  

Will increasing the 'R' value (# replicates) reduce the size of confidence intervals?  
No.  


```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(here)
library(ggplot2)
library(visreg)
library(jtools)
library(interactions)
library(kableExtra)
library(stringr)
```


#### Load Data  
```{r message = FALSE, warning = FALSE}
nemo_df2 <- read_csv(here::here("data_cleaning", "nemo_full_1901_2019.csv")) %>%  
  mutate(error_bin = as_factor(error_bin)) #Should this be ordered? #Combined specimen & climate data from 1901-2019
#1677 obs, 1251 columns

nemo_df1 <- read_csv(here::here("data_cleaning", "nemo_full_1861_2019.csv")) #Combined data for all years
#1764 obs, 1251 columns

options(contrasts = c("contr.sum", "contr.poly"))
```

Data subset by error distances/bins  
```{r message = FALSE, warning = FALSE}
#All errors
nemo_all_errors <- nemo_df2 %>% 
  filter(!is.na(error_dist_m)) 
#1239 out of 1764 obs with error distance
#1166 after rm records before 1901

#0-5 km resolution
nemo_e0_5 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km" | error_bin == "2-5 km") 

#0-4 km - not used here
nemo_e0_4 <-  nemo_all_errors %>% 
  filter(error_dist_m >= 0 & error_dist_m <= 4000) #Do Not include error_bin in models

#0-2 km
nemo_e2 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km") 

```

Smallest sample size is N = 743 in 0-2 km data subset. Randomly sample 743 obs from each subset and compare models.  
<br>  


## Bootstrap Resampling  

*Bins*  
- Original Data set  
- Error Distance present  
- 0-5 km error  
- 0-2 km error  

**Objective**  
1. Re-sample from the three larger data sets (OG, All errors, 0-5 km) at N = 743 (size of 0-2 km)  
2. For each resample, fit a pheno-climatic linear model (for each data set)  
3. Compare the parameter estimates (for climate variables) and confidence intervals based on xxxx samples  
4. Compute significance of differences between estimates among each data set  


**Early by-hand attempt** (Ignore)  
```{r message = FALSE, eval = FALSE}
# Attempt first with one data set

samplelm_params <- matrix(data = NA, nrow = 100, ncol = 8)
colnames(samplelm_params) <-  c("MAT_est", "MAP_est", "MAT_SE", "MAP_SE", "MAT_Clo", "MAT_Cup", "MAP_Cup", "MAP_Clo")


for(i in 1:100){
  #sample
  sample_og <- sample_n(nemo_df2, size = 743, replace = FALSE)

  #modeling
  lm_n <- lm(DOY ~ MAT_100Y + MAP_100Y, data = sample_og)
    
  #store coeffs, std.e [row, col]
  coeffs <- summary(lm_n)$coefficients[c(2:3),1] #2:3 to exclude intercept, inc MAT & MAP
  stde <- summary(lm_n)$coefficients[c(2:3),2]
  
  samplelm_params[i,] <- as.numeric(c(coeffs, stde, 
                            as.numeric(confint(object = lm_n, parm = 'MAT_100Y', level = 0.95)), 
                            as.numeric(confint(object = lm_n, parm = 'MAP_100Y', level = 0.95)))) #Calculate CIs. Must specify vars
  
} 
#for 1:1000, takes about a minute

####
# Significance Tests

# Are parameter estimates significantly different from 0? From each other wrt different error subsets?
#How much do the fits of each sample differ? (variance?)
#Cross-validation: estimate test error? Bootstrapping?

```

*t0 values do not reflect original regressions. - bootMed estimates are close but in some cases fall far outside of bootstrap confidence intervals. Find a straightforward & parsimonious way to display coefficient estimates and bootstrapped CIs*  


**Notes** from the ![CRAN R Newsletter](http://cran.fhcrc.org/doc/Rnews/Rnews_2002-3.pdf) on the `boot` package:
 - $t0$ is the "result of evaluating the statistic on the original dataset"
 - "bootstrap standard errors are 15–20% higher than the usual standard errors" from linear models
 - "The bootstrap normal interval assumes an asymptotic normal distribution an used the bootstrap estimates of bias and variance for the parameters of the distribution.
 - 
 
 
 
Parametric bootstrap (default 'sim' = ordinary, nonparametric)  


#### MAT & MAP Alone

Goal: Estimate the sampling distribution of a statistic (regression coefficient). The repeated sampling provides the bootstrap mean and SE of the metric. Mimics the sampling of our data from the population. Obtain sampling distribution of the metric.  
Default method for lm regression bootstrap is random-x or case resampling. Bias estimates the bias of the statistic relative to the true population value.  

**R** = 5000 replicates/resamples (Increase to 10000 did not appear to affect results)  
**t0** = original statistic (but not equal to summary.lm() estimates???)    

Confidence Intervals:  
- Norm type assumes estimates are normally distributed - looks accurate from histograms (below)  
- Alternative: BCA confint method - corrects for bias/skewedness in bootstrapped distribution, uses original estimates unlike norm method  
Note: Using BCa almost always leads to warning "extreme order statistics used as endpoints", so it may not be appropriate.  

**CI type: Norm seems most appropriate**  
Comparisons of different CI methods was done for different iterations of the bootstrap analysis. Normal, Basic, and BCA methods were highly similar. BCA methods were somewhat more restricted, but often "used extreme quantiles" and may be unstable.  

```{r alldata_100Y, message = FALSE}
library(boot) #Alternative: try Boot() ftn from `car` package - but provides very similar outputs
#Option: Set seed for reproducible result
set.seed(999)


#In boot() below, each call of the function is without replacement, but replacement = TRUE over multiple samples

#Create function to call in boot()
param_est <- function(df, index){ # df = data, index = # obs to inc [req by boot()]
  
  df_samp <- sample_n(df, size = 743, replace = FALSE) #boot() recomputes the function for each re-sample
  lm_c <- lm(DOY ~ MAT_100Y + MAP_100Y, data = df_samp)
  
  coef(lm_c)
}

#e.g. param_est(nemo_df2, 1:743)


#Save boostrapped data - all observations
boot_df2 <- boot(nemo_df2, param_est, 5000)



##### Confidence Intervals #### 

# -- by hand  
# Note: index = 2 for MAT, = 3 for MAP  #

#boot_df2_ci_MAT <- boot.ci(boot_df2, index = 2, conf = 0.95, type = 'norm') 
#boot_df2_ci_MAP <- boot.ci(boot_df2, index = 3, conf = 0.95, type = 'norm') #low ci is especially negative...
#Alternative: Confint method - car package


boot_df2_ci <- Confint(boot_df2, level = 0.95, type = "norm") #identical to boot.ci() #above#

#Compare different methods - MAP
#boot.ci(boot_df2, index = 3, conf = 0.95, type = c("basic", "norm", "bca", "perc"))


#Outputs
summary(boot_df2)
boot_df2_ci #confidence intervals are not constructed around bootstrap means/medians

#Compare to SEs in regular summary. #If SEs are similar b/w boot and original lm outputs, method is appropriate
summary(lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_df2))


#Plot
plot(boot_df2) #can specify index for different predictors (default = intercept)
hist(boot_df2, ci = 'norm', legend = "separate")

#Distribution of samples appear fairly normally distributed, though confidence intervals (horizontal black bars) are uneven. 
#Observed value of statistic = original estimate (bootMed)


boot_df2_gg <- data.frame(c(boot_df2$t0[2], boot_df2$t0[3]), boot_df2_ci[2:3, 1:2], c(mean(boot_df2$t[,2]), mean(boot_df2$t[,3])), c(median(boot_df2$t[,2]), median(boot_df2$t[,3]))) #save bootstrapped estimates for MAT, MAP 

boot_df2_ggp <- rownames_to_column(boot_df2_gg) %>% 
  mutate(data = "all")
colnames(boot_df2_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


```


```{r allerrors_100Y, message = FALSE}
###
# For the subset data:
###

###
#nemo_all_errors
boot_alle <- boot(nemo_all_errors, param_est, 5000)
boot_alle_ci <- Confint(boot_alle, level = 0.95, type = "norm")

#outputs
summary(boot_alle)
boot_alle_ci

#og lm
summary(lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_all_errors))

plot(boot_alle)
hist(boot_alle, ci = 'norm', legend = "separate") #CIs look super weird... which type to use???

boot_alle_gg <- data.frame(c(boot_alle$t0[2], boot_alle$t0[3]), boot_alle_ci[2:3, 1:2], c(mean(boot_alle$t[,2]), mean(boot_alle$t[,3])), c(median(boot_alle$t[,2]), median(boot_alle$t[,3])))

boot_alle_ggp <- rownames_to_column(boot_alle_gg) %>% 
  mutate(data = "all_E")
colnames(boot_alle_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


###
#nemo_e0_5
boot_05 <- boot(nemo_e0_5, param_est, 5000)
boot_05_ci <- Confint(boot_05, level = 0.95, type = "norm")

#outputs
summary(boot_05)
boot_05_ci

#og lm
summary(lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_e0_5))

plot(boot_05)
hist(boot_05, ci = 'norm', legend = "separate") 

boot_05_gg <- data.frame(c(boot_05$t0[2], boot_05$t0[3]), boot_05_ci[2:3, 1:2], c(mean(boot_05$t[,2]), mean(boot_05$t[,3])), c(median(boot_05$t[,2]), median(boot_05$t[,3])))

boot_05_ggp <- rownames_to_column(boot_05_gg) %>% 
  mutate(data = "05km")
colnames(boot_05_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


###
#nemo_e2 - should have identical results each time #Does not make sense to bootstrap this data set.

#boot_02 <- boot(nemo_e2, param_est, 1000)
#boot.ci(boot_02, index = 2, conf = 0.95, type = 'norm')
#plot(boot_02) - Same data, no distribution of estimates.

#lm sumamry
M100Y_02_lm <- lm(DOY ~ MAT_100Y + MAP_100Y, data = nemo_e2)
summary(M100Y_02_lm) 
#SEs from bootstrap are much much smaller but estimates are identical, as expected

confint(M100Y_02_lm, level = 0.95, type = "norm")

Nboot_02_gg <- data.frame(c(summary(M100Y_02_lm)$coefficient[2], summary(M100Y_02_lm)$coefficient[3]), confint(M100Y_02_lm, level = 0.95, type = "norm")[2:3, 1:2], NA, NA)

Nboot_02_ggp <- rownames_to_column(Nboot_02_gg) %>% 
  mutate(data = "02km")
colnames(Nboot_02_ggp) <-  c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


```


##### Plotting Coefficient Estimates with confidence intervals  
```{r message = FALSE}
##
# Comparing & Plotting bootstrapped parameter estimates
# 95% confidence intervals computed by COnfint (identical to boot.ci) using type = #### (norm)?

#Combine different subset boot estimates 

boots_alldata <- rbind(boot_df2_ggp, boot_alle_ggp, boot_05_ggp, Nboot_02_ggp) %>% 
  mutate(data = factor(data, levels = c("all", "all_E", "05km", "02km"))) 



ggplot(data = boots_alldata) +
  geom_errorbarh(aes(y = var, xmin = ci_2.5, xmax = ci_97.5, color = data), size = 1) +
  geom_point(aes(x = coefEst, y = var), size = 2) + 
  #geom_point(aes(x = bootMean, y = var), size = 2, col = "red") +
  geom_vline(xintercept = 0, lty = 2) +
  scale_x_continuous(breaks = seq(-10, 10, 1)) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap(~data, ncol = 1) +
  theme_bw()


##MANUAL construction of confidence intervals???


```


#### MAT & MAP + Other Covariates  
```{r message = FALSE}
#including year, elev_m, and long
param_estC <- function(df, index){ # df = data, index = # obs to inc [req by boot()]
  
  df_samp <- sample_n(df, size = 743, replace = FALSE) #boot() recomputes the function for each re-sample
  lm_c <- lm(DOY ~ MAT_100Y + MAP_100Y + year + elev_m + long, data = df_samp)
  
  coef(lm_c)
}

####
#ALL DATA
boot_df2C <- boot(nemo_df2, param_estC, 5000)
boot_df2C_ci <- Confint(boot_df2C, level = 0.95, type = "norm")

#outputs
summary(boot_df2C)
boot_df2C_ci
#og lm
summary(lm(DOY ~ MAT_100Y + MAP_100Y + year + elev_m + long, data = nemo_df2))

plot(boot_df2C) #can specify index for different predictors (default = intercept)
hist(boot_df2C, ci = 'norm', legend = "separate")

#Save to df for plotting
boot_df2C_gg <- data.frame(c(boot_df2C$t0[2], boot_df2C$t0[3]), boot_df2C_ci[2:3, 1:2], c(mean(boot_df2C$t[,2]), mean(boot_df2C$t[,3])), c(median(boot_df2C$t[,2]), median(boot_df2C$t[,3]))) 

boot_df2C_ggp <- rownames_to_column(boot_df2C_gg) %>% 
  mutate(data = "all")
colnames(boot_df2C_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")



###
# ALL ERRORS
boot_alleC <- boot(nemo_all_errors, param_estC, 5000)
boot_alleC_ci <- Confint(boot_alleC, level = 0.95, type = "norm")

#outputs
summary(boot_alleC)
boot_alleC_ci

#og lm
summary(lm(DOY ~ MAT_100Y + MAP_100Y + year + elev_m + long, data = nemo_all_errors))

plot(boot_alleC)
hist(boot_alleC, ci = 'norm', legend = "separate") 

#Compare different methods - MAP
#boot.ci(boot_df2C, index = 3, conf = 0.95, type = c("basic", "norm", "bca", "perc"))


boot_alleC_gg <- data.frame(c(boot_alleC$t0[2], boot_alleC$t0[3]), boot_alleC_ci[2:3, 1:2], c(mean(boot_alleC$t[,2]), mean(boot_alleC$t[,3])), c(median(boot_alleC$t[,2]), median(boot_alleC$t[,3])))

boot_alleC_ggp <- rownames_to_column(boot_alleC_gg) %>% 
  mutate(data = "all_E")
colnames(boot_alleC_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


###
# 0-5 KM
boot_05C <- boot(nemo_e0_5, param_estC, 5000)
boot_05C_ci <- Confint(boot_05C, level = 0.95, type = "norm")

#outputs
summary(boot_05C)
boot_05C_ci

#og lm
summary(lm(DOY ~ MAT_100Y + MAP_100Y + year + elev_m + long, data = nemo_e0_5))

plot(boot_05C)
hist(boot_05C, ci = 'norm', legend = "separate") 

boot_05C_gg <- data.frame(c(boot_05C$t0[2], boot_05C$t0[3]), boot_05C_ci[2:3, 1:2], c(mean(boot_05C$t[,2]), mean(boot_05C$t[,3])), c(median(boot_05C$t[,2]), median(boot_05C$t[,3])))

boot_05C_ggp <- rownames_to_column(boot_05C_gg) %>% 
  mutate(data = "05km")
colnames(boot_05C_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


###
# 0-2 KM (no bootstrap)

#og lm
M100Y_02C_lm <- lm(DOY ~ MAT_100Y + MAP_100Y + year + elev_m + long, data = nemo_e2)
summary(M100Y_02C_lm)

confint(M100Y_02C_lm, level = 0.95, type = "norm")

Nboot_02C_gg <- data.frame(c(summary(M100Y_02C_lm)$coefficient[2], summary(M100Y_02C_lm)$coefficient[3]), confint(M100Y_02C_lm, level = 0.95, type = "norm")[2:3, 1:2], NA, NA)

Nboot_02C_ggp <- rownames_to_column(Nboot_02C_gg) %>% 
  mutate(data = "02km")
colnames(Nboot_02C_ggp) <-  c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")
```


```{r message = FALSE}
##GGPLOT of Bootstrapped models + covariates
boots_alldataC <- rbind(boot_df2C_ggp, boot_alleC_ggp, boot_05C_ggp, Nboot_02C_ggp) %>% 
  mutate(data = factor(data, levels = c("all", "all_E", "05km", "02km")))


ggplot(data = boots_alldataC) +
  geom_errorbarh(aes(y = var, xmin = ci_2.5, xmax = ci_97.5, color = data), size = 1) +
  geom_point(aes(x = coefEst, y = var), size = 2) + 
  #geom_point(aes(x = bootMean, y = var), size = 2, col = "red") +
  geom_vline(xintercept = 0, lty = 2) +
  scale_x_continuous(breaks = seq(-10, 24, 2)) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap(~data, ncol = 1) +
  theme_bw()

ggsave(here::here("analyses", "figs1", "errorD", "errorboots_100Y_t0.png"), width = 6, height = 4)



```

<br>  


#### MAT & MAP ANOMALIES + Other Covariates  

##### Anomalies    
```{r warning = FALSE, message = FALSE}
param_estA <- function(df, index){ # df = data, index = # obs to inc [req by boot()]
  
  df_samp <- sample_n(df, size = 743, replace = FALSE) #boot() recomputes the function for each re-sample
  lm_a <- lm(DOY ~ MAT_A + MAP_A + year + elev_m + long, data = df_samp)
  
  coef(lm_a)
}

####
#ALL DATA
boot_df2A <- boot(nemo_df2, param_estA, 5000)
boot_df2A_ci <- Confint(boot_df2A, level = 0.95, type = "norm")

#outputs
summary(boot_df2A)
boot_df2A_ci
#og lm
summary(lm(DOY ~ MAT_A + MAP_A + year + elev_m + long, data = nemo_df2))

plot(boot_df2A) 
hist(boot_df2A, ci = 'norm', legend = "separate")

#Compare different methods - MAP
boot.ci(boot_df2A, index = 3, conf = 0.95, type = c("basic", "norm", "bca", "perc"))

#Save to df for plotting
boot_df2A_gg <- data.frame(c(boot_df2A$t0[2], boot_df2A$t0[3]), boot_df2A_ci[2:3, 1:2], c(mean(boot_df2A$t[,2]), mean(boot_df2A$t[,3])), c(median(boot_df2A$t[,2]), median(boot_df2A$t[,3]))) #Just estimates for MAT, MAP Anoms

boot_df2A_ggp <- rownames_to_column(boot_df2A_gg) %>% 
  mutate(data = "all")
colnames(boot_df2A_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")



###
# ALL ERRORS
boot_alleA <- boot(nemo_all_errors, param_estA, 5000)
boot_alleA_ci <- Confint(boot_alleA, level = 0.95, type = "norm")

#outputs
summary(boot_alleA)
boot_alleA_ci

#og lm
summary(lm(DOY ~ MAT_A + MAP_A + year + elev_m + long, data = nemo_all_errors))

plot(boot_alleA)
hist(boot_alleA, ci = 'norm', legend = "separate") 

boot_alleA_gg <- data.frame(c(boot_alleA$t0[2], boot_alleA$t0[3]), boot_alleA_ci[2:3, 1:2], c(mean(boot_alleA$t[,2]), mean(boot_alleA$t[,3])), c(median(boot_alleA$t[,2]), median(boot_alleA$t[,3])))

boot_alleA_ggp <- rownames_to_column(boot_alleA_gg) %>% 
  mutate(data = "all_E")
colnames(boot_alleA_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


###
# 0-5 KM
boot_05A <- boot(nemo_e0_5, param_estA, 5000)
boot_05A_ci <- Confint(boot_05A, level = 0.95, type = "norm")

#outputs
summary(boot_05A)
boot_05A_ci

#og lm
summary(lm(DOY ~ MAT_A + MAP_A + year + elev_m + long, data = nemo_e0_5))

plot(boot_05A)
hist(boot_05A, ci = 'norm', legend = "separate") 

boot_05A_gg <- data.frame(c(boot_05A$t0[2], boot_05A$t0[3]), boot_05A_ci[2:3, 1:2], c(mean(boot_05A$t[,2]), mean(boot_05A$t[,3])), c(median(boot_05A$t[,2]), median(boot_05A$t[,3])))

boot_05A_ggp <- rownames_to_column(boot_05A_gg) %>% 
  mutate(data = "05km")
colnames(boot_05A_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


###
# 0-2 KM (no bootstrap)

#og lm
M100Y_02A_lm <- lm(DOY ~ MAT_A + MAP_A + year + elev_m + long, data = nemo_e2)
summary(M100Y_02A_lm)

confint(M100Y_02A_lm, level = 0.95, type = "norm")

Nboot_02A_gg <- data.frame(c(summary(M100Y_02A_lm)$coefficient[2], summary(M100Y_02A_lm)$coefficient[3]), confint(M100Y_02A_lm, level = 0.95, type = "norm")[2:3, 1:2], NA, NA)

Nboot_02A_ggp <- rownames_to_column(Nboot_02A_gg) %>% 
  mutate(data = "02km")
colnames(Nboot_02A_ggp) <-  c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")

```


```{r message = FALSE}
##GGPLOT of Bootstrapped models: Anoms + other covariates
boots_alldataA <- rbind(boot_df2A_ggp, boot_alleA_ggp, boot_05A_ggp, Nboot_02A_ggp) %>% 
  mutate(data = factor(data, levels = c("all", "all_E", "05km", "02km")))


#STANDARDIZE VALUES
ggplot(data = boots_alldataA) +
  geom_errorbarh(aes(y = var, xmin = ci_2.5, xmax = ci_97.5, color = data), size = 1) +
  geom_point(aes(x = coefEst, y = var), size = 2) + 
  #geom_point(aes(x = bootMean, y = var), size = 2, col = "red") +
  geom_vline(xintercept = 0, lty = 2) +
  scale_x_continuous(breaks = seq(-10, 10, 1)) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap(~data, ncol = 1) +
  theme_bw()

ggsave(here::here("analyses", "figs1", "errorD", "errorboots_ANOM_t0.png"), width = 6, height = 4)

```
<br>  


##### Anomalies + 100Y  
*EXCLUDE: CIs are VERY STRANGE here!*  

```{r warning = FALSE, message = FALSE}
param_estAL <- function(df, index){ # df = data, index = # obs to inc [req by boot()]
  
  df_samp <- sample_n(df, size = 743, replace = FALSE) #boot() recomputes the function for each re-sample
  lm_al <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + year + elev_m + long, data = df_samp)
  
  coef(lm_al)
}

####
#ALL DATA
boot_df2AL <- boot(nemo_df2, param_estAL, 5000)
boot_df2AL_ci <- Confint(boot_df2AL, level = 0.95, type = "norm")

boot_df2AL_ci2 <- boot.ci(boot_df2AL, index = 3, conf = 0.95, type = "norm")

#outputs
summary(boot_df2AL)
boot_df2AL_ci
#og lm
summary(lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + year + elev_m + long, data = nemo_df2))

plot(boot_df2AL) 
hist(boot_df2AL, ci = 'norm', legend = "separate")

#Save to df for plotting
boot_df2AL_gg <- data.frame(c(boot_df2AL$t0[2], boot_df2AL$t0[3], boot_df2AL$t0[4], boot_df2AL$t0[5]), boot_df2AL_ci[2:5, 1:2], c(mean(boot_df2AL$t[,2]), mean(boot_df2AL$t[,3]), mean(boot_df2AL$t[,4]), mean(boot_df2AL$t[,5])), c(median(boot_df2AL$t[,2]), median(boot_df2AL$t[,3]), median(boot_df2AL$t[,4]), median(boot_df2AL$t[,5]))) #Just estimates for MAT, MAP Anoms

boot_df2AL_ggp <- rownames_to_column(boot_df2AL_gg) %>% 
  mutate(data = "all")
colnames(boot_df2AL_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")



###
# ALL ERRORS
boot_alleAL <- boot(nemo_all_errors, param_estAL, 5000)
boot_alleAL_ci <- Confint(boot_alleAL, level = 0.95, type = "norm")

#outputs
summary(boot_alleAL)
boot_alleAL_ci

#Check different CI types
boot.ci(boot_alleAL, index = 3, conf = 0.95, type = c("basic", "norm", "bca", "perc"))

#og lm
summary(lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + year + elev_m + long, data = nemo_all_errors))

plot(boot_alleAL)
hist(boot_alleAL, ci = 'norm', legend = "separate") 

boot_alleAL_gg <- data.frame(c(boot_alleAL$t0[2], boot_alleAL$t0[3], boot_alleAL$t0[4], boot_alleAL$t0[5]), boot_alleAL_ci[2:5, 1:2], c(mean(boot_alleAL$t[,2]), mean(boot_alleAL$t[,3]), mean(boot_alleAL$t[,4]), mean(boot_alleAL$t[,5])), c(median(boot_alleAL$t[,2]), median(boot_alleAL$t[,3]), median(boot_alleAL$t[,4]), median(boot_alleAL$t[,5])))

boot_alleAL_ggp <- rownames_to_column(boot_alleAL_gg) %>% 
  mutate(data = "all_E")
colnames(boot_alleAL_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


###
# 0-5 KM
boot_05AL <- boot(nemo_e0_5, param_estAL, 5000)
boot_05AL_ci <- Confint(boot_05AL, level = 0.95, type = "norm")

#outputs
summary(boot_05AL)
boot_05AL_ci

#og lm
summary(lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + year + elev_m + long, data = nemo_e0_5))

plot(boot_05AL)
hist(boot_05AL, ci = 'norm', legend = "separate") 

boot_05AL_gg <- data.frame(c(boot_05AL$t0[2], boot_05AL$t0[3], boot_05AL$t0[4], boot_05AL$t0[5]), boot_05AL_ci[2:5, 1:2], c(mean(boot_05AL$t[,2]), mean(boot_05AL$t[,3]), mean(boot_05AL$t[,4]), mean(boot_05AL$t[,5])), c(median(boot_05AL$t[,2]), median(boot_05AL$t[,3]), median(boot_05AL$t[,4]), median(boot_05AL$t[,5])))

boot_05AL_ggp <- rownames_to_column(boot_05AL_gg) %>% 
  mutate(data = "05km")
colnames(boot_05AL_ggp) <- c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")


###
# 0-2 KM (no bootstrap)

#og lm
M100Y_02AL_lm <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + year + elev_m + long, data = nemo_e2)
summary(M100Y_02AL_lm)

confint(M100Y_02AL_lm, level = 0.95, type = "norm")

Nboot_02AL_gg <- data.frame(c(summary(M100Y_02AL_lm)$coefficient[2], summary(M100Y_02AL_lm)$coefficient[3], summary(M100Y_02AL_lm)$coefficient[4], summary(M100Y_02AL_lm)$coefficient[5]), confint(M100Y_02AL_lm, level = 0.95, type = "norm")[2:5, 1:2], NA, NA)

Nboot_02AL_ggp <- rownames_to_column(Nboot_02AL_gg) %>% 
  mutate(data = "02km")
colnames(Nboot_02AL_ggp) <-  c("var", "coefEst", "ci_2.5", "ci_97.5", "bootMean", "bootMed", "data")

```


```{r message = FALSE}
##GGPLOT of Bootstrapped models: Anoms + other covariates
boots_alldataAL <- rbind(boot_df2AL_ggp, boot_alleAL_ggp, boot_05AL_ggp, Nboot_02AL_ggp) %>% 
  mutate(data = factor(data, levels = c("all", "all_E", "05km", "02km")))

#Change colors of Anomalies!

ggplot(data = boots_alldataAL) +
  geom_errorbarh(aes(y = var, xmin = ci_2.5, xmax = ci_97.5, color = data), size = 1) +
  geom_point(aes(x = coefEst, y = var), size = 2) + 
  #geom_point(aes(x = bootMean, y = var), size = 2, col = "red") +
  geom_vline(xintercept = 0, lty = 2) +
  scale_x_continuous(breaks = seq(-10, 10, 1)) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap(~data, ncol = 1) +
  theme_bw()


```
It appears like there may be more variation in MAT anomalies compared to MAT_100Y. *Make sure nothing weird is happening with these estimates!*  

---  




