---
title: "bias_error2b"
author: "Devin Gamble"
date: "4/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(here)
library(ggplot2)
library(visreg)
library(jtools)
```



# Bootstrap Resampling Analysis  
(Second iteration)



B: Bayesian Approach

*Notes:*  
- Fix and validate bootstrap confidence intervals  
- **Standardize (Scale)** coefficient estimates (and CIs) for comparison among long-term climate and anomalies (be consistent)  


Load Data  
```{r message = FALSE, warning = FALSE}
nemo_df2 <- read_csv(here::here("data_cleaning", "nemo_full_1901_2019.csv")) %>%  
  mutate(error_bin = as_factor(error_bin)) #Should this be ordered? #Combined specimen & climate data from 1901-2019
#1677 obs, 1251 columns

nemo_df1 <- read_csv(here::here("data_cleaning", "nemo_full_1861_2019.csv")) #Combined data for all years
#1764 obs, 1251 columns

options(contrasts = c("contr.sum", "contr.poly"))
```

Data subset by error distances/bins  
```{r message = FALSE, warning = FALSE}
#All errors
nemo_all_errors <- nemo_df2 %>% 
  filter(!is.na(error_dist_m)) 
#1239 out of 1764 obs with error distance
#1166 after rm records before 1901

#0-5 km resolution
nemo_e0_5 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km" | error_bin == "2-5 km") 

#0-2 km
nemo_e2 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km") 

```

*Bins*  
- Original Data set  
- Error Distance present  
- 0-5 km error  
- 0-2 km error  


## Bayesian PCMs

Construct simple linear models (PCMs) and compare estimates among error distance subsets (as done in `bias_error.Rmd`), but now use a Bayesian method instead.


```{r warning = FALSE}
#Bayesian Packages
#library("rstan")
#options: 

library(rethinking)
library(bayesplot)
options(mc.cores = parallel::detectCores()) #faster model computation
#rstan_options(auto_write = TRUE) #bypass re-compiling

source("../error_distance/helper.R") #functions by Stephen Proulx for improving the ease of use of 'rethinking' functions

```

Use 'ulam()' for HMCMC 

### Annual Climate models  
Long-term conditions  

*Select Data* for use in ulam models

```{r}
nemo_bd <- nemo_df2 %>% 
  select(DOY, MAT_100Y, MAP_100Y, MAT_A, MAP_A, elev_m, long, year) %>% 
  rename(lons = long) %>% #long reserved, use 'lons' instead
  mutate(DOY = scale(DOY, scale = FALSE), elev_m = scale(elev_m), lons = scale(lons), year = scale(year), MAT_100Y = scale(MAT_100Y), MAP_100Y = scale(MAP_100Y), MAT_A = scale(MAT_A), MAP_A = scale(MAP_A)) #center/standardize variables (DOY only centered)

```

```{r eval = FALSE}
#Base model, regular regression
base_lm1 <- lm(DOY ~ MAT_100Y + MAP_100Y + elev_m + lons + year, data = nemo_bd)
summary(base_lm1)

base_lm2 <- lm(DOY ~ MAT_100Y + MAP_100Y + MAT_A + MAP_A + elev_m + lons + year, data = nemo_bd)
summary(base_lm2)
summ(base_lm2, vif = TRUE)

```

#### All Records

```{r}
set.seed(100)

ann_clim_b1 <- ulam(alist(
  
    DOY ~ dnorm(mu, sigma), #DOY is normally distributed
    mu <- alpha + bTL*MAT_100Y + bPL*MAP_100Y + bTA*MAT_A + bPA*MAP_A + bE*elev_m + bL*lons + bY*year,
    alpha ~ dnorm(0, 1), #prior sigmas for coeffs = 2
    bTL ~ dnorm(-2, 2), #priors chosen based coeffs from OLS regression
    bPL ~ dnorm(6, 2),
    bTA ~ dnorm(-3, 2),
    bPA ~ dnorm(1, 2),
    bE ~ dnorm(0, 2), #nonclimatic var.s mean = 0 prior
    bL ~ dnorm(0, 2),
    bY ~ dnorm(0, 1),
    sigma ~ dexp(1)), #best prior for sigma...?
  
  data = select(nemo_bd, DOY, MAT_100Y, MAP_100Y, MAT_A, MAP_A, elev_m, lons, year), chains = 2, iter = 5000)
#add loglik = TRUE to make AIC comparisons

precis(ann_clim_b1)
#Looks pretty good


```

Inspect Posterior
```{r}
#Additional diagnostic checks

plot(ann_clim_b1)
traceplot(ann_clim_b1)

#Coeffs Post
post_ann_clim_b1 <- extract.samples(ann_clim_b1@stanfit) %>% 
  as_tibble() %>% mutate(dset = "All") #samples 10,000 obs from the posterior

bayesplot::mcmc_intervals(select(post_ann_clim_b1, bTL, bPL, bTA, bPA))

```

#### All Error records

```{r}
nemo_bdE <- nemo_all_errors %>% 
  select(DOY, MAT_100Y, MAP_100Y, MAT_A, MAP_A, elev_m, long, year) %>% 
  rename(lons = long) %>% #long reserved, use 'lons' instead
  mutate(DOY = scale(DOY, scale = FALSE), elev_m = scale(elev_m), lons = scale(lons), year = scale(year), MAT_100Y = scale(MAT_100Y), MAP_100Y = scale(MAP_100Y), MAT_A = scale(MAT_A), MAP_A = scale(MAP_A))

ann_clim_b1E <- ulam(alist(
  
    DOY ~ dnorm(mu, sigma), #DOY is normally distributed
    mu <- alpha + bTL*MAT_100Y + bPL*MAP_100Y + bTA*MAT_A + bPA*MAP_A + bE*elev_m + bL*lons + bY*year,
    alpha ~ dnorm(0, 1), #prior sigmas for coeffs = 2
    bTL ~ dnorm(-2, 2), #priors chosen based coeffs from OLS regression
    bPL ~ dnorm(6, 2),
    bTA ~ dnorm(-3, 2),
    bPA ~ dnorm(1, 2),
    bE ~ dnorm(0, 2), #nonclimatic var.s mean = 0 prior
    bL ~ dnorm(0, 2),
    bY ~ dnorm(0, 1),
    sigma ~ dexp(1)), #best prior for sigma...?
  
  data = select(nemo_bdE, DOY, MAT_100Y, MAP_100Y, MAT_A, MAP_A, elev_m, lons, year), chains = 2, iter = 5000)


precis(ann_clim_b1E)


```

#### 0-5 km records

```{r}
nemo_bd5k <- nemo_e0_5 %>% 
  select(DOY, MAT_100Y, MAP_100Y, MAT_A, MAP_A, elev_m, long, year) %>% 
  rename(lons = long) %>% #long reserved, use 'lons' instead
  mutate(DOY = scale(DOY, scale = FALSE), elev_m = scale(elev_m), lons = scale(lons), year = scale(year), MAT_100Y = scale(MAT_100Y), MAP_100Y = scale(MAP_100Y), MAT_A = scale(MAT_A), MAP_A = scale(MAP_A))

ann_clim_b15 <- ulam(alist(
  
    DOY ~ dnorm(mu, sigma), #DOY is normally distributed
    mu <- alpha + bTL*MAT_100Y + bPL*MAP_100Y + bTA*MAT_A + bPA*MAP_A + bE*elev_m + bL*lons + bY*year,
    alpha ~ dnorm(0, 1), #prior sigmas for coeffs = 2
    bTL ~ dnorm(-2, 2), #priors chosen based coeffs from OLS regression
    bPL ~ dnorm(6, 2),
    bTA ~ dnorm(-3, 2),
    bPA ~ dnorm(1, 2),
    bE ~ dnorm(0, 2), #nonclimatic var.s mean = 0 prior
    bL ~ dnorm(0, 2),
    bY ~ dnorm(0, 1),
    sigma ~ dexp(1)), #best prior for sigma...?
  
  data = select(nemo_bd5k, DOY, MAT_100Y, MAP_100Y, MAT_A, MAP_A, elev_m, lons, year), chains = 2, iter = 5000)


precis(ann_clim_b15)


```

#### 0-2 km records

```{r}
nemo_bd2k <- nemo_e2 %>% 
  select(DOY, MAT_100Y, MAP_100Y, MAT_A, MAP_A, elev_m, long, year) %>% 
  rename(lons = long) %>% #long reserved, use 'lons' instead
  mutate(DOY = scale(DOY, scale = FALSE), elev_m = scale(elev_m), lons = scale(lons), year = scale(year), MAT_100Y = scale(MAT_100Y), MAP_100Y = scale(MAP_100Y), MAT_A = scale(MAT_A), MAP_A = scale(MAP_A))

ann_clim_b12 <- ulam(alist(
  
    DOY ~ dnorm(mu, sigma), #DOY is normally distributed
    mu <- alpha + bTL*MAT_100Y + bPL*MAP_100Y + bTA*MAT_A + bPA*MAP_A + bE*elev_m + bL*lons + bY*year,
    alpha ~ dnorm(0, 1), #prior sigmas for coeffs = 2
    bTL ~ dnorm(-2, 2), #priors chosen based coeffs from OLS regression
    bPL ~ dnorm(6, 2),
    bTA ~ dnorm(-3, 2),
    bPA ~ dnorm(1, 2),
    bE ~ dnorm(0, 2), #nonclimatic var.s mean = 0 prior
    bL ~ dnorm(0, 2),
    bY ~ dnorm(0, 1),
    sigma ~ dexp(1)), #best prior for sigma...?
  
  data = select(nemo_bd2k, DOY, MAT_100Y, MAP_100Y, MAT_A, MAP_A, elev_m, lons, year), chains = 2, iter = 5000)


precis(ann_clim_b12)


```

**Examine Posteriors**:

```{r}
post_ann_clim_b1E <- extract.samples(ann_clim_b1E@stanfit) %>% 
  as_tibble() %>% mutate(dset = "Error")
post_ann_clim_b15 <- extract.samples(ann_clim_b15@stanfit) %>% 
  as_tibble() %>% mutate(dset = "0-5 km")
post_ann_clim_b12 <- extract.samples(ann_clim_b12@stanfit) %>% 
  as_tibble()  %>% mutate(dset = "0-2 km")



bayesplot::mcmc_areas(select(post_ann_clim_b1, bTL, bPL, bTA, bPA), point_est = "mean", prob = 0.95) #95% Outer Probability Mass (default = 1)
bayesplot::mcmc_areas(select(post_ann_clim_b1E, bTL, bPL, bTA, bPA), point_est = "mean", prob = 0.95)
bayesplot::mcmc_areas(select(post_ann_clim_b15, bTL, bPL, bTA, bPA), point_est = "mean", prob = 0.95)
bayesplot::mcmc_areas(select(post_ann_clim_b12, bTL, bPL, bTA, bPA), point_est = "mean", prob = 0.95)
#Interior HDPI/HDR = 50%
```



Combine model outputs in coeff plots
```{r}
library(reshape2)
library(stringr)

summ_table <- rbind(post_ann_clim_b1, post_ann_clim_b1E, post_ann_clim_b15, post_ann_clim_b12) %>% 
  melt(id.vars = c("dset"), measure.vars = c("bTL", "bPL", "bTA", "bPA"), variable.name = "Parameter", value.name = "coeff")

summ_table1 <- group_by(summ_table, dset, Parameter) %>% 
  summarize(mean.coeff = mean(coeff),
            low.coeff = quantile(coeff, 0.025),
            high.coeff = quantile(coeff, 0.975)) %>% 
  ungroup() %>% 
  mutate(dset = factor(dset, levels = c("All", "Error", "0-5 km", "0-2 km"))) %>%  
  mutate(Parameter = recode_factor(Parameter, bTL = "MAT_100Y", bTA= "MAT_A", bPL= "MAP_100Y", bPA = "MAP_A", .ordered = TRUE))


ggplot(data = summ_table1) + 
  geom_errorbarh(aes(y = Parameter, xmin = low.coeff, xmax = high.coeff, color = dset), size = 1) +
  geom_point(aes(x = mean.coeff, y = Parameter), size = 2) + 
  geom_vline(xintercept = 0, lty = 2) +
  facet_wrap(~dset, ncol = 1) +
  labs(color = "Data set", x = "Estimate (standardized)") +
  theme_bw()

ggsave(here::here("analyses", "figs1", "errorD", "Bayes_error_comp1.png"), width = 6, height = 4)

```



**Objective**  
1. Re-sample from the three larger data sets (OG, All errors, 0-5 km) at N = 743 (size of 0-2 km)  
2. For each resample, fit a pheno-climatic linear model (for each data set)  
3. Compare the parameter estimates (for climate variables) and confidence intervals based on xxxx samples  
4. Compute significance of differences between estimates among each data set  

