---
title: "Error Distance Analyses 3a"
author: "Devin Gamble"
date: "11/21/2020"
output: html_document
---

# Simulations of new coordinates (based on error distance) on pheno-climatic models  



```{r echo = FALSE, message = FALSE, warning = FALSE}
#Load Packages
library(car)
library(tidyverse)
library(here)
library(ggplot2)
library(visreg)
library(jtools)
library(interactions)
library(kableExtra)
library(stringr)
```


#### Load Data  
```{r message = FALSE, warning = FALSE}
nemo_df2 <- read_csv(here::here("data_cleaning", "nemo_full_1901_2019.csv")) %>%  
  mutate(error_bin = as_factor(error_bin)) #Should this be ordered? #Combined specimen & climate data from 1901-2019
#1677 obs, 1251 columns

nemo_df1 <- read_csv(here::here("data_cleaning", "nemo_full_1861_2019.csv")) #Combined data for all years
#1764 obs, 1251 columns

options(contrasts = c("contr.sum", "contr.poly"))
```

Data subset by error distances/bins  
```{r message = FALSE, warning = FALSE}
#All errors
nemo_all_errors <- nemo_df2 %>% 
  filter(!is.na(error_dist_m)) 
#1239 out of 1764 obs with error distance
#1166 after rm records before 1901

#0-5 km resolution
nemo_e0_5 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km" | error_bin == "2-5 km") 

#0-4 km - not used here
nemo_e0_4 <-  nemo_all_errors %>% 
  filter(error_dist_m >= 0 & error_dist_m <= 4000) #Do Not include error_bin in models

#0-2 km
nemo_e2 <- nemo_all_errors %>% 
  filter(error_bin == "<2 km") 

```
<br>  



## Randomly simulated coordinates (lat/long) by a set error distance  

How does varying point coordinates by different error distances affect pheno-climatic models?  

Steps:  
1. Assign each record (of the 0-2 km set) four sets of new coordinates, each dispersed in a random direction from the original  
  - 2 km away  
  - 5 km away  
  - 15 km away  
  - 25 km away  
2. Obtain climate data for each new coordinate set:
  - MAT_100Y, MAP_100Y  
  - MAT_A, MAP_A  
  - (Tmin_wt + sp, PPT_wt + sp)  
3. Compare models of the original 2 km data set with those of the 4 new data sets  
4. Replication (5x)  

<br>  

Determining new coordinates based on km will depend on the present latitude and longitude of a collection. Simulations here are based off a subset of the original data for which confidence in specimen collection locations is high (0-2 km) so that deviations in the parameter estimates and $R^2$ values of models from simulated data can be attributed to effects of real differences in collection uncertainty AND locations. Use the WGS84 ellipsoid (the datum used for the majority of records; some NAD83 and NAD27 [*calculate % in 0-2km data - specify WGS4 or NAD83/27 method?*]) to calculate new decimal degrees based on some km deviation at each record. 

"geosphere" package -> `destPoint()` function computes a new coordinate point (WGS84) when given a start point, initial bearing, and distance.  


*NOTE*: Differences between the WGS84 and NAD83 geodetic datum are minuscule and assumed to not have an impact on the estimation of new coordinates.  

### Assign new coordinates  

#### 2 km displacement  

```{r}
library(geosphere)
nemo_r_2 <- nemo_e2 %>% 
  select(specimen_number:mature_5) #exclude existing climate data

#destPoint from geosphere package - e.g.
destPoint(p = c(-120.0312, 37.47905), b = 45, d = 2000) #default WGS84
#Seems pretty accurate!!! (Compared start and end points in Google maps)


##
### Goal: apply destPoint() to all existing lat/long to get new lat/long, each with *different* random bearing

#Basic for loop
  long_n1 <- rep(NA, nrow(nemo_r_2))
  lat_n1 <- rep(NA, nrow(nemo_r_2))
  
for(i in 1:length(nemo_r_2$lat)){
  
  
  latlong_n <- destPoint(p = c(nemo_r_2$long[i], nemo_r_2$lat[i]), b = sample(0:360, 1), d = 1000)
  
  long_n1[i] <-  latlong_n[1]
  lat_n1[i] <-  latlong_n[2]
   
}


#######
# 2 km error new coords
#######
#Simulations + for loop

  
sim_list_2ka <- list()

for(x in 1:5){ #5 reps (10 reps was too much for my cpu to handle...)
  
  long_n1 <- rep(NA,nrow(nemo_r_2))
  lat_n1 <- rep(NA, nrow(nemo_r_2))

  
for(i in 1:length(nemo_r_2$lat)){
  
  latlong_n <- destPoint(p = c(nemo_r_2$long[i], nemo_r_2$lat[i]), b = sample(0:360, 1), d = runif(1, 0, 2000))
  
  long_n1[i] <-  latlong_n[1]
  lat_n1[i] <-  latlong_n[2]
   
}
  
  sim_list_2ka[[x]] <- cbind(nemo_r_2$specimen_number, long_n1, lat_n1)
  colnames(sim_list_2ka[[x]]) <- c("specimen_number", "long_n2k", "lat_n2k")
  
  print(x)
  
}
  
  
#Rbind all list elements

  
#Using bind_rows()
#sims_all_2ka <- bind_rows(sim_list_2ka[[1:10]])


#using reduce() 
sims_all_2ka <- as.data.frame(reduce(sim_list_2ka, rbind)) %>% 
  mutate(replicate = c(rep("rep1", times = 743), rep("rep2", times = 743), rep("rep3", times = 743), rep("rep4", times = 743), rep("rep5", times = 743))) %>% 
  mutate(long_n2k = as.numeric(long_n2k), lat_n2k = as.numeric(lat_n2k))
```

##### Add elevation to records (optional for ClimateNA) -- **RUN MANUALLY**  
**Very time-consuming!!!**  
```{r message = FALSE, eval = FALSE}
#Add elevation
library(elevatr)
prj_dd <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs" #Define parameters for get_elev_point()


sims_all_2kaE$elev_m_n <- get_elev_point(sims_all_2ka[,2:3], prj = prj_dd, src = "epqs")$elevation #store only elev, function creates new df...


sims_all_2kaE2 <- sims_all_2ka %>% 
  mutate(elev_m_n = sims_all_2kaE[[1]]) 


#save as CSV before something fucks up and I have to rerun the 3h elev grab code
write_csv(sims_all_2kaE2, here::here("analyses", "new_coords", "sims_2ka.csv"))


#E.g. 2, 5, 15, 25 km coords all in same csv...?
```

**Load csv w/ elevation**  

```{r message = FALSE}
sims_2KE <- read_csv(here::here("analyses", "new_coords", "sims_2ka.csv")) %>% 
  filter(!elev_m_n < 0) %>%  #remove records with negative elevation
  filter(replicate %in% c("rep1", "rep2", "rep3", "rep4", "rep5")) # Remove replicates 6-10 (previously generated)
```

<br>  

**Standardize & Save CSV for ClimateNA data extraction**  
Columns: ID1, ID2, lat, long,	el  

```{r message = FALSE, eval = FALSE}
# 2 km simulated coordinates 
#Maybe have ID2 = replicate identifier?

sims_2KE_s <- sims_2KE %>% 
  select(specimen_number, replicate, lat_n2k, long_n2k, elev_m_n) %>% 
  rename(ID1 = specimen_number, ID2 = replicate, lat = lat_n2k, long = long_n2k, el = elev_m_n)

#Using replicate as a second ID -- will have to add YoC back in later for calculating anomalies

write_csv(sims_2KE_s, here::here("analyses", "new_coords", "sims_2ka_s.csv"))


```
*NOTE*: If extraction fails at first, **clear** all cells below final rows of standardized CSV!  

*Calculate* Difference in elevation (MAT and MAP too?) between original and simulated coordinates  
- Determine if differences in elev or climate relate to differences in model results!  


##### Organize Climate Data  

```{r message = FALSE}

TS_sims_2kE <- read_csv(here::here("analyses", "new_coords", "new_clim", "sims_2ka_s_1901-2019MSY.csv"), na = c("-9999", "-9999.0")) %>%
  rename(specimen_number = ID1, replicate = ID2, lat_n2k = Latitude, long_n2k = Longitude, elev_m_n = Elevation) %>% 
  filter(replicate %in% c("rep1", "rep2", "rep3", "rep4", "rep5")) %>%  # Remove replicates 6-10 (previously generated)
  filter(!is.na(MAT)) %>%  #Filter records (1 rep obs, or 119 rows here) in the ocean
  select(-c(Rad01:Rad12, Rad_wt:Rad_at, MAR)) #remove these columns
  
#Column renaming function

rename_ftn <- function(x, apnd, rang){         
  names_x <- colnames(x)[rang]
  print(paste(names_x, apnd, sep = ""))
} 

#Add in YoC
nemo_2k_YoC <- nemo_r_2 %>% 
  select(specimen_number, year) %>%  
  rename(YoC = year)



TS_sims_2kE_YoC <- merge(TS_sims_2kE, nemo_2k_YoC, all.x = TRUE) #Takes too much memory??

sims_2kE_YoC <- TS_sims_2kE_YoC %>% 
  filter(YoC == Year) %>%  #Select year-of-collection climate conditions x 5 replicates for each record
  select(-YoC)
#3709 observations instead of 3715: some simulated records w/ elevation < 0 --> excluded
#1 replicate in ocean removed


#Append column names
colnames(sims_2kE_YoC)[7:236] <- rename_ftn(sims_2kE_YoC, apnd = "_Y", rang = 7:236)


#Average across years 1901 - 2000 for each specimen
TS_2k_100avg <- TS_sims_2kE %>% 
  filter(Year >= 1901 & Year < 2001) %>% #Can adjust period (e.g. 80, 90, 110 yr ave)
  group_by(specimen_number) %>% #Cannot group by multiple columns, kept only specimen number
  summarize_at(vars(Tmax01:RH), mean)  #It works!
#NA values returned if any single value is NA - looks like it mostly affects Rad and MAR

  
colnames(TS_2k_100avg)[2:231] <- rename_ftn(TS_2k_100avg, apnd = "_100Y", rang = 2:231)

## merge YoC & long-term data

sims_2kE_m <- merge(TS_2k_100avg, sims_2kE_YoC, all.x = TRUE)


## Anomalies

anoms_2k1 <- sims_2kE_m %>% 
  select(specimen_number:elev_m_n, Tmax01_100Y:PPT12_100Y, Tmax_wt_100Y:PPT_at_100Y, MAT_100Y:MSP_100Y, 
         Tmax01_Y:PPT12_Y, Tmax_wt_Y:PPT_at_Y, MAT_Y:MSP_Y) %>% 
  filter(!is.na(MAT_Y)) #remove records without YoC climate - will apply to all climate variables

anoms_2k2 <- anoms_2k1 %>% 
  mutate(Tmax01_A = Tmax01_Y - Tmax01_100Y,
         Tmax02_A = Tmax02_Y - Tmax02_100Y,
         Tmax03_A = Tmax03_Y - Tmax03_100Y,
         Tmax04_A = Tmax04_Y - Tmax04_100Y,
         Tmax05_A = Tmax05_Y - Tmax05_100Y,
         Tmax06_A = Tmax06_Y - Tmax06_100Y,
         Tmax07_A = Tmax07_Y - Tmax07_100Y,
         Tmax08_A = Tmax08_Y - Tmax08_100Y,
         Tmax09_A = Tmax09_Y - Tmax09_100Y,
         Tmax10_A = Tmax10_Y - Tmax10_100Y,
         Tmax11_A = Tmax11_Y - Tmax11_100Y,
         Tmax12_A = Tmax12_Y - Tmax12_100Y,
         Tmin01_A = Tmin01_Y - Tmin01_100Y,
         Tmin02_A = Tmin02_Y - Tmin02_100Y,
         Tmin03_A = Tmin03_Y - Tmin03_100Y,
         Tmin04_A = Tmin04_Y - Tmin04_100Y,
         Tmin05_A = Tmin05_Y - Tmin05_100Y,
         Tmin06_A = Tmin06_Y - Tmin06_100Y,
         Tmin07_A = Tmin07_Y - Tmin07_100Y,
         Tmin08_A = Tmin08_Y - Tmin08_100Y,
         Tmin09_A = Tmin09_Y - Tmin09_100Y,
         Tmin10_A = Tmin10_Y - Tmin10_100Y,
         Tmin11_A = Tmin11_Y - Tmin11_100Y,
         Tmin12_A = Tmin12_Y - Tmin12_100Y,
         Tave01_A = Tave01_Y - Tave01_100Y,
         Tave02_A = Tave02_Y - Tave02_100Y,
         Tave03_A = Tave03_Y - Tave03_100Y,
         Tave04_A = Tave04_Y - Tave04_100Y,
         Tave05_A = Tave05_Y - Tave05_100Y,
         Tave06_A = Tave06_Y - Tave06_100Y,
         Tave07_A = Tave07_Y - Tave07_100Y,
         Tave08_A = Tave08_Y - Tave08_100Y,
         Tave09_A = Tave09_Y - Tave09_100Y,
         Tave10_A = Tave10_Y - Tave10_100Y,
         Tave11_A = Tave11_Y - Tave11_100Y,
         Tave12_A = Tave12_Y - Tave12_100Y,
         PPT01_A = PPT01_Y - PPT01_100Y,
         PPT02_A = PPT02_Y - PPT02_100Y,
         PPT03_A = PPT03_Y - PPT03_100Y,
         PPT04_A = PPT04_Y - PPT04_100Y,
         PPT05_A = PPT05_Y - PPT05_100Y,
         PPT06_A = PPT06_Y - PPT06_100Y,
         PPT07_A = PPT07_Y - PPT07_100Y,
         PPT08_A = PPT08_Y - PPT08_100Y,
         PPT09_A = PPT09_Y - PPT09_100Y,
         PPT10_A = PPT10_Y - PPT10_100Y,
         PPT11_A = PPT11_Y - PPT11_100Y,
         PPT12_A = PPT12_Y - PPT12_100Y,
         Tmax_wt_A = Tmax_wt_Y - Tmax_wt_100Y,
         Tmax_sp_A = Tmax_sp_Y - Tmax_sp_100Y,
         Tmax_sm_A = Tmax_sm_Y - Tmax_sm_100Y,
         Tmax_at_A = Tmax_at_Y - Tmax_at_100Y,
         Tmin_wt_A = Tmin_wt_Y - Tmin_wt_100Y,
         Tmin_sp_A = Tmin_sp_Y - Tmin_sp_100Y,
         Tmin_sm_A = Tmin_sm_Y - Tmin_sm_100Y,
         Tmin_at_A = Tmin_at_Y - Tmin_at_100Y,
         Tave_wt_A = Tave_wt_Y - Tave_wt_100Y,
         Tave_sp_A = Tave_sp_Y - Tave_sp_100Y,
         Tave_sm_A = Tave_sm_Y - Tave_sm_100Y,
         Tave_at_A = Tave_at_Y - Tave_at_100Y,
         PPT_wt_A = PPT_wt_Y - PPT_wt_100Y,
         PPT_sp_A = PPT_sp_Y - PPT_sp_100Y,
         PPT_sm_A = PPT_sm_Y - PPT_sm_100Y,
         PPT_at_A = PPT_at_Y - PPT_at_100Y,
         MAT_A = MAT_Y - MAT_100Y,
         MWMT_A = MWMT_Y - MWMT_100Y,
         MCMT_A = MCMT_Y - MCMT_100Y,
         MAP_A = MAP_Y - MAP_100Y,
         MSP_A = MSP_Y - MSP_100Y)


anoms_2k3 <- anoms_2k2 %>% 
  select(specimen_number:elev_m_n, Tmax01_A:MSP_A)


## Combine data frames into one for all 2k simulations climate

sims_2k_all <- merge(sims_2kE_m, anoms_2k3, all.x = TRUE) %>% 
  rename(year = Year) %>% 
  select(specimen_number, year, replicate, lat_n2k, long_n2k, elev_m_n, everything())

write_csv(sims_2k_all, here::here("analyses", "new_coords", "sims_2ka_all.csv"))

```



#### 5 km Displacement  

Create Simulated records

```{r message = FALSE}
  
sim_list_5ka <- list()

for(x in 1:5){ #5 reps (10 reps was too much for my cpu to handle...)
  
  long_n1 <- rep(NA, nrow(nemo_r_2))
  lat_n1 <- rep(NA, nrow(nemo_r_2))

  
for(i in 1:length(nemo_r_2$lat)){
  
  latlong_n <- destPoint(p = c(nemo_r_2$long[i], nemo_r_2$lat[i]), b = sample(0:360, 1), d = runif(1, 0, 5000))
  
  long_n1[i] <-  latlong_n[1]
  lat_n1[i] <-  latlong_n[2]
   
}
  
  sim_list_5ka[[x]] <- cbind(nemo_r_2$specimen_number, long_n1, lat_n1)
  colnames(sim_list_5ka[[x]]) <- c("specimen_number", "long_n5k", "lat_n5k")
  
  print(x)
  
}
  
  
#Combine Rows
#using reduce() 
sims_all_5ka <- as.data.frame(reduce(sim_list_5ka, rbind))  %>% 
  mutate(replicate = c(rep("rep1", times = 743), rep("rep2", times = 743), rep("rep3", times = 743), rep("rep4", times = 743), rep("rep5", times = 743))) %>% 
  mutate(long_n5k = as.numeric(long_n5k), lat_n5k = as.numeric(lat_n5k))

```


##### Add elevation to records -- **RUN MANUALLY**  
**Very time-consuming!!!**  
```{r message = FALSE, eval = FALSE}
#Add elevation
library(elevatr)
prj_dd <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs" #Define parameters for get_elev_point()

sims_all_5kaE <- sims_all_5ka
sims_all_5kaE$elev_m_n <- NA

sims_all_5kaE$elev_m_n <- get_elev_point(sims_all_5ka[,2:3], prj = prj_dd, src = "epqs")$elevation #store only elev, function creates new df...


#save as CSV before something fucks up and I have to rerun the 3h elev grab code
write_csv(sims_all_5kaE, here::here("analyses", "new_coords", "sims_5ka.csv"))


#E.g. 2, 5, 15, 25 km coords all in same csv...?
```



**Standardize csv, fetch & organize ClimateNA Data**  


```{r message = FALSE}
sims_5KE <- read_csv(here::here("analyses", "new_coords", "sims_5ka.csv")) %>% 
  filter(!elev_m_n < 0)  #remove records with negative elevation
#3706 records - expect to lose more & more to negative elevation as displacement grows


sims_5KE_s <- sims_5KE %>% 
  select(specimen_number, replicate, lat_n5k, long_n5k, elev_m_n) %>% 
  rename(ID1 = specimen_number, ID2 = replicate, lat = lat_n5k, long = long_n5k, el = elev_m_n)

#Using replicate as a second ID -- will have to add YoC back in later for calculating anomalies

write_csv(sims_5KE_s, here::here("analyses", "new_coords", "sims_5ka_s.csv"))



######
#Organize Climate Data
TS_sims_5kE <- read_csv(here::here("analyses", "new_coords", "new_clim", "sims_5ka_s_1901-2019MSY.csv"), na = c("-9999", "-9999.0")) %>%
  rename(specimen_number = ID1, replicate = ID2, lat_n5k = Latitude, long_n5k = Longitude, elev_m_n = Elevation) %>% 
  filter(!is.na(MAT)) %>% #Filter records (13 rep obs, or 1547 rows here) in the ocean
  select(-c(Rad01:Rad12, Rad_wt:Rad_at, MAR)) #remove these columns

#Add in YoC
nemo_5k_YoC <- nemo_r_2 %>% 
  select(specimen_number, year) %>%  
  rename(YoC = year)


TS_sims_5kE_YoC <- merge(TS_sims_5kE, nemo_5k_YoC, all.x = TRUE) 

sims_5kE_YoC <- TS_sims_5kE_YoC %>% 
  filter(YoC == Year) %>%  
  select(-YoC)
#3706 obs (3693 after NA removal):
# 13 rows all NA - all retrieved coords ARE IN THE OCEAN (elevations also 0) - removed

#Append column names
colnames(sims_5kE_YoC)[7:236] <- rename_ftn(sims_5kE_YoC, apnd = "_Y", rang = 7:236)


#Average across years 1901 - 2000 for each specimen
TS_5k_100avg <- TS_sims_5kE %>% 
  filter(Year >= 1901 & Year < 2001) %>% 
  group_by(specimen_number) %>% 
  summarize_at(vars(Tmax01:RH), mean)  
#NA values returned if any single value is NA - looks like it mostly affects Rad and MAR

colnames(TS_5k_100avg)[2:231] <- rename_ftn(TS_5k_100avg, apnd = "_100Y", rang = 2:231)

## merge YoC & long-term data

sims_5kE_m <- merge(TS_5k_100avg, sims_5kE_YoC, all.x = TRUE)


## Anomalies

anoms_5k1 <- sims_5kE_m %>% 
  select(specimen_number:elev_m_n, Tmax01_100Y:PPT12_100Y, Tmax_wt_100Y:PPT_at_100Y, MAT_100Y:MSP_100Y, 
         Tmax01_Y:PPT12_Y, Tmax_wt_Y:PPT_at_Y, MAT_Y:MSP_Y) %>% 
  filter(!is.na(MAT_Y)) #remove records without YoC climate - will apply to all climate variables

anoms_5k2 <- anoms_5k1 %>% 
  mutate(Tmax01_A = Tmax01_Y - Tmax01_100Y,
         Tmax02_A = Tmax02_Y - Tmax02_100Y,
         Tmax03_A = Tmax03_Y - Tmax03_100Y,
         Tmax04_A = Tmax04_Y - Tmax04_100Y,
         Tmax05_A = Tmax05_Y - Tmax05_100Y,
         Tmax06_A = Tmax06_Y - Tmax06_100Y,
         Tmax07_A = Tmax07_Y - Tmax07_100Y,
         Tmax08_A = Tmax08_Y - Tmax08_100Y,
         Tmax09_A = Tmax09_Y - Tmax09_100Y,
         Tmax10_A = Tmax10_Y - Tmax10_100Y,
         Tmax11_A = Tmax11_Y - Tmax11_100Y,
         Tmax12_A = Tmax12_Y - Tmax12_100Y,
         Tmin01_A = Tmin01_Y - Tmin01_100Y,
         Tmin02_A = Tmin02_Y - Tmin02_100Y,
         Tmin03_A = Tmin03_Y - Tmin03_100Y,
         Tmin04_A = Tmin04_Y - Tmin04_100Y,
         Tmin05_A = Tmin05_Y - Tmin05_100Y,
         Tmin06_A = Tmin06_Y - Tmin06_100Y,
         Tmin07_A = Tmin07_Y - Tmin07_100Y,
         Tmin08_A = Tmin08_Y - Tmin08_100Y,
         Tmin09_A = Tmin09_Y - Tmin09_100Y,
         Tmin10_A = Tmin10_Y - Tmin10_100Y,
         Tmin11_A = Tmin11_Y - Tmin11_100Y,
         Tmin12_A = Tmin12_Y - Tmin12_100Y,
         Tave01_A = Tave01_Y - Tave01_100Y,
         Tave02_A = Tave02_Y - Tave02_100Y,
         Tave03_A = Tave03_Y - Tave03_100Y,
         Tave04_A = Tave04_Y - Tave04_100Y,
         Tave05_A = Tave05_Y - Tave05_100Y,
         Tave06_A = Tave06_Y - Tave06_100Y,
         Tave07_A = Tave07_Y - Tave07_100Y,
         Tave08_A = Tave08_Y - Tave08_100Y,
         Tave09_A = Tave09_Y - Tave09_100Y,
         Tave10_A = Tave10_Y - Tave10_100Y,
         Tave11_A = Tave11_Y - Tave11_100Y,
         Tave12_A = Tave12_Y - Tave12_100Y,
         PPT01_A = PPT01_Y - PPT01_100Y,
         PPT02_A = PPT02_Y - PPT02_100Y,
         PPT03_A = PPT03_Y - PPT03_100Y,
         PPT04_A = PPT04_Y - PPT04_100Y,
         PPT05_A = PPT05_Y - PPT05_100Y,
         PPT06_A = PPT06_Y - PPT06_100Y,
         PPT07_A = PPT07_Y - PPT07_100Y,
         PPT08_A = PPT08_Y - PPT08_100Y,
         PPT09_A = PPT09_Y - PPT09_100Y,
         PPT10_A = PPT10_Y - PPT10_100Y,
         PPT11_A = PPT11_Y - PPT11_100Y,
         PPT12_A = PPT12_Y - PPT12_100Y,
         Tmax_wt_A = Tmax_wt_Y - Tmax_wt_100Y,
         Tmax_sp_A = Tmax_sp_Y - Tmax_sp_100Y,
         Tmax_sm_A = Tmax_sm_Y - Tmax_sm_100Y,
         Tmax_at_A = Tmax_at_Y - Tmax_at_100Y,
         Tmin_wt_A = Tmin_wt_Y - Tmin_wt_100Y,
         Tmin_sp_A = Tmin_sp_Y - Tmin_sp_100Y,
         Tmin_sm_A = Tmin_sm_Y - Tmin_sm_100Y,
         Tmin_at_A = Tmin_at_Y - Tmin_at_100Y,
         Tave_wt_A = Tave_wt_Y - Tave_wt_100Y,
         Tave_sp_A = Tave_sp_Y - Tave_sp_100Y,
         Tave_sm_A = Tave_sm_Y - Tave_sm_100Y,
         Tave_at_A = Tave_at_Y - Tave_at_100Y,
         PPT_wt_A = PPT_wt_Y - PPT_wt_100Y,
         PPT_sp_A = PPT_sp_Y - PPT_sp_100Y,
         PPT_sm_A = PPT_sm_Y - PPT_sm_100Y,
         PPT_at_A = PPT_at_Y - PPT_at_100Y,
         MAT_A = MAT_Y - MAT_100Y,
         MWMT_A = MWMT_Y - MWMT_100Y,
         MCMT_A = MCMT_Y - MCMT_100Y,
         MAP_A = MAP_Y - MAP_100Y,
         MSP_A = MSP_Y - MSP_100Y)


anoms_5k3 <- anoms_5k2 %>% 
  select(specimen_number:elev_m_n, Tmax01_A:MSP_A)


## Combine data frames into one for all 2k simulations climate

sims_5k_all <- merge(sims_5kE_m, anoms_5k3, all.x = TRUE) %>% 
  rename(year = Year) %>% 
  select(specimen_number, year, replicate, lat_n5k, long_n5k, elev_m_n, everything())

write_csv(sims_5k_all, here::here("analyses", "new_coords", "sims_5ka_all.csv"))

```


#### 15 km Displacement  



Create Simulated records

```{r message = FALSE}
  
sim_list_15ka <- list()

for(x in 1:5){ #5 reps (10 reps was too much for my cpu to handle...)
  
  long_n1 <- rep(NA, nrow(nemo_r_2))
  lat_n1 <- rep(NA, nrow(nemo_r_2))

  
for(i in 1:length(nemo_r_2$lat)){
  
  latlong_n <- destPoint(p = c(nemo_r_2$long[i], nemo_r_2$lat[i]), b = sample(0:360, 1), d = runif(1, 0, 15000))
  
  long_n1[i] <-  latlong_n[1]
  lat_n1[i] <-  latlong_n[2]
   
}
  
  sim_list_15ka[[x]] <- cbind(nemo_r_2$specimen_number, long_n1, lat_n1)
  colnames(sim_list_15ka[[x]]) <- c("specimen_number", "long_n15k", "lat_n15k")
  
  print(x)
  
}
  
  
#Combine Rows
#using reduce() 
sims_all_15ka <- as.data.frame(reduce(sim_list_15ka, rbind))  %>% 
  mutate(replicate = c(rep("rep1", times = 743), rep("rep2", times = 743), rep("rep3", times = 743), rep("rep4", times = 743), rep("rep5", times = 743))) %>% 
  mutate(long_n15k = as.numeric(long_n15k), lat_n15k = as.numeric(lat_n15k))

```


##### Add elevation to records -- **RUN MANUALLY**  
```{r message = FALSE, eval = FALSE}
#Add elevation
library(elevatr)
prj_dd <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs" #Define parameters for get_elev_point()

sims_all_15kaE <- sims_all_15ka
sims_all_15kaE$elev_m_n <- NA

sims_all_15kaE$elev_m_n <- get_elev_point(sims_all_15ka[,2:3], prj = prj_dd, src = "epqs")$elevation #store only elev, function creates new df...


#save as CSV before something fucks up and I have to rerun the 3h elev grab code
write_csv(sims_all_15kaE, here::here("analyses", "new_coords", "sims_15ka.csv"))


#E.g. 2, 5, 15, 25 km coords all in same csv...?
```



**Standardize csv, fetch & organize ClimateNA Data**  


```{r message = FALSE}
sims_15KE <- read_csv(here::here("analyses", "new_coords", "sims_15ka.csv")) %>% 
  filter(!elev_m_n < 0)  #remove records with negative elevation
#3706 records - expect to lose more & more to negative elevation as displacement grows


sims_15KE_s <- sims_15KE %>% 
  select(specimen_number, replicate, lat_n15k, long_n15k, elev_m_n) %>% 
  rename(ID1 = specimen_number, ID2 = replicate, lat = lat_n15k, long = long_n15k, el = elev_m_n)

#Using replicate as a second ID -- will have to add YoC back in later for calculating anomalies

write_csv(sims_15KE_s, here::here("analyses", "new_coords", "sims_15ka_s.csv"))



######
#Organize Climate Data
TS_sims_15kE <- read_csv(here::here("analyses", "new_coords", "new_clim", "sims_15ka_s_1901-2019MSY.csv"), na = c("-9999", "-9999.0")) %>%
  rename(specimen_number = ID1, replicate = ID2, lat_n15k = Latitude, long_n15k = Longitude, elev_m_n = Elevation) %>% 
  filter(!is.na(MAT)) %>% #Filter records (13 rep obs, or 1547 rows here) in the ocean
  select(-c(Rad01:Rad12, Rad_wt:Rad_at, MAR)) #remove these columns


#Add in YoC
nemo_15k_YoC <- nemo_r_2 %>% 
  select(specimen_number, year) %>%  
  rename(YoC = year)


TS_sims_15kE_YoC <- merge(TS_sims_15kE, nemo_15k_YoC, all.x = TRUE) 

sims_15kE_YoC <- TS_sims_15kE_YoC %>% 
  filter(YoC == Year) %>%  
  select(-YoC)
#3630 obs


#Append column names
colnames(sims_15kE_YoC)[7:236] <- rename_ftn(sims_15kE_YoC, apnd = "_Y", rang = 7:236)


#Average across years 1901 - 2000 for each specimen
TS_15k_100avg <- TS_sims_15kE %>% 
  filter(Year >= 1901 & Year < 2001) %>% #Can adjust period (e.g. 80, 90, 110 yr ave)
  group_by(specimen_number) %>% #Cannot group by multiple columns, kept only specimen number
  summarize_at(vars(Tmax01:RH), mean)  #It works!

colnames(TS_15k_100avg)[2:231] <- rename_ftn(TS_15k_100avg, apnd = "_100Y", rang = 2:231)

## merge YoC & long-term data

sims_15kE_m <- merge(TS_15k_100avg, sims_15kE_YoC, all.x = TRUE)


## Anomalies

anoms_15k1 <- sims_15kE_m %>% 
  select(specimen_number:elev_m_n, Tmax01_100Y:PPT12_100Y, Tmax_wt_100Y:PPT_at_100Y, MAT_100Y:MSP_100Y, 
         Tmax01_Y:PPT12_Y, Tmax_wt_Y:PPT_at_Y, MAT_Y:MSP_Y) %>% 
  filter(!is.na(MAT_Y)) #remove records without YoC climate - will apply to all climate variables

anoms_15k2 <- anoms_15k1 %>% 
  mutate(Tmax01_A = Tmax01_Y - Tmax01_100Y,
         Tmax02_A = Tmax02_Y - Tmax02_100Y,
         Tmax03_A = Tmax03_Y - Tmax03_100Y,
         Tmax04_A = Tmax04_Y - Tmax04_100Y,
         Tmax05_A = Tmax05_Y - Tmax05_100Y,
         Tmax06_A = Tmax06_Y - Tmax06_100Y,
         Tmax07_A = Tmax07_Y - Tmax07_100Y,
         Tmax08_A = Tmax08_Y - Tmax08_100Y,
         Tmax09_A = Tmax09_Y - Tmax09_100Y,
         Tmax10_A = Tmax10_Y - Tmax10_100Y,
         Tmax11_A = Tmax11_Y - Tmax11_100Y,
         Tmax12_A = Tmax12_Y - Tmax12_100Y,
         Tmin01_A = Tmin01_Y - Tmin01_100Y,
         Tmin02_A = Tmin02_Y - Tmin02_100Y,
         Tmin03_A = Tmin03_Y - Tmin03_100Y,
         Tmin04_A = Tmin04_Y - Tmin04_100Y,
         Tmin05_A = Tmin05_Y - Tmin05_100Y,
         Tmin06_A = Tmin06_Y - Tmin06_100Y,
         Tmin07_A = Tmin07_Y - Tmin07_100Y,
         Tmin08_A = Tmin08_Y - Tmin08_100Y,
         Tmin09_A = Tmin09_Y - Tmin09_100Y,
         Tmin10_A = Tmin10_Y - Tmin10_100Y,
         Tmin11_A = Tmin11_Y - Tmin11_100Y,
         Tmin12_A = Tmin12_Y - Tmin12_100Y,
         Tave01_A = Tave01_Y - Tave01_100Y,
         Tave02_A = Tave02_Y - Tave02_100Y,
         Tave03_A = Tave03_Y - Tave03_100Y,
         Tave04_A = Tave04_Y - Tave04_100Y,
         Tave05_A = Tave05_Y - Tave05_100Y,
         Tave06_A = Tave06_Y - Tave06_100Y,
         Tave07_A = Tave07_Y - Tave07_100Y,
         Tave08_A = Tave08_Y - Tave08_100Y,
         Tave09_A = Tave09_Y - Tave09_100Y,
         Tave10_A = Tave10_Y - Tave10_100Y,
         Tave11_A = Tave11_Y - Tave11_100Y,
         Tave12_A = Tave12_Y - Tave12_100Y,
         PPT01_A = PPT01_Y - PPT01_100Y,
         PPT02_A = PPT02_Y - PPT02_100Y,
         PPT03_A = PPT03_Y - PPT03_100Y,
         PPT04_A = PPT04_Y - PPT04_100Y,
         PPT05_A = PPT05_Y - PPT05_100Y,
         PPT06_A = PPT06_Y - PPT06_100Y,
         PPT07_A = PPT07_Y - PPT07_100Y,
         PPT08_A = PPT08_Y - PPT08_100Y,
         PPT09_A = PPT09_Y - PPT09_100Y,
         PPT10_A = PPT10_Y - PPT10_100Y,
         PPT11_A = PPT11_Y - PPT11_100Y,
         PPT12_A = PPT12_Y - PPT12_100Y,
         Tmax_wt_A = Tmax_wt_Y - Tmax_wt_100Y,
         Tmax_sp_A = Tmax_sp_Y - Tmax_sp_100Y,
         Tmax_sm_A = Tmax_sm_Y - Tmax_sm_100Y,
         Tmax_at_A = Tmax_at_Y - Tmax_at_100Y,
         Tmin_wt_A = Tmin_wt_Y - Tmin_wt_100Y,
         Tmin_sp_A = Tmin_sp_Y - Tmin_sp_100Y,
         Tmin_sm_A = Tmin_sm_Y - Tmin_sm_100Y,
         Tmin_at_A = Tmin_at_Y - Tmin_at_100Y,
         Tave_wt_A = Tave_wt_Y - Tave_wt_100Y,
         Tave_sp_A = Tave_sp_Y - Tave_sp_100Y,
         Tave_sm_A = Tave_sm_Y - Tave_sm_100Y,
         Tave_at_A = Tave_at_Y - Tave_at_100Y,
         PPT_wt_A = PPT_wt_Y - PPT_wt_100Y,
         PPT_sp_A = PPT_sp_Y - PPT_sp_100Y,
         PPT_sm_A = PPT_sm_Y - PPT_sm_100Y,
         PPT_at_A = PPT_at_Y - PPT_at_100Y,
         MAT_A = MAT_Y - MAT_100Y,
         MWMT_A = MWMT_Y - MWMT_100Y,
         MCMT_A = MCMT_Y - MCMT_100Y,
         MAP_A = MAP_Y - MAP_100Y,
         MSP_A = MSP_Y - MSP_100Y)


anoms_15k3 <- anoms_15k2 %>% 
  select(specimen_number:elev_m_n, Tmax01_A:MSP_A)


## Combine data frames into one for all 2k simulations climate

sims_15k_all <- merge(sims_15kE_m, anoms_15k3, all.x = TRUE) %>% 
  rename(year = Year) %>% 
  select(specimen_number, year, replicate, lat_n15k, long_n15k, elev_m_n, everything())

write_csv(sims_15k_all, here::here("analyses", "new_coords", "sims_15ka_all.csv"))

```
<br>  



#### 25 km Displacement  

**NOTE**: *Do 30 km displacement instead?*  


```{r message = FALSE}
  
sim_list_25ka <- list()

for(x in 1:5){ #5 reps (10 reps was too much for my cpu to handle...)
  
  long_n1 <- rep(NA, nrow(nemo_r_2))
  lat_n1 <- rep(NA, nrow(nemo_r_2))

  
for(i in 1:length(nemo_r_2$lat)){
  
  latlong_n <- destPoint(p = c(nemo_r_2$long[i], nemo_r_2$lat[i]), b = sample(0:360, 1), d = runif(1, 0, 25000))
  
  long_n1[i] <-  latlong_n[1]
  lat_n1[i] <-  latlong_n[2]
   
}
  
  sim_list_25ka[[x]] <- cbind(nemo_r_2$specimen_number, long_n1, lat_n1)
  colnames(sim_list_25ka[[x]]) <- c("specimen_number", "long_n25k", "lat_n25k")
  
  print(x)
  
}
  
  
#Combine Rows
#using reduce() 
sims_all_25ka <- as.data.frame(reduce(sim_list_25ka, rbind))  %>% 
  mutate(replicate = c(rep("rep1", times = 743), rep("rep2", times = 743), rep("rep3", times = 743), rep("rep4", times = 743), rep("rep5", times = 743))) %>% 
  mutate(long_n25k = as.numeric(long_n25k), lat_n25k = as.numeric(lat_n25k))

```


##### Add elevation to records -- **RUN MANUALLY**  
```{r message = FALSE, eval = FALSE}
#Add elevation
library(elevatr)
prj_dd <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs" #Define parameters for get_elev_point()

sims_all_25kaE <- sims_all_25ka
sims_all_25kaE$elev_m_n <- NA

sims_all_25kaE$elev_m_n <- get_elev_point(sims_all_25ka[,2:3], prj = prj_dd, src = "epqs")$elevation #store only elev, function creates new df...


#save as CSV before something fucks up and I have to rerun the 3h elev grab code
write_csv(sims_all_25kaE, here::here("analyses", "new_coords", "sims_25ka.csv"))


#E.g. 2, 5, 15, 25 km coords all in same csv...?
```



**Standardize csv, fetch & organize ClimateNA Data**  

*START HERE*  

```{r message = FALSE}
sims_25KE <- read_csv(here::here("analyses", "new_coords", "sims_25ka.csv")) %>% 
  filter(!elev_m_n < 0)  #remove records with negative elevation
#3672 records - expect to lose more & more to negative elevation as displacement grows


sims_25KE_s <- sims_25KE %>% 
  select(specimen_number, replicate, lat_n25k, long_n25k, elev_m_n) %>% 
  rename(ID1 = specimen_number, ID2 = replicate, lat = lat_n25k, long = long_n25k, el = elev_m_n)

#Using replicate as a second ID -- will have to add YoC back in later for calculating anomalies

write_csv(sims_25KE_s, here::here("analyses", "new_coords", "sims_25ka_s.csv"))



######
#Organize Climate Data
TS_sims_25kE <- read_csv(here::here("analyses", "new_coords", "new_clim", "sims_25ka_s_1901-2019MSY.csv"), na = c("-9999", "-9999.0")) %>%
  rename(specimen_number = ID1, replicate = ID2, lat_n25k = Latitude, long_n25k = Longitude, elev_m_n = Elevation) %>% 
  filter(!is.na(MAT)) %>% #Filter records (13 rep obs, or 1547 rows here) in the ocean
  select(-c(Rad01:Rad12, Rad_wt:Rad_at, MAR)) #remove these columns


#Add in YoC
nemo_25k_YoC <- nemo_r_2 %>% 
  select(specimen_number, year) %>%  
  rename(YoC = year)


TS_sims_25kE_YoC <- merge(TS_sims_25kE, nemo_25k_YoC, all.x = TRUE) 

sims_25kE_YoC <- TS_sims_25kE_YoC %>% 
  filter(YoC == Year) %>%  
  select(-YoC)
# obs


#Append column names
colnames(sims_25kE_YoC)[7:236] <- rename_ftn(sims_25kE_YoC, apnd = "_Y", rang = 7:236)


#Average across years 1901 - 2000 for each specimen
TS_25k_100avg <- TS_sims_25kE %>% 
  filter(Year >= 1901 & Year < 2001) %>% 
  group_by(specimen_number) %>% 
  summarize_at(vars(Tmax01:RH), mean)  

colnames(TS_25k_100avg)[2:231] <- rename_ftn(TS_25k_100avg, apnd = "_100Y", rang = 2:231)

## merge YoC & long-term data

sims_25kE_m <- merge(TS_25k_100avg, sims_25kE_YoC, all.x = TRUE)


## Anomalies

anoms_25k1 <- sims_25kE_m %>% 
  select(specimen_number:elev_m_n, Tmax01_100Y:PPT12_100Y, Tmax_wt_100Y:PPT_at_100Y, MAT_100Y:MSP_100Y, 
         Tmax01_Y:PPT12_Y, Tmax_wt_Y:PPT_at_Y, MAT_Y:MSP_Y) %>% 
  filter(!is.na(MAT_Y)) #remove records without YoC climate - will apply to all climate variables

anoms_25k2 <- anoms_25k1 %>% 
  mutate(Tmax01_A = Tmax01_Y - Tmax01_100Y,
         Tmax02_A = Tmax02_Y - Tmax02_100Y,
         Tmax03_A = Tmax03_Y - Tmax03_100Y,
         Tmax04_A = Tmax04_Y - Tmax04_100Y,
         Tmax05_A = Tmax05_Y - Tmax05_100Y,
         Tmax06_A = Tmax06_Y - Tmax06_100Y,
         Tmax07_A = Tmax07_Y - Tmax07_100Y,
         Tmax08_A = Tmax08_Y - Tmax08_100Y,
         Tmax09_A = Tmax09_Y - Tmax09_100Y,
         Tmax10_A = Tmax10_Y - Tmax10_100Y,
         Tmax11_A = Tmax11_Y - Tmax11_100Y,
         Tmax12_A = Tmax12_Y - Tmax12_100Y,
         Tmin01_A = Tmin01_Y - Tmin01_100Y,
         Tmin02_A = Tmin02_Y - Tmin02_100Y,
         Tmin03_A = Tmin03_Y - Tmin03_100Y,
         Tmin04_A = Tmin04_Y - Tmin04_100Y,
         Tmin05_A = Tmin05_Y - Tmin05_100Y,
         Tmin06_A = Tmin06_Y - Tmin06_100Y,
         Tmin07_A = Tmin07_Y - Tmin07_100Y,
         Tmin08_A = Tmin08_Y - Tmin08_100Y,
         Tmin09_A = Tmin09_Y - Tmin09_100Y,
         Tmin10_A = Tmin10_Y - Tmin10_100Y,
         Tmin11_A = Tmin11_Y - Tmin11_100Y,
         Tmin12_A = Tmin12_Y - Tmin12_100Y,
         Tave01_A = Tave01_Y - Tave01_100Y,
         Tave02_A = Tave02_Y - Tave02_100Y,
         Tave03_A = Tave03_Y - Tave03_100Y,
         Tave04_A = Tave04_Y - Tave04_100Y,
         Tave05_A = Tave05_Y - Tave05_100Y,
         Tave06_A = Tave06_Y - Tave06_100Y,
         Tave07_A = Tave07_Y - Tave07_100Y,
         Tave08_A = Tave08_Y - Tave08_100Y,
         Tave09_A = Tave09_Y - Tave09_100Y,
         Tave10_A = Tave10_Y - Tave10_100Y,
         Tave11_A = Tave11_Y - Tave11_100Y,
         Tave12_A = Tave12_Y - Tave12_100Y,
         PPT01_A = PPT01_Y - PPT01_100Y,
         PPT02_A = PPT02_Y - PPT02_100Y,
         PPT03_A = PPT03_Y - PPT03_100Y,
         PPT04_A = PPT04_Y - PPT04_100Y,
         PPT05_A = PPT05_Y - PPT05_100Y,
         PPT06_A = PPT06_Y - PPT06_100Y,
         PPT07_A = PPT07_Y - PPT07_100Y,
         PPT08_A = PPT08_Y - PPT08_100Y,
         PPT09_A = PPT09_Y - PPT09_100Y,
         PPT10_A = PPT10_Y - PPT10_100Y,
         PPT11_A = PPT11_Y - PPT11_100Y,
         PPT12_A = PPT12_Y - PPT12_100Y,
         Tmax_wt_A = Tmax_wt_Y - Tmax_wt_100Y,
         Tmax_sp_A = Tmax_sp_Y - Tmax_sp_100Y,
         Tmax_sm_A = Tmax_sm_Y - Tmax_sm_100Y,
         Tmax_at_A = Tmax_at_Y - Tmax_at_100Y,
         Tmin_wt_A = Tmin_wt_Y - Tmin_wt_100Y,
         Tmin_sp_A = Tmin_sp_Y - Tmin_sp_100Y,
         Tmin_sm_A = Tmin_sm_Y - Tmin_sm_100Y,
         Tmin_at_A = Tmin_at_Y - Tmin_at_100Y,
         Tave_wt_A = Tave_wt_Y - Tave_wt_100Y,
         Tave_sp_A = Tave_sp_Y - Tave_sp_100Y,
         Tave_sm_A = Tave_sm_Y - Tave_sm_100Y,
         Tave_at_A = Tave_at_Y - Tave_at_100Y,
         PPT_wt_A = PPT_wt_Y - PPT_wt_100Y,
         PPT_sp_A = PPT_sp_Y - PPT_sp_100Y,
         PPT_sm_A = PPT_sm_Y - PPT_sm_100Y,
         PPT_at_A = PPT_at_Y - PPT_at_100Y,
         MAT_A = MAT_Y - MAT_100Y,
         MWMT_A = MWMT_Y - MWMT_100Y,
         MCMT_A = MCMT_Y - MCMT_100Y,
         MAP_A = MAP_Y - MAP_100Y,
         MSP_A = MSP_Y - MSP_100Y)


anoms_25k3 <- anoms_25k2 %>% 
  select(specimen_number:elev_m_n, Tmax01_A:MSP_A)


## Combine data frames into one for all 2k simulations climate

sims_25k_all <- merge(sims_25kE_m, anoms_25k3, all.x = TRUE) %>% 
  rename(year = Year) %>% 
  select(specimen_number, year, replicate, lat_n25k, long_n25k, elev_m_n, everything())

write_csv(sims_25k_all, here::here("analyses", "new_coords", "sims_25ka_all.csv"))

```

*See next RMD script for analyses of dispersed data!!!*  


```{r DEFUNCT, eval = FALSE, message = FALSE}
#DEFUNCT/FAILED ANALYSES
library(elevatr) #must have package rgdal installed!
#Get elevation for new coords as well
prj_dd <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs" #Define parameters for get_elev_point() ##MAKE DATUM SPECIFIC TO RECORD???

for(x in 1:length(sim_list_2ka)){
  
elev_n1 <- rep(NA, nrow(nemo_r_2))

for(i in 1:length(nemo_r_2$lat)){

elev_n1[i] <- get_elev_point(as.numeric(sim_list_2ka[[x]][,2:3]), prj = prj_dd, src = "epqs")

}

sim_list_2ka_e[[x]] <- cbind(sim_list_2ka, elev_n1)

}

######Unable to apply for loop using get_elev_point to list - too complicated


#Tadeo's randCoord function
#randCoord(x = c(-120.66, -120), y = c(34.66, 37), d_min = 1.5, d_max = 2.5)

#randCoord(x = nemo_r_2$long, y = nemo_r_2$lat, d_min = 1.5, d_max = 2.5)

# apply() functions approach


#destPoint alone
nemo_ncoords_2km <- nemo_r_2 %>% 
  mutate(long_n1 = sapply(X = c(long, lat), FUN = destPoint(long, lat, b = sample(0:360, 1), d = 2000)))


#getLatLong_r function
nemo_ncoords_2km <- nemo_r_2 %>% 
  mutate(longlat_n1 = sapply(X = c(long, lat, d = 2000), FUN = getLatLong_r(lat = lat, long = long)))

#destPoint(p = c(long, lat), b = sample(0:360, 1), d = 2000)[,1]) #for loop or tapply

nemo_ncoords_2km <- nemo_r_2 %>% 
  mutate(long_n1 = NA, lat_n1 = NA)


```


