---
title: "ClimateNA Data for cch1 & 2"
author: "Devin Gamble"
date: "4/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, message = FALSE, echo = FALSE}
library(tidyverse)
library(here)
library(ggplot2)
library(stringr)
library(janitor)
```


## Obtaining Climate data for all specimen records  

###### This document and the code within is based off earlier attempts at obtaining climateNA data ('cch2_getCNA.R', 'climate_import-clean_cch1.Rmd')  


###### Jump to Step 4. to see how climate data are organized and which parameters are available.  
<br>  

### Step 1.  

**Creating a ClimateNA compatible file to download climate data**



- Read in the cleaned, updated datset for cch1 and cch2
- Standardize columns to have two identifiers (specimen number and year), lat/long, and elevation
- Export ClimateNA compatible csv file  

```{r warning = FALSE, message = FALSE}
nemo_all1 <- read_csv(here::here("data_cleaning", "nemo_all_2.csv")) %>% 
  rename(YoC = year) #to avoid later confusion


nemo_1_CNA <- nemo_all1 %>% 
  select(specimen_number, YoC, lat, long, elev_m) %>% 
  rename(ID1 = specimen_number, ID2 = YoC, el = elev_m)  #specimen_number and year used as identifiers


write_csv(nemo_1_CNA, here::here("climateNA", "all_cna", "all_CNA_s.csv"), na = "")

```
**IMPORTANT**  

There is a bug in saving csv files after using `dplyr` functions like `select()` to remove columns. After savine the file with `write_csv()`, you need to open up the csv, select all of the white space to the right of the five standardized columns - *where there used to be columns* , right-click, and hit **Clear Contents** to erase the ghosts of leftover data. This is the only way I've found the standradized csv to work with ClimateNA. You will have to repeat this process everytime you run the above code and wish to get any output from ClimateNA.    
<br>  

### Step 2.  

**Specify variables and time series to download, using this standardized csv in the ClimateNA application**

#### Normals & Decadal data 
Open the climateNA application. Under the 'Multi-Location' heading, specify which normals you would like to download in the box. Select the input file (the csv we just standardized). Specify the output file with the name and a desired pathway/folder. Once you hit `Start`, Climate NA will download the type of normals you specified and append them as columns to the standardized csv.  

You should then have a new file with normals for all the locations in the original csv.  
For Normals, I selected 'All Variables' to download annual, seasonal, and monthly 30-year averages for 1951-1980 and 1981 - 2010.  
<br>  


#### Annual, Monthly, and Seasonal data for all years  
Under the 'Multi-location' heading, select `Historical Time Series`. Below this box, select the desired variables (I selected 'All Variables' again). Up to the right, select the years for which you would like to download climate data (e.g. 1901 - 2018). Select the same standardized input csv and the name and location for the output file. Hit `Start TS`.    
(This will probably take some time.....)  

You should eventually get a csv file with data for all the specified years, now with a new first column 'Year'. You will now have **as many rows** as the *number of different years* multiplied by *the number of observations in the original dataset*.  

Note: ClimateNA uses `-9999` as NA values, be sure to account for these later.  

<br>  

### Step 3.
**Organizing our ClimateNA data**  


#### Read in Normals  
These csv's have monthly, seasonal, and annual climate variables averaged over each of the 30-year periods

```{r warning = FALSE, message = FALSE}
norms_1951_1980 <- read_csv(here::here("climateNA", "all_cna", "cna_rawfiles", "all_CNA_Normal_1951_1980MSY.csv"), na = c("-9999", "-9999.0")) %>% #Fix NAs
  rename(specimen_number = ID1, YoC = ID2, lat = Latitude, long = Longitude, elev_m = Elevation) %>% #Fixing names
  filter(!(specimen_number %in% c("DAV300381", "UC880904"))) #obs in water - remove
#1764 obs - same as input df

norms_1981_2010 <- read_csv(here::here("climateNA", "all_cna", "cna_rawfiles", "all_CNA_Normal_1981_2010MSY.csv"), na = c("-9999", "-9999.0")) %>% #Fix NAs
  rename(specimen_number = ID1, YoC = ID2, lat = Latitude, long = Longitude, elev_m = Elevation) %>% 
  filter(!(specimen_number %in% c("DAV300381", "UC880904")))

#252 total columns in these


```

<br>  

#### Read in Time Series
These data has monthly, seasonal, and annual variables for ALL YEARS (1901 - 2018)

```{r warning = FALSE, message = FALSE}
TS_1901_2018 <- read_csv(here::here("climateNA", "all_cna", "cna_rawfiles", "all_CNA_1901-2018MSY.csv"), na = c("-9999", "-9999.0")) %>%
  rename(specimen_number = ID1, YoC = ID2, lat = Latitude, long = Longitude, elev_m = Elevation) %>% 
  filter(!(specimen_number %in% c("DAV300381", "UC880904")))

#Columns that appear as `col_logical()` in the run message are largely NA

```
<br>  


##### Checking things out


For some reason, two records come back with all NAs:  

- DAV300381 - 1997   - Appears to be in the middle of the pacific ocean [cch2] - removed.
- UC880904 - 1938   - Appears to be very close, but not in water [cch2] - removed

<br>  


#### Match TS data to specimens for the Yoc and the Yoc - 1 (previous year)  

```{r}
TS_YoC <- TS_1901_2018 %>% 
  filter(YoC == Year) %>% 
  select(-Year)
#1675 obs - some lost outside of 1901-2018


TS_YoC_less1 <- TS_1901_2018 %>% 
  filter(YoC == Year - 1) %>% 
  select(-Year)
#1677 obs - similar issue [2 more obs]


```

<br>  

#### Combining Climate Datasets (Prospective)  

Both the Climate Normals and the Time Series should now have the same number of columns. The two timeseries subsets (YoC and YoC - 1) will have slightly fewer rows when combined with the normals, which will show up as NAs.  

We need to append column names of these variables with their particular sources (e.g. _YoC, _N51). Below I employ a simple function to do so, but there may be a more straightforward way.  


```{r}
#Function: append character strings to column names

rename_ftn <- function(x, apnd, rang){         
  names_x <- colnames(x)[rang]
  print(paste(names_x, apnd, sep = ""))
} 

#Where `x` is the df, `apnd` is the string to be added as a suffix, and `rang` is the range of columns, by position, to add the character string to.

```

<br>  


##### First, the Normals. This should be a relatively clean merge.  


```{r message = FALSE, results = 'hide'}
norms51 <- norms_1951_1980
colnames(norms51)[6:252] <- rename_ftn(norms51, apnd = "_N51", rang = 6:252)

norms81 <- norms_1981_2010
colnames(norms81)[6:252] <- rename_ftn(norms81, apnd = "_N81", rang = 6:252)


Norms_df <- merge(norms51, norms81) %>% 
  select(-c(Rad01_N51:Rad12_N51, Rad_wt_N51:Rad_at_N51, MAR_N51, Rad01_N81:Rad12_N81, Rad_wt_N81:Rad_at_N81, MAR_N81)) #Mostly NAs
#Ensure columns 1-5 [specimen_number, YoC, lat, long, elev_m] are intace and merged correctly
#There should be 465 columns and 1764 obs (in this case)
write_csv(Norms_df, here::here("climateNA", "all_CNA", "norms_raw_51_and_81.csv"))

```

<br>  


##### Now, the Time Series YoC and YoC - 1.

```{r message = FALSE, results = 'hide'}

YoC_1 <- TS_YoC
colnames(YoC_1)[6:252] <- rename_ftn(YoC_1, apnd = "_Y", rang = 6:252)
#2 less obs than YoC_less1 [1675]


YoC_less1 <- TS_YoC_less1
colnames(YoC_less1)[6:252] <- rename_ftn(YoC_less1, apnd = "_L1", rang = 6:252) #L1 for last year
# obs [1677]


YoC_df <- merge(YoC_less1, YoC_1, all.x = TRUE) %>% 
  select(-c(Rad01_L1:Rad12_L1, Rad_wt_L1:Rad_at_L1, MAR_L1, Rad01_Y:Rad12_Y, Rad_wt_Y:Rad_at_Y, MAR_Y)) #Remove NAs
#1677 obs and 465 rows - looks good! No rows should have been eliminated.
#2 obs should be NAs for "_Y1" parameters BUT sum(is.na(YoC_df$MAT_Y)) is showing 3. strange. NA introduced in merge??
#Removing the all.x = TRUE leads to a df with 1674 obs - there is a non-overlapping difference! YoC_less1 has a record included that YoC_1 does not, and vice versa, hence the 3NA values when merged - all good.

write_csv(YoC_df, here::here("climateNA", "all_cna", "YoC_Y_and_L1.csv"))

```
###### Keeping the YoC and Norms datasets separate for now, there's no reason to combine them (yet)  


<br>  

#### Additional formatting of Climate averages:
```{r}
## Calculate Long-Term Average Climate:


#Average across years 1901 - 2000 for each specimen

TS_100_avg <- TS_1901_2018 %>% 
  filter(Year >= 1901 & Year < 2001) %>% #Can adjust period (e.g. 80, 90, 110 yr ave)
  group_by(specimen_number) %>% #Cannot group by multiple columns, kept only specimen number
  summarize_at(vars(Tmax01:RH), mean) %>%  #It works!
  select(-c(Rad01:Rad12, Rad_wt:Rad_at, MAR)) #Remove NAs
#NA values returned if any single value is NA - looks like it mostly affects Rad and MAR

colnames(TS_100_avg)[2:231] <- rename_ftn(TS_100_avg, apnd = "_100Y", rang = 2:231) #100Y for 100-yr avg

write_csv(TS_100_avg, here::here("climateNA", "all_cna", "100y_avg.csv"))


#Get older set of normals? (e.g. 1901 - 1930)



#See Susan's recent seed mass paper where they compare two sets of normals - they are very correlated and patterns are pretty much the same


```

<br>  

### Step 4.  
**Climate Parameter Selection, Tidying Up**  


Now to select the parameters that we weill definitely be using in analyses. Parameters that are uninformative of local conditions or have a large number of NA values will be ignored, with the option of being removed.  

Here are the suffixes appended to columns to indicate the period for which parameters are given (from code above):  


In 'Norms_df':  
`_N51` indicates a parameter averaged from 1951 - 1980  
`_N81` indicates an average from 1981 - 2010  


In 'YoC_df':  
`_Y` indicates the climate variables for the year in which a specimen was collected  
`_L1` indicates variables for the year prior to which a specimen was collected, as in less (or last) 1  


<br>  

The following climate parameters for Temperature and Precipitation (and other derived variables) will be retained:  


#### Temperature  
- *Annual*: MAT, MWMT, MCMT, TD
- *Seasonal*: Tave, Tmax, Tmin
- *Monthly*: Tave, Tmax, Tmin


#### Precipitation  
- *Annual*: MAP, MSP, PAS
- *Seasonal*: PPT, PAS(wt & sp only)
- *Monthly*: PPT, PAS

#### Combined/Derived variables
- *Annual*: AHM, SHM, DD<0, DD>5, NFFD, Eref, CMD, RH, EMT & EXT
- *Seasonal*: DD_0, DD5, NFFD(wt & sp only), Eref, CMD, RH
- *Monthly*: DD_0, DD5, Eref, CMD, RH, NFFD


##### IGNORE (Remove)  
- *Annual*: DD<18, DD>18, FFP, bFFP, eFFP, MAR
- *Seasonal*: RAD, DD_18, DD18, NFFD(sm & at), PAS(sm & at)
- *Monthly* RAD, DD_18, DD18 

###### Is there any point to removing these variables, other than not having them in the datasheet? The climate csvs are already huge, and apart from the TS one, removing these columns has no other discernable effect.  

<br>  

##### Definitions (from ClimateNA [6.20] 'help' document)  

`_wt` = Dec, Jan, Feb; `_sp` = Mar, Apr, May; `sm` = Jun, Jul, Aug; `_at` = Sep, Oct, Nov  
`_0` to `_12` indicate months  


*Directly calculated annual variables*:  
<font size = "2">
MAT	=  	mean annual temperature (°C),  
MWMT = 	mean warmest month temperature (°C),  
MCMT   =	mean coldest month temperature (°C),  
TD 	 =	temperature difference between MWMT and MCMT, or continentality (°C),  
MAP  =		mean annual precipitation (mm),  
MSP  =		May to September precipitation (mm),  
AHM   =	annual heat-moisture index (MAT+10)/(MAP/1000))  
SHM  =	 	summer heat-moisture index ((MWMT)/(MSP/1000))  
	</font>  
	
*Derived annual variables*:  
<font size = "2">
DD<0	=	degree-days below 0°C, chilling degree-days  
DD>5	 = 	degree-days above 5°C, growing degree-days  
DD<18	= degree-days below 18°C, heating degree-days  
DD>18	= degree-days above 18°C, cooling degree-days  
NFFD	= 	the number of frost-free days  
FFP		= frost-free period  
bFFP	= 	the day of the year on which FFP begins  
eFFP	= 	the day of the year on which FFP ends  
PAS	= precipitation as snow (mm). For individual years, it covers the period between August in the previous year and July in the current year.  
EMT		= extreme minimum temperature over 30 years  
EXT		= extreme maximum temperature over 30 years  
Eref	= 	Hargreaves reference evaporation (mm)  
CMD	= 	Hargreaves climatic moisture deficit (mm)  
MAR	= 	mean annual solar radiation (MJ m‐2 d‐1)  
RH	= 	mean annual relative humidity (%)  
  </font>  

<br>  
 
```{r echo = FALSE, eval = FALSE}
#Removing Variables #Optional!
YoC_dfc <- YoC_df %>% 
  select(-c(Rad01_L1:Rad12_L1, DD_18_01_L1:DD18_12_L1, Rad_wt_L1:Rad_at_L1, DD_18_wt_L1:DD18_at_L1, PAS_sm_L1, PAS_at_L1,  DD_18_L1, DD18_L1, bFFP_L1:FFP_L1, MAR_L1, #Last year
            Rad01_Y1:Rad12_Y1, DD_18_01_Y1:DD18_12_Y1, Rad_wt_Y1:Rad_at_Y1, DD_18_wt_Y1:DD18_at_Y1, PAS_sm_Y1, PAS_at_Y1,  DD_18_Y1, DD18_Y1, bFFP_Y1:FFP_Y1, MAR_Y1)) #YoC



Norms_dfc <- Norms_df %>% 
  select(-c(Rad01_N51:Rad12_N51, DD_18_01_N51:DD18_12_N51, Rad_wt_N51:Rad_at_N51, DD_18_wt_N51:DD18_at_N51, PAS_sm_N51, PAS_at_N51, DD_18_N51, DD18_N51, bFFP_N51:FFP_N51, MAR_N51, #51-80
            Rad01_N81:Rad12_N81, DD_18_01_N81:DD18_12_N81, Rad_wt_N81:Rad_at_N81, DD_18_wt_N81:DD18_at_N81, PAS_sm_N81, PAS_at_N81, DD_18_N81, DD18_N81, bFFP_N81:FFP_N81, MAR_N81)) #81-10


```



##### Calculate Anomalies   
Anomalies = deviations from the average climate. These could be computed as `abs(x_ann - x_norm)` where 'x' is a climate variable.  


Calculate anomalies for long-term average climate *and* climate normals - compare later.  


```{r}

#Calculate anomalies for YoC and YoC-1
#Save each in YoC dataset, one csv for each average/normal period used (2 or 3 total?)


#Combine all into one df to calculate anomalies
#First, Norms and 100y avg. Both have 1764 obs (the total)


Norms_100Y <- merge(Norms_df, TS_100_avg) #Good


#Now for YoC and Yoc-1. Should have 1155 columns and 1764 obs (87-90 rows NAs for Yoc variables):
climNA_nemo_merge <- merge(Norms_100Y, YoC_df, all.x = TRUE)

```

```{r}
#Creating Anomalies for the 100Y average - ignore Rad variables, too many NAs
#climNa_nemo_all1 <- climNA_nemo_merge %>% 
# mutate_at(vars(Tmax01_100Y:RH_100Y))



write_csv(climNA_nemo_merge, here::here("climateNA", "all_cna", "climNA_nemo_all.csv"))


```



Update after calculating anomalies here. Since each observation must have annual data to calculate the anomalies, save (overwrite) new csv over YoC_df.  



**NEXT STEPS**
- Find out the best way to calculate Climate anomalies - Calculate Anomalies
- Research which climate parameters other studies have found to be important - help in finding most influential ones  
- Climate EDA & Analyses  



